\entry{1}{Kellie Dora Rogers}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Walter Rogers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Patricia Kay Ehlers}}}}, was born on 17 Mar 1977 in Fort Knox, Meade, KY. Second Generation}
\marriage{Kellie married \href{#}{\textcolor{accent}{\textbf{\underline{Jeremiah Parranto.}}}}}
\dividerline

\entry{2}{John Walter Rogers}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Keith Rogers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Doris Henze}}}}, was born on 29 Jan 1957 in Dubuque, Dubuque, IA. 1976 in Dubuque, Dubuque, IA.}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Patricia Kay Ehlers}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jerome Francis Ehlers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Norma Linda Leik}}}}, on 16 Jan}
\childrenrenheading
\childentrylinked{1}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Kellie Dora Rogers}}}}}
\childentrylinked{--}{ii}{\href{#}{\textcolor{accent}{\textbf{\underline{Jerrod Rogers was born on 26 Feb 1978 in Fort Knox, Meade, KY}}}}}
\childentrylinked{--}{iii}{\href{#}{\textcolor{accent}{\textbf{\underline{Joel Rogers was born on 13 Sep 1982 in Dubuque, Dubuque, IA}}}}}
\dividerline

\entry{3}{Patricia Kay Ehlers}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jerome Francis Ehlers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Norma Linda Leik}}}}, was born on 3 Aug 1956 in Dubuque, Dubuque, IA. Dubuque, Dubuque, IA. Third Generation}
\marriage{Patricia married \href{#}{\textcolor{accent}{\textbf{\underline{John Walter Rogers}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Keith Rogers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Doris Henze}}}}, on 16 Jan 1976 in}
\dividerline

\entry{4}{Robert Keith Rogers}{son of \href{#}{\textcolor{accent}{\textbf{\underline{William Vincent Rogers Sr}}}}. and Esther Elnora Williams, was born on 16 Oct 1926 in Richland Center, Richland, WI and died on 7 Nov 2012 in Dubuque, Dubuque, IA, at age 86. General Notes: He registered for the U.S. military draft, Oct 13, 1944, at which time he was a resident of Farmington, Dakota, MN, where he listed his employer as Henry Brandtjen. He is described as 5'9", 144 lbs., brown hair, and brown eyes. Frankfurt, Darmstadt, Hesse, Germany.}
\marriage{Robert married \href{#}{\textcolor{accent}{\textbf{\underline{Doris Henze}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Paul Henze}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Katherine "Kate" Wilde}}}}, on 20 Nov 1948 in}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Gerald "Gary" Rogers}}}}}
\childentrylinked{--}{ii}{\href{#}{\textcolor{accent}{\textbf{\underline{Robert P}}}} Rogers}
\childentrylinked{--}{iii}{\href{#}{\textcolor{accent}{\textbf{\underline{Timothy Rogers}}}}}
\childentrylinked{--}{iv}{\href{#}{\textcolor{accent}{\textbf{\underline{Linda Rogers}}}}}
\childentry{}{2 v. John Walter Rogers}
\childentrylinked{--}{vi}{\href{#}{\textcolor{accent}{\textbf{\underline{Thomas Rogers}}}}}
\dividerline

\entry{5}{Doris Henze}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Paul Henze}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Katherine "Kate" Wilde}}}}, was born on 21 May 1928 in Zary, Zary, Lubusz, Poland and died on 15 Jan 2015 in Dubuque, Dubuque, IA, at age 86. General Notes: She was a World War II refugee. On Feb 13, 1945, the Soviet Red Army conquered the town of Zary (referred to as Sorau by the Germans). The Polish-German border was hotly contested during the war and initially the Allies wanted the border to be further east so that Zary would have fallen within German territory. But at the Potsdam Conference in July-August 1945, at which the United States, the United Kingdom, and the Soviet Union negotiated the map of Europe and their various domains of control. The border was eventually settled to the west and Zary was designated as part of Poland. The German residents were expelled and the town was repopulated by Poles in the years that followed. Doris Nov 1948 in Frankfurt, Darmstadt, Hesse, Germany.}
\marriage{Doris married \href{#}{\textcolor{accent}{\textbf{\underline{Robert Keith Rogers}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{William Vincent Rogers Sr}}}}. and Esther Elnora Williams, on 20}
\dividerline

\entry{6}{Jerome Francis Ehlers}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Francis Kenneth "Frank" Ehlers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Louise Kamm}}}}, was born on 13 Dec 1932 in Buena Vista, Clayton, IA.}
\marriage{Jerome married \href{#}{\textcolor{accent}{\textbf{\underline{Norma Linda Leik}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Russell William Leik}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Viola Miller}}}}.}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Dennis Ehlers}}}}}
\childentry{}{3 ii. Patricia Kay Ehlers}
\childentrylinked{--}{iii}{\href{#}{\textcolor{accent}{\textbf{\underline{Steve Ehlers}}}}}
\childentrylinked{--}{iv}{\href{#}{\textcolor{accent}{\textbf{\underline{Todd Ehlers}}}}}
\childentrylinked{--}{v}{\href{#}{\textcolor{accent}{\textbf{\underline{Chris Ehlers}}}}}
\childentrylinked{--}{vi}{\href{#}{\textcolor{accent}{\textbf{\underline{Brian Ehlers}}}}}
\childentrylinked{--}{vii}{\href{#}{\textcolor{accent}{\textbf{\underline{Jill Ehlers}}}}}
\dividerline

\entry{7}{Norma Linda Leik}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Russell William Leik}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Viola Miller}}}}, was born on 27 Aug 1935 in Dubuque, Dubuque, IA and died on 17 Aug 2015 in Dubuque, Dubuque, IA, at age 79. Kamm. Fourth Generation}
\marriage{Norma married \href{#}{\textcolor{accent}{\textbf{\underline{Jerome Francis Ehlers}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Francis Kenneth "Frank" Ehlers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Louise}}}}}
\dividerline

\entry{8}{William Vincent Rogers Sr. son of George Richard Rogers and Catherine}{Josephine Ruppert, was born on 22 Oct 1886 in Clyde, Iowa, WI and died on 4 Jun 1961 in Dodgeville, Iowa, WI, at age 74. General Notes: In 1910, he and his family rented land in Arena, Iowa, WI, where he worked as a farm laborer. In 1920, they owned a house on Church Street, in Dodgeville, Iowa, WI, where he worked as a miner in a lead mine. In 1930, they owned a farm in Wyoming, Iowa, WI. They must have lost their farm during the Great Depression, for in 1940, they rented a farm there. Mary E. Williams, on 30 Mar 1910 in Iowa Co., WI.}
\marriage{William married \href{#}{\textcolor{accent}{\textbf{\underline{Esther Elnora Williams}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jesse Williams and}}}}}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Clifford Everett Rogers was born on 2 Nov 1911 in Mazomanie, Dane, WI}}}}}
\childentrylinked{--}{ii}{\href{#}{\textcolor{accent}{\textbf{\underline{William Vincent Rogers Jr}}}} was born on 29 Dec 1916 in Spring Green, Iowa, WI and died on 12}
\childentryplain{Mar 2000 in New Albany}{iii}{, Floyd, IN, at age 83.}
\childentrylinked{--}{iv}{\href{#}{\textcolor{accent}{\textbf{\underline{Gerald Sylvester Rogers was born on 2 May 1919 in Dodgeville, Iowa, WI}}}}}
\childentry{}{4 iv. Robert Keith Rogers}
\dividerline

\entry{9}{Esther Elnora Williams}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jesse Williams}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary E}}}}. Williams, was born in 1890 in Dodgeville, Iowa, WI and died in 1928 in Dodgeville, Iowa, WI, at age 38. and Catherine Josephine Ruppert, on 30 Mar 1910 in Iowa Co., WI.}
\marriage{Esther married \href{#}{\textcolor{accent}{\textbf{\underline{William Vincent Rogers Sr.}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{George Richard Rogers}}}}}
\dividerline

\entry{10}{Paul Henze .}{General Notes: There are a number of possible matches for Paul Henze and Katherine Wilde in several towns that are currently situated along the western border of Poland.}
\marriage{Paul married \href{#}{\textcolor{accent}{\textbf{\underline{Katherine "Kate" Wilde.}}}}}
\childrenrenheading
\childentrylinked{5}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Doris Henze}}}}}
\childentry{}{11. Katherine "Kate" Wilde .}
\childentry{}{Katherine married Paul Henze.}
\dividerline

\entry{12}{Francis Kenneth "Frank" Ehlers}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Frederick "Fred" Ehlers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Adelaid Loretta De Mars}}}}, was born on 24 Apr 1907 in Holy Cross, Dubuque, IA and died on 24 Sep 1983 in Dubuque, Dubuque, IA, at age 76. General Notes: In 1940, he and his family rented a house in Dubuque, Dubuque, IA, where he worked as a moulder at a foundry. In 1950, they lived on Kaufman Street, in Dubuque, where he worked as a carpenter's assistant for a construction company. Charlotte's widowed father lived with them there at the time. Mary Machellack, on 17 May 1932 in Buena Vista, Clayton, IA.}
\marriage{Francis married \href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Louise Kamm}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Kamm and}}}}}
\childrenheading
\childentrylinked{6}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jerome Francis Ehlers}}}}}
\dividerline

\entry{13}{Charlotte Louise Kamm}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Kamm}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Machellack}}}}, was born on 17 Nov 1913 in Buena Vista, Clayton, IA and died on 2 Feb 1997 in Dubuque, Dubuque, IA, at age 83. Frederick "Fred" Ehlers and Adelaid Loretta De Mars, on 17 May 1932 in Buena Vista, Clayton, IA.}
\marriage{Charlotte married \href{#}{\textcolor{accent}{\textbf{\underline{Francis Kenneth "Frank" Ehlers}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann}}}}}
\dividerline

\entry{14}{Russell William Leik}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Edward Harvey Leik}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Ida May Parker}}}}, was born on 6 Dec 1905 in Center, Dubuque, IA and died on 2 Jun 1968 in Dubuque, Dubuque, IA, at age 62. General Notes: In 1930, he and his family rented a house at 2524 Jackson Street, in Julien, Dubuque, IA, where he worked as a machinist at a sack and door factory. In 1940, they rented a house at 2643 Central Street, in Dubuque, Dubuque, IA, where he worked as a millworker at a sack and door mill. and Theresa Ospelt, on 28 Dec 1926 in Dubuque Co., IA.}
\marriage{Russell married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Viola Miller}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Christian Frederick Miller}}}}}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Joan Pearl Leik was born on 17 Oct 1927 in Dubuque, Dubuque, IA}}}}}
\childentryplain{and died on 26 Oct 2010 in East Dubuque}{ii}{, Jo Daviess, IL, at age 83.}
\childentrylinked{--}{iii}{\href{#}{\textcolor{accent}{\textbf{\underline{Germaine Evelyn Leik was born on 4 Aug 1932 in Dubuque, Dubuque, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 27 Nov 1984}}}}}
\childentryplain{in Dubuque}{iv}{, Dubuque, IA, at age 52.}
\childentry{}{7 iii. Norma Linda Leik}
\dividerline

\entry{15}{Anna Viola Miller}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Christian Frederick Miller}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Theresa Ospelt}}}}, was born on 29 May 1907 in Center, Dubuque, IA and died on 24 Feb 2000 in Dubuque, Dubuque, IA, at age 92. Dubuque Co., IA. Fifth Generation}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Russell William Leik}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Edward Harvey Leik}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Ida May Parker}}}}, on 28 Dec 1926 in}
\dividerline

\entry{16}{George Richard Rogers}{son of \href{#}{\textcolor{accent}{\textbf{\underline{James Henry Rogers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Jane Lean}}}}, was born on 22 Aug 1859 in Linden, Iowa, WI and died on 27 Nov 1935 in Spring Green, Iowa, WI, at age 76. General Notes: In 1880, he lived on his parents' farm in Clyde, Iowa, WI, where he worked as a laborer. In 1900, he and his family rented a house in Blue Mounds, Dane, WI, where he worked as a section hand for the railroad. In 1910, they owned a house on West 2nd Street, in Mount Horeb, Dane, WI, where he continued in the same line of work. In 1920, they rented a house at 135 Antoine Street, in Mineral Point, Iowa, WI, where he worked as a laborer at a foundry of some kind (it is blurred in the census, perhaps "engine works"). By 1930, he was a widower and he lived with his daughter, Rhoda, and the latter's family in Brigham, Iowa, WI, where he was retired. Feb 1884 in Iowa Co., WI.}
\marriage{George married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Josephine Ruppert}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Nicholas Ruppert}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaretta Ley}}}}, on 25}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Margaret E}}}} Rogers was born on 23 Mar 1885 in Iowa Co., WI and died on 25 Aug 1946, at age 61.}
\childentry{}{8 ii. William Vincent Rogers Sr.}
\childentrylinked{--}{iii}{\href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth J}}}} Rogers was born in Apr 1888 in Wisconsin and died on 8 Jun 1947 in Iowa Co., WI, at}
\childentry{}{age 59.}
\childentrylinked{--}{v}{\href{#}{\textcolor{accent}{\textbf{\underline{Frank Peter Rogers was born on 24 Feb 1890 in Wisconsin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 4 Dec 1960 in Dodgeville,}}}}}
\childentryplain{Iowa}{vi}{, WI, at age 70.}
\childentrylinked{--}{vii}{\href{#}{\textcolor{accent}{\textbf{\underline{Clara Rogers was born on 26 Oct 1891 in Mineral Point, Iowa, WI}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 10 Dec 1911 in}}}}}
\childentryplain{Chicago}{viii}{, Cook, IL, at age 20.}
\childentrylinked{--}{ix}{\href{#}{\textcolor{accent}{\textbf{\underline{Rhoda Ann Rogers was born in 1894 in Dodgeville, Iowa, WI}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 13 Feb 1960 in}}}}}
\childentryplain{Dodgeville}{x}{, Iowa, WI, at age 66.}
\dividerline

\entry{17}{Catherine Josephine Ruppert}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Nicholas Ruppert}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaretta Ley}}}}, was born on 6 Jan 1865 in Niederdonven, Grevenmacher, Luxembourg and died on 20 Sep 1920 in Dodgeville, Iowa, WI, at age 55. General Notes: Obituary, Iowa County Democrat, Sep 30, 1920: Mrs. George Rogers of this city died in St. Joseph's Hospital in Dodgeville Monday, Sept. 20, 1920, after a lingering illness. She had been in failing health for many years. Three months prior to her death she entered St. Joseph's Hospital, but the best of medical skill and tender care proved to no avail and she passed to life eternal well prepared with the rites of her Catholic faith. Mrs. Rogers was fifty-five years of age. She was a devoted wife and mother. Her husband, two sons and three daughters deeply mourn their loss. The funeral, which was largely attended, took place in Dodgeville Thursday morning with services in St. Joseph's Church. Requiem High Mass was celebrated by Rev. A. Ambauen. Internment in St. Joseph's Cemetery. Feb 1884 in Iowa Co., WI.}
\marriage{Catherine married \href{#}{\textcolor{accent}{\textbf{\underline{George Richard Rogers}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{James Henry Rogers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Jane Lean}}}}, on 25}
\dividerline

\entry{18}{Jesse Williams}{son of \href{#}{\textcolor{accent}{\textbf{\underline{David W}}}}. Williams Sr. and Hannah Jones, was born in Jan 1847 in Llanarmon-yn-lal, Denbighshire, Wales and died in 1930 in Dodgeville, Iowa, WI, at age 83. General Notes: In 1870, he lived on his parents' farm in Ridgeway, Iowa, WI, where he worked as a lead miner. In 1900, he and his family owned a house in Dodgeville, Iowa, WI, where he worked as a zinc ore miner. In 1910, they owned a farm in Wyoming, Iowa, WI. In 1920, they owned a farm in Dodgeville, Iowa, WI. In 1930, as a widower, he lived with his son, Frank, on the latter's farm in Wyoming, Iowa, WI.}
\marriage{Jesse married \href{#}{\textcolor{accent}{\textbf{\underline{Mary E. Williams}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Samuel Williams}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Ester}}}}, on 2 Aug 1886 in Iowa Co., WI.}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Everett B}}}} Williams was born on 3 Aug 1888 in Dodgeville, Iowa, WI.}
\childentry{}{9 ii. Esther Elnora Williams}
\childentrylinked{--}{iii}{\href{#}{\textcolor{accent}{\textbf{\underline{Frank Barnard Williams was born on 30 Nov 1895 in Dodgeville, Iowa, WI}}}}}
\dividerline

\entry{19}{Mary E. Williams}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Samuel Williams}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Ester}}}}, was born in Jan 1857 in Illinois and died in Apr 1929 in Spring Green, Iowa, WI, at age 72. General Notes: In 1880, she lived with her widowed mother in Dodgeville, Iowa, WI, where she worked as a domestic. WI.}
\marriage{Mary married \href{#}{\textcolor{accent}{\textbf{\underline{Jesse Williams}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{David W}}}}. Williams Sr. and Hannah Jones, on 2 Aug 1886 in Iowa Co.,}
\dividerline

\entry{24}{Johann Frederick "Fred" Ehlers}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Paul Ehlers}}}}, was born on 2 Oct 1865 in Hannover, Lower Saxony, Germany and died on 10 Oct 1946 in Dubuque, Dubuque, IA, at age 81. General Notes: In 1900, he and his family rented land and ran a farm in Concord, Dubuque, IA. In 1910-30, they owned a farm there. Marguerite Audere.}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Adelaid Loretta De Mars}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Flavian De Mars and}}}}}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elmer Ehlers was born in Mar 1890 in Iowa}}}}}
\childentrylinked{--}{ii}{\href{#}{\textcolor{accent}{\textbf{\underline{Paul Joseph Ehlers was born on 1 Jun 1892 in Holy Cross, Dubuque, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 23 Feb 1977 in}}}}}
\childentryplain{New Prague}{iii}{, Scott, MN, at age 84.}
\childentrylinked{--}{iv}{\href{#}{\textcolor{accent}{\textbf{\underline{Edna Marie Ehlers was born on 10 Dec 1897 in Sherrill, Dubuque, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 9 Nov 1966 in}}}}}
\childentryplain{Dubuque}{v}{, Dubuque, IA, at age 68.}
\childentrylinked{--}{vi}{\href{#}{\textcolor{accent}{\textbf{\underline{John H}}}} Ehlers was born on 25 Jun 1900 in Holy Cross, Dubuque, IA and died on 1 Mar 1968 in}
\childentryplain{Oakdale}{vii}{, Johnson, IA, at age 67.}
\childentrylinked{--}{viii}{\href{#}{\textcolor{accent}{\textbf{\underline{Frederick Andrew Ehlers was born on 24 Feb 1903 in Dubuque Co}}}} , IA and died on 15 May 1969}
\childentryplain{in Dubuque}{ix}{, Dubuque, IA, at age 66.}
\childentry{}{12 vi. Francis Kenneth "Frank" Ehlers}
\childentrylinked{--}{xi}{\href{#}{\textcolor{accent}{\textbf{\underline{Dorothea Ehlers was born on 7 Jan 1910 in Dubuque Co}}}} , IA and died on 5 Feb 1913 in Dubuque}
\childentryplain{Co.}{xii}{, IA, at age 3.}
\childentrylinked{--}{xiii}{\href{#}{\textcolor{accent}{\textbf{\underline{Gerald Lewis Ehlers was born on 21 Nov 1913 in Holy Cross, Dubuque, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 25 Jul}}}}}
\childentryplain{1998 in Dubuque}{xiv}{, Dubuque, IA, at age 84.}
\dividerline

\entry{25}{Adelaid Loretta De Mars}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Flavian De Mars}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Audere}}}}, was born in Aug 1871 in Dubuque, Dubuque, IA and died on 15 Feb 1935 in Dubuque, Dubuque, IA, at age 63. General Notes: Obituary: Mrs. Adelaid Ehlers, wife of John Ehlers, North Buena Vista, Iowa, died Thursday evening at Finley Hospital at 10:35 o'clock. She was born August 26, 1870 [sic], in this city [Buena Vista, IA] but for the last 35 years had lived in North Ehlers. She was a Catholic and attended Holy Cross church. Funeral services will be held Monday morning at 8:30 to St. Patrick's Church at 9 o'clock. Burial will be in Mt. Calvary cemetery.}
\marriage{Adelaid married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Frederick "Fred" Ehlers}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Paul Ehlers}}}}.}
\dividerline

\entry{26}{Joseph Kamm}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Heinrich "Henry" Kamm}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Margarethe "Mary" Bockel}}}}, was born on 6 Apr 1881 in Buena Vista, Clayton, IA and died on 18 Oct 1963 in Dubuque, Dubuque, IA, at age 82. General Notes: In 1920, he and his family owned a farm in Buena Vista, Clayton, IA. In 1930, they owned a house (or farm) there which was worth $4500 which indicates that they were successful for the area. At that time, he worked as a laborer at a quarry. In 1950, as a widower, he lived with his daughter Charlotte and the latter's family in Dubuque, Dubuque, IA, where he worked as a section hand for the railroad. Amelia Jesse.}
\marriage{Joseph married \href{#}{\textcolor{accent}{\textbf{\underline{Mary Machellack}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Belen Peter Machellack and}}}}}
\childrenheading
\childentrylinked{13}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Louise Kamm}}}}}
\dividerline

\entry{27}{Mary Machellack}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Belen Peter Machellack}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Amelia Jesse}}}}, was born on 20 Sep 1881 in Germany and died on 10 Oct 1947 in Buena Vista, Clayton, IA, at age 66. Margarethe "Mary" Bockel. 28. Edward Harvey Leik, son of \href{#}{\textcolor{accent}{\textbf{\underline{Conrad Leik}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Emmaline Shaffer}}}}, was born on 5 May 1881 in Dubuque, Dubuque, IA and died on 5 Dec 1963 in Dubuque, Dubuque, IA, at age 82. Anna Elizabeth Schaumburg.}
\marriage{Edward married \href{#}{\textcolor{accent}{\textbf{\underline{Ida May Parker}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Howard Parker and}}}}}
\childrenheading
\childentrylinked{14}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Russell William Leik}}}}}
\dividerline

\entry{29}{Ida May Parker}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Howard Parker}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Elizabeth Schaumburg}}}}, was born on 27 Apr 1887 in Dubuque, Dubuque, IA and died on 5 Sep 1943 in Dubuque, Dubuque, IA, at age 56.}
\marriage{Ida married \href{#}{\textcolor{accent}{\textbf{\underline{Edward Harvey Leik}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Conrad Leik}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Emmaline Shaffer}}}}.}
\dividerline

\entry{30}{Christian Frederick Miller}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Christoph Jakob Muller}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Christine Sofie Hellenschmitt}}}}, was born on 1 Aug 1871 in Iowa and died on 5 Oct 1966 in Dubuque, Dubuque, IA, at age 95. 1897 in Dubuque Co., IA.}
\marriage{Christian married \href{#}{\textcolor{accent}{\textbf{\underline{Theresa Ospelt}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Emil Anton Ospelt}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Ursula Taescher}}}}, on 1 Jun}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Leo George Miller was born on 16 Feb 1898 in Center, Dubuque, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 8 Nov 1966 in}}}}}
\childentryplain{Dubuque}{ii}{, Dubuque, IA, at age 68.}
\childentrylinked{--}{iii}{\href{#}{\textcolor{accent}{\textbf{\underline{Frederick Miller was born in Nov 1899 in Center, Dubuque, IA}}}}}
\childentrylinked{--}{iv}{\href{#}{\textcolor{accent}{\textbf{\underline{Charlotte B}}}} Miller was born on 16 Jan 1901 in Center, Dubuque, IA and died on 11 Oct 1996 in}
\childentryplain{Dubuque}{v}{, Dubuque, IA, at age 95.}
\childentrylinked{--}{vi}{\href{#}{\textcolor{accent}{\textbf{\underline{Bertha Ursula Miller was born on 5 Nov 1902 in Center, Dubuque, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 27 Jan 1999 in}}}}}
\childentryplain{Dubuque}{vii}{, Dubuque, IA, at age 96.}
\childentrylinked{--}{viii}{\href{#}{\textcolor{accent}{\textbf{\underline{Ellen S}}}} Miller was born on 9 Feb 1903 in Center, Dubuque, IA.}
\childentrylinked{--}{ix}{\href{#}{\textcolor{accent}{\textbf{\underline{Linda Esther Miller was born on 1 Nov 1905 in Center, Dubuque, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 9 Jul 1984 in}}}}}
\childentryplain{Dubuque}{x}{, Dubuque, IA, at age 78.}
\childentry{}{15 vii. Anna Viola Miller}
\childentrylinked{--}{xii}{\href{#}{\textcolor{accent}{\textbf{\underline{Milton Fred "Mike" Miller was born on 10 Mar 1909 in Center, Dubuque, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 30 Mar}}}}}
\childentryplain{1980}{xiii}{, at age 71.}
\childentrylinked{--}{xiv}{\href{#}{\textcolor{accent}{\textbf{\underline{Paul Miller was born on 30 Jan 1911 in Center, Dubuque, IA}}}}}
\childentrylinked{--}{xv}{\href{#}{\textcolor{accent}{\textbf{\underline{Edna Crystal Miller was born on 4 Sep 1912 in Center, Dubuque, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 28 May 2008 in}}}}}
\childentryplain{Dubuque}{xv}{, Dubuque, IA, at age 95.}
\childentrylinked{--}{xv}{\href{#}{\textcolor{accent}{\textbf{\underline{Bernice J}}}} Miller was born on 10 Nov 1914 in Center, Dubuque, IA and died on 30 Oct 1981 in}
\childentryplain{Dubuque}{xv}{, Dubuque, IA, at age 66.}
\dividerline

\entry{31}{Theresa Ospelt}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Emil Anton Ospelt}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Ursula Taescher}}}}, was born on 7 Feb 1877 in Austria and died on 19 Mar 1939 in Dubuque, Dubuque, IA, at age 62. Hellenschmitt, on 1 Jun 1897 in Dubuque Co., IA. Sixth Generation}
\marriage{Theresa married \href{#}{\textcolor{accent}{\textbf{\underline{Christian Frederick Miller}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Christoph Jakob Muller}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Christine Sofie}}}}}
\dividerline

\entry{32}{James Henry Rogers}{son of \href{#}{\textcolor{accent}{\textbf{\underline{John Rogers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Ann George}}}}, was born in 1833 in Gwithian, Cornwall, England and died on 18 Aug 1859 in Wisconsin, at age 26. 1855 in Camborne, Cornwall, England.}
\marriage{James married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Jane Lean}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{George Trewren Lean}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Susanna Perry Jones}}}}, on 7 Oct}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{James Henry Rogers Jr}}}} was born on 6 Mar 1856 in England and died on 23 Aug 1932 in Nobles}
\childentryplain{Co.}{ii}{, MN, at age 76.}
\childentry{}{16 ii. George Richard Rogers}
\dividerline

\entry{33}{Elizabeth Jane Lean}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{George Trewren Lean}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Susanna Perry Jones}}}}, was born on 23 Aug 1836 in Camborne, Cornwall, England and died on 12 Apr 1918 in Clyde, Iowa, WI, at age 81. Camborne, Cornwall, England.}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{James Henry Rogers}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{John Rogers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Ann George}}}}, on 7 Oct 1855 in}
\dividerline

\entry{34}{Nicholas Ruppert}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Franz Ruppert}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Claris Kieffer}}}}, was born on 1 Dec 1816 in Niederdonven, Grevenmacher, Luxembourg and died on 20 Oct 1900 in Iowa Co., WI, at age 83. General Notes: In 1880, he and his family ran a farm in Dodgeville, Iowa, WI. In 1900, as a widower, he lived with his son Matthew in Dodgeville, were the latter's family also had a farm (perhaps the same farm, inherited from his father). There was a place named Ruppert's Saloon in Mineral Point, WI, that may have some connection to the family. Reiff, on 29 Jan 1845 in Flaxweiler, Grevenmacher, Luxembourg.}
\marriage{Nicholas married \href{#}{\textcolor{accent}{\textbf{\underline{Margaretta Ley}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Peter Ley}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria}}}}}
\childrenheading
\childentrylinked{17}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Catherine Josephine Ruppert}}}}}
\dividerline

\entry{35}{Margaretta Ley}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Peter Ley}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Reiff}}}}, was born on 23 Mar 1828 in Niederdonven, Grevenmacher, Luxembourg and died on 19 Dec 1893 in Iowa Co., WI, at age 65. Flaxweiler, Grevenmacher, Luxembourg.}
\marriage{Margaretta married \href{#}{\textcolor{accent}{\textbf{\underline{Nicholas Ruppert}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Franz Ruppert}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Claris Kieffer}}}}, on 29 Jan 1845 in}
\dividerline

\entry{36}{David W. Williams Sr. was born about 1824 in Llandeilo}{Carmarthenshire, Wales and died on 22 Oct 1899 in Arena, Iowa, WI, about age 75. General Notes: In 1851-61, he and his family lived in Low Caldbeck, Cumberland, England, where he worked as a lead miner. They emigrated to the United States in 1862 and were residents of Ridgeway, Iowa, WI, in 1863. In 1870, they owned a farm there that was worth $1200 and they had a personal estate of $400, which would have made them middle class farmers. They continued to farm there in 1880. [Dodgeville Chronicle, Apr 19, 1872; Apr 26, 1872; May 3, 1872; May 10, 1872; May 17, 1872; May 31, 1872] He and his son, Jesse, were involved in a court case disputing inheritance with the heirs of David P. Jones, a relative of David's wife, in 1872.}
\marriage{David married \href{#}{\textcolor{accent}{\textbf{\underline{Hannah Jones}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Jones}}}}.}
\childrenrenheading
\childentrylinked{18}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jesse Williams}}}}}
\childentrylinked{--}{ii}{\href{#}{\textcolor{accent}{\textbf{\underline{William Williams was born about 1849 in Low Caldbeck, Cumberland, England}}}}}
\childentrylinked{--}{iii}{\href{#}{\textcolor{accent}{\textbf{\underline{Mary Williams was born about 1849 in Low Caldbeck, Cumberland, England}}}}}
\childentrylinked{--}{iv}{\href{#}{\textcolor{accent}{\textbf{\underline{Hannah Williams was born about 1851 in Low Caldbeck, Cumberland, England}}}}}
\childentrylinked{--}{v}{\href{#}{\textcolor{accent}{\textbf{\underline{James Williams was born about 1853 in Low Caldbeck, Cumberland, England}}}}}
\childentrylinked{--}{vi}{\href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Williams was born on 29 Jan 1856 in Low Caldbeck, Cumberland, England}}}}}
\childentrylinked{--}{vii}{\href{#}{\textcolor{accent}{\textbf{\underline{John Williams was born about 1859 in Low Caldbeck, Cumberland, England}}}}}
\childentrylinked{--}{viii}{\href{#}{\textcolor{accent}{\textbf{\underline{David W}}}} Williams Jr. was born on 26 Apr 1860 in Low Caldbeck, Cumberland, England and died}
\childentryplain{on 3 Jan 1909 in Dodgeville}{ix}{, Iowa, WI, at age 48.}
\dividerline

\entry{37}{Hannah Jones}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Jones}}}}, was born about 1824 in Llanbedr, Newport, Wales and died in 1895 in Iowa Co., WI, about age 71.}
\marriage{Hannah married \href{#}{\textcolor{accent}{\textbf{\underline{David W. Williams Sr..}}}}}
\dividerline

\entry{38}{Samuel Williams was born in Wales.}{General Notes: He and his wife emigrated to the United States in the early 1850s, first settling in Missouri. They moved to Illinois by 1857 and to Dodgeville, Iowa, WI, by 1870, though he died prior to 1870.}
\marriage{Samuel married \href{#}{\textcolor{accent}{\textbf{\underline{Ester.}}}}}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{William Williams was born about 1854 in Missouri}}}}}
\childentry{}{19 ii. Mary E. Williams}
\childentrylinked{--}{iii}{\href{#}{\textcolor{accent}{\textbf{\underline{Margaret Jennie Williams was born about 1860 in Illinois}}}}}
\dividerline

\entry{39}{Ester was born about 1832 in Wales.}{General Notes: In 1870-80, as a widow, she headed a household in Dodgeville, Iowa, WI, that included her children.}
\marriage{Ester married \href{#}{\textcolor{accent}{\textbf{\underline{Samuel Williams.}}}}}
\dividerline

\entry{48}{Paul Ehlers was born about 1838 in Schleswig-Holstein}{Germany. General Notes: In 1870, he lived in a boarding house in Davenport, Scott, IA, where he worked as a dealer in horses. In 1880, he lived in the household of G. Brainard in Davenport, where he worked as a servant. In 1885, he lived alone in Davenport, where he ran a small farm. In 1900, he lived as a boarder in the household of Amos Priester, where he worked on the latter's farm. In 1910, he lived alone as a boarder in Davenport, where he worked as a laborer at a saloon. His child was: 24 i. Johann Frederick "Fred" Ehlers}
\marriage{Paul married \href{#}{\textcolor{accent}{\textbf{\underline{someone.}}}}}
\dividerline

\entry{50}{Flavian De Mars}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Demers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Catherine Proteau}}}}, was born in Aug 1810 in Montreal, Quebec, Canada and died on 20 Jun 1903 in Balltown, Dubuque, IA, at age 92. General Notes: He and his family emigrated from Quebec, Canada, to Dubuque, Dubuque, IA, where in 1880 they lived. At that time, he worked as a millwright. Obituary: "An Old Settler Dies at Balltown: Flavian De Mars, a Nonogenarian and Well Known Citizen Laid to Rest" Mr. Flavian De Mars died last Saturday morning at 7:30 o'clock at the residence of his son-in-law, Mr. W. Fitzpatrick, at Balltown, Jefferson township. Death was due to the infirmities of old age. The remains were brought to this city [Dubuque] and taken to the establishment of Undertaker Walton from which the funeral took place at 9 o'clock this morning, under the auspices of Harmony Lodge, I. Q. O. F., No. 2, and who also conducted the services and furnished the pall bearers. The internment was in Linwood, where services were also held. Mr. De Mars was born in Montreal, Can., in August 1810, and was almost 93 years of age at the time of his demise. Leaving Montreal, he came direct to Dubuque fifty-five years ago [1848], and continued as a resident of this city until about four years ago, when he decided to spend the remainder of his days with his daughter at Balltown. Mr. De Mars was a millwright, and accounted one of the best in the northwest. He set up all of the machinery in the Pelan & Randall saw mill, the Dubuque Lumber company's mill, the Standard Lumber company's mill, the old Jaeger distillery, and he also put in the machinery in many mills throughout the northwest. Mr. De Mars was a well informed man and had a good reputation. He was warm-hearted and genial and always a true friend. His friendship was not a sham. It was of that kind which demonstrated itself in the hour of adversity and he never turned a deaf ear to the wail of distress. He was a man whose integrity was never doubted and whose was never smirched during his long and noble life. In the fullness of years, he has been called to enjoy the reward of a well spent life. He is survived by three daughters and two sons, Mrs. John Ellis of Holy Cross, Mrs. Margaret De Lisle of Dubuque, Mrs. Holder of Waterloo, Gus of Dubuque and Sol of Winona, Minn.; also by a brother in New York and a sister in Montreal.}
\marriage{Flavian married \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Audere}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Ulric Euder}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Morin}}}}.}
\childrenheading
\childentrylinked{25}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Adelaid Loretta De Mars}}}}}
\dividerline

\entry{51}{Marguerite Audere}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Ulric Euder}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Morin}}}}, was born on 12 Feb 1819 in Montreal, Quebec, Canada and died on 12 Feb 1899 in Peru Twp., Dubuque, IA, at age 80. General Notes: Obituary: "Sudden Death of One of the Oldest Residents of Sherrill's Mound" Friday morning, at 8 o'clock, death came suddenly and unexpectedly to one of the oldest and best known residents of Peru township, Mrs. Margaret De Mars, wife of Flavian De Mars. Mrs. De Mars was 85 years of age [sic], yet was as hale and hearty as many younger women. On Ash Wednesday she walked two and a half miles to the Catholic church, where she worshipped. Yesterday morning she got up early and prepared the breakfast as usual, and while at work clearing off the table fell, and when picked up was dead. Heart disease was given as the cause of death. Mr. and Mrs. De Mars have lived together as man and wife the long period of sixty-five years. Three sons and four daughters, all living in the county or near here, are left with the aged father to mourn this mother in Israel. She was born in Montreal, Canada, but for over sixty years has lived in Dubuque county. Mrs. Margaret F. De Lisle, of this city, is one of her daughters. The funeral will be on Sunday morning at 9 o'clock at the Catholic church in Sherrill's.}
\marriage{Marguerite married \href{#}{\textcolor{accent}{\textbf{\underline{Flavian De Mars}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Demers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Catherine Proteau}}}}.}
\dividerline

\entry{52}{Heinrich "Henry" Kamm}{son of \href{#}{\textcolor{accent}{\textbf{\underline{David Kamm}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaretha Meixmer}}}}, was born on 5 Dec 1842 in Steinreinach, Baden-Wuerttemberg, Germany and died on 9 Aug 1922 in Buena Vista, Clayton, IA, at age 79. General Notes: In 1880, he and his family ran a farm in Buena Vista, Clayton, IA. In 1900, they owned a farm there. Heinrich Bockel and Marie Margaretha "Maggie" Vogel.}
\marriage{Heinrich married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Margarethe "Mary" Bockel}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Philipp}}}}}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Robert Kamm was born on 18 Jan 1873 in Buena Vista, Clayton, IA}}}}}
\childentryplain{and died on 19 May 1960 in Dubuque}{ii}{, Dubuque, IA, at age 87.}
\childentrylinked{--}{iii}{\href{#}{\textcolor{accent}{\textbf{\underline{Emma Maria Wilhemina Kamm was born on 2 Nov 1875 in Buena Vista, Clayton, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on}}}}}
\childentryplain{25 Feb 1955 in Oelwein}{iv}{, Fayette, IA, at age 79.}
\childentrylinked{--}{v}{\href{#}{\textcolor{accent}{\textbf{\underline{Heinrich Christian "Henry" Kamm was born on 2 Feb 1877 in Buena Vista, Clayton, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died}}}}}
\childentryplain{on 19 Mar 1908 in Buena Vista}{vi}{, Clayton, IA, at age 31.}
\childentry{}{26 iv. Joseph Kamm}
\childentrylinked{--}{viii}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Dorothea "Mary" Kamm was born on 9 Apr 1883 in Buena Vista, Clayton, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on}}}}}
\childentryplain{18 Feb 1948 in Hazleton}{ix}{, Buchanan, IA, at age 64.}
\childentrylinked{--}{x}{\href{#}{\textcolor{accent}{\textbf{\underline{George Christopher Kamm was born on 13 Mar 1886 in Buena Vista, Clayton, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 28}}}}}
\childentryplain{May 1970 in Dubuque}{xi}{, Dubuque, IA, at age 84.}
\childentrylinked{--}{xii}{\href{#}{\textcolor{accent}{\textbf{\underline{Friedrich Gottlieb Kamm was born on 5 Aug 1888 in Buena Vista, Clayton, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died in Nov}}}}}
\childentryplain{1888 in Buena Vista}{xiii}{, Clayton, IA.}
\childentrylinked{--}{xiv}{\href{#}{\textcolor{accent}{\textbf{\underline{Louisa Katharina Kamm was born on 2 Dec 1890 in Buena Vista, Clayton, IA}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 10 May}}}}}
\childentryplain{1906 in Buena Vista}{xv}{, Clayton, IA, at age 15.}
\dividerline

\entry{53}{Marie Margarethe "Mary" Bockel}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Philipp Heinrich Bockel}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Margaretha "Maggie" Vogel}}}}, was born on 8 Dec 1847 in Schrondorf, Baden-Wuerttemberg, Germany and died on 23 Jan 1926 in Buena Vista, Clayton, IA, at age 78.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Heinrich "Henry" Kamm}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{David Kamm}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaretha Meixmer}}}}.}
\dividerline

\entry{54}{Belen Peter Machellack was born in May 1854 in Germany and died on 21 Aug 1907 in Lancaster}{Grant, WI, at age 53. General Notes: Obituary: Peter Machalleck [sic], formerly a resident of Cassville, died at the Grant county asylum August 21, after a week's illness. Deceased's wife and daughters Mary, Anna and Barbara, and sons Joe and George live at Michigan City, Ind. One daughter Mrs. Claude Dietrich lives in Cassville; she and her husband and Mrs. Alfred Dietrich and Miss Millie Bossert went to Lancaster Thursday to attend the funeral held that afternoon. Internment was in the asylum cemetery. Bajrovik.}
\marriage{Belen married \href{#}{\textcolor{accent}{\textbf{\underline{Amelia Jesse}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Andrei Jeosek}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne}}}}}
\childrenheading
\childentrylinked{27}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Mary Machellack}}}}}
\dividerline

\entry{55}{Amelia Jesse}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Andrei Jeosek}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Bajrovik}}}}, was born on 10 Jun 1852 in Strelitz, Kreis Kolmar, Posen, Germany and died on 18 Jan 1930 in Michigan City, La Porte, IN, at age 77.}
\marriage{Amelia married \href{#}{\textcolor{accent}{\textbf{\underline{Belen Peter Machellack.}}}}}
\dividerline

\entry{56}{Conrad Leik}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Andreas Heinrich "Andrew" Leik}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Elizabeth Fiedler}}}}, was born on 30 Jul 1845 in Darmstadt, Darmstadt, Hessen, Germany and died on 11 Oct 1923 in Dubuque, Dubuque, IA, at age 78. General Notes: In 1900, they rented a farm in Dubuque, Dubuque, IA. M. Pitcher, in Mar 1871.}
\marriage{Conrad married \href{#}{\textcolor{accent}{\textbf{\underline{Emmaline Shaffer}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Andrew Shaffer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Nancy}}}}}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Charles H}}}} Leik was born in Mar 1875 in Iowa.}
\childentrylinked{--}{ii}{\href{#}{\textcolor{accent}{\textbf{\underline{Anna E}}}} Leik was born on 19 Apr 1877 in Iowa and died on 27 Oct 1907, at age 30.}
\childentrylinked{--}{iii}{\href{#}{\textcolor{accent}{\textbf{\underline{Emily Leik was born in Sep 1879 in Iowa}}}}}
\childentry{}{28 iv. Edward Harvey Leik}
\childentrylinked{--}{v}{\href{#}{\textcolor{accent}{\textbf{\underline{Ella Leik was born in Jun 1883 in Iowa}}}}}
\childentrylinked{--}{vi}{\href{#}{\textcolor{accent}{\textbf{\underline{Carrie Leik was born on 7 May 1885 in Iowa}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died in Jun 1964, at age 79}}}}}
\childentrylinked{--}{vii}{\href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Leik was born in Nov 1888 in Iowa}}}}}
\childentrylinked{--}{viii}{\href{#}{\textcolor{accent}{\textbf{\underline{Bertha Leik was born in Feb 1893 in Iowa}}}}}
\dividerline

\entry{57}{Emmaline Shaffer}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Andrew Shaffer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Nancy M}}}}. Pitcher, was born on 25 Jun 1853 in North Beaver, Lawrence, PA and died on 22 Feb 1913 in Dubuque, Dubuque, IA, at age 59. Mar 1871.}
\marriage{Emmaline married \href{#}{\textcolor{accent}{\textbf{\underline{Conrad Leik}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Andreas Heinrich "Andrew" Leik}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Elizabeth Fiedler}}}}, in}
\dividerline

\entry{58}{William Howard Parker}{son of \href{#}{\textcolor{accent}{\textbf{\underline{William W}}}}. Parker and Mary Fry, was born on 21 Apr 1858 in Dubuque, Dubuque, IA and died on 4 Apr 1912 in Dubuque, Dubuque, IA, at age 53. Christina Puls, on 2 Jun 1886 in Sherrill, Dubuque, IA.}
\marriage{William married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Elizabeth Schaumburg}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Friedrich Ulrich Christoph Schaumburg and}}}}}
\childrenheading
\childentrylinked{29}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Ida May Parker}}}}}
\dividerline

\entry{59}{Anna Elizabeth Schaumburg}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Friedrich Ulrich Christoph Schaumburg}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Christina Puls}}}}, was born on 1 Nov 1865 in Rickardsville, Dubuque, IA and died on 11 Sep 1941 in Durango, Dubuque, IA, at age 75. Fry, on 2 Jun 1886 in Sherrill, Dubuque, IA.}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{William Howard Parker}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{William W}}}}. Parker and Mary}
\dividerline

\entry{60}{Christoph Jakob Muller}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Christoph Muller}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Julia Weis}}}}, was born on 2 Mar 1840 in Ernsbach, Hohenlohekreis, Baden-Wuerttemberg, Germany and died on 25 Mar 1929 in Dubuque, Dubuque, IA, at age 89. General Notes: In 1870, they rented land in Jefferson, Dubuque, IA, and had a personal estate of $350. In 1880, they ran a farm in Center, Dubuque, IA. This family is mentioned in the Luxemburger Gazette, a German-language newspaper based in Dubuque. Hellenschmitt and Elisabethe Charlotte Wild.}
\marriage{Christoph married \href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Christine Sofie Hellenschmitt}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Jakob}}}}}
\childrenheading
\childentrylinked{30}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Christian Frederick Miller}}}}}
\dividerline

\entry{61}{Charlotte Christine Sofie Hellenschmitt}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Jakob Hellenschmitt}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elisabethe Charlotte Wild}}}}, was born on 10 Mar 1837 in Ernsbach, Hohenlohekreis, Baden-Wuerttemberg, Germany and died in 1885 in Dubuque, Dubuque, IA, at age 48.}
\marriage{Charlotte married \href{#}{\textcolor{accent}{\textbf{\underline{Christoph Jakob Muller}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Christoph Muller}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Julia Weis}}}}.}
\dividerline

\entry{62}{Emil Anton Ospelt}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Anton Ospelt}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Magdalena Falk}}}}, was born in Mar 1852 in Austria and died on 2 Mar 1934 in Mountaindale, Washington, OR, at age 82. General Notes: In 1900, he and his family owned a farm in Mountaindale, Washington, OR. In 1910, they lived on East Dairy Creek Road, in Mountaindale, where he worked as a house carpenter. In 1920-30, they owned a farm there. Vaduz, Liechtenstein.}
\marriage{Emil married \href{#}{\textcolor{accent}{\textbf{\underline{Maria Ursula Taescher}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Taescher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Dorothea Krattli}}}}, on 6 Nov 1876 in}
\childrenheading
\childentrylinked{31}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Theresa Ospelt}}}}}
\dividerline

\entry{63}{Maria Ursula Taescher}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Taescher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Dorothea Krattli}}}}, was born on 18 Nov 1853 in Trimmis, Graubunden, Switzerland and died on 9 May 1930 in Mountaindale, Washington, OR, at age 76. Vaduz, Liechtenstein. Seventh Generation 64. John Rogers .}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Mary Ann George.}}}}}
\childrenheading
\childentrylinked{32}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{James Henry Rogers}}}}}
\dividerline

\entry{65}{Mary Ann George .}{}
\marriage{Mary married \href{#}{\textcolor{accent}{\textbf{\underline{John Rogers.}}}}}
\dividerline

\entry{66}{George Trewren Lean}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Lean Sr}}}}. and Elizabeth Ann Trewren, was born on 8 Dec 1810 in Camborne, Cornwall, England and died on 15 Mar 1869 in Rockland, Ontonagon, MI, at age 58. General Notes: He and his father appear in a criminal ledger in Cornwall, England, in 1835, when they faced trial for assault of a "peace officer." His father was acquitted, but George was sentenced to 3 months at the Bodmin Jail in Bodmin, Cornwall, England, and was released later that same year. In 1851, he and his family lived in Camborne, Cornwall, England, where he worked as a tin miner. They emigrated to the United States shortly afterward and settled in Wisconsin. in Camborne, Cornwall, England.}
\marriage{George married \href{#}{\textcolor{accent}{\textbf{\underline{Susanna Perry Jones}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Jones}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jenefer Jane Perry}}}}, on 9 May 1830}
\childrenheading
\childentrylinked{33}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Jane Lean}}}}}
\dividerline

\entry{67}{Susanna Perry Jones}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Jones}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jenefer Jane Perry}}}}, was born on 10 May 1812 in Gwinear, Cornwall, England and died on 7 Feb 1884 in Norway, Dickinson, MI, at age 71. 1830 in Camborne, Cornwall, England.}
\marriage{Susanna married \href{#}{\textcolor{accent}{\textbf{\underline{George Trewren Lean}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Lean Sr}}}}. and Elizabeth Ann Trewren, on 9 May}
\dividerline

\entry{68}{Franz Ruppert}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Peter Ruppert}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Schmit}}}}, was born about 1776 in Oberdonven, Grevenmacher, Luxembourg and died on 18 May 1836 in Oberdonven, Grevenmacher, Luxembourg, about age 60. Grevenmacher, Luxembourg.}
\marriage{Franz married \href{#}{\textcolor{accent}{\textbf{\underline{Claris Kieffer}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Peter Kieffer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Louisa}}}}, in Dec 1816 in Niederdonven,}
\childrenheading
\childentrylinked{34}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Nicholas Ruppert}}}}}
\dividerline

\entry{69}{Claris Kieffer}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Peter Kieffer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Louisa}}}}, was born on 20 Dec 1786 in Ellange, Remich, Luxembourg and died on 18 Nov 1826 in Oberdonven, Grevenmacher, Luxembourg, at age 39. Niederdonven, Grevenmacher, Luxembourg.}
\marriage{Claris married \href{#}{\textcolor{accent}{\textbf{\underline{Franz Ruppert}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Peter Ruppert}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Schmit}}}}, in Dec 1816 in}
\dividerline

\entry{70}{Peter Ley}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Ley}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catharina Wagner}}}}, was born on 1 Apr 1803 in Niederdonven, Grevenmacher, Luxembourg and died on 29 Aug 1876 in Union Mills, Iowa, WI, at age 73. Flaxweiler, Grevenmacher, Luxembourg.}
\marriage{Peter married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Reiff}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Wilhelmus Reiff}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Barbara Bastian}}}}, on 4 Apr 1827 in}
\childrenheading
\childentrylinked{35}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Margaretta Ley}}}}}
\dividerline

\entry{71}{Anna Maria Reiff}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Wilhelmus Reiff}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Barbara Bastian}}}}, was born on 10 Jul 1810 in Niederdonven, Grevenmacher, Luxembourg and died on 11 Feb 1880 in Union Mills, Iowa, WI, at age 69. Grevenmacher, Luxembourg.}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Peter Ley}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Ley}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catharina Wagner}}}}, on 4 Apr 1827 in Flaxweiler,}
\dividerline

\entry{74}{Thomas Jones .}{His child was: 37 i. Hannah Jones}
\marriage{Thomas married \href{#}{\textcolor{accent}{\textbf{\underline{someone.}}}}}
\dividerline

\entry{100}{Antoine Demers}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Amable Demers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Favreau}}}}, was born on 4 Nov 1785 in Chambly, Quebec, Canada and died in 1843, at age 58.}
\marriage{Antoine married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Catherine Proteau}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Proteau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elisabeth Benoit}}}}.}
\childrenheading
\childentrylinked{50}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Flavian De Mars}}}}}
\dividerline

\entry{101}{Marie Catherine Proteau}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Proteau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elisabeth Benoit}}}}, was born on 3 Sep 1791 in Chambly, Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Demers}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Amable Demers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Favreau}}}}.}
\dividerline

\entry{102}{Ulric Euder}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Christian Euder}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Benneger}}}}, was born on 13 Oct 1788 in Buchs, St. Gall, Switzerland and died in Quebec, Canada. 1822 in Chambly, Quebec, Canada.}
\marriage{Ulric married \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Morin}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Noel Morin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Louise Panneton}}}}, on 29 Oct}
\childrenheading
\childentrylinked{51}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Audere}}}}}
\dividerline

\entry{103}{Marguerite Morin}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Noel Morin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Louise Panneton}}}}, was born about 1800 in Quebec, Canada and died on 12 May 1860 in St. Didace, Quebec, Canada, about age 60. Quebec, Canada.}
\marriage{Marguerite married \href{#}{\textcolor{accent}{\textbf{\underline{Ulric Euder}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Christian Euder}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Benneger}}}}, on 29 Oct 1822 in Chambly,}
\dividerline

\entry{104}{David Kamm}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Heinrich Kamm}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Kohler}}}}, was born on 15 Jul 1799 in Steinreinach, Baden-Wuerttemberg, Germany and died on 18 Mar 1863 in Steinreinach, Baden-Wuerttemberg, Germany, at age 63. 1828 in Korb, Wuerttemberg, Germany.}
\marriage{David married \href{#}{\textcolor{accent}{\textbf{\underline{Margaretha Meixmer}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Meixmer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Catharina}}}}, on 5 Oct}
\childrenheading
\childentrylinked{52}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Heinrich "Henry" Kamm}}}}}
\dividerline

\entry{105}{Margaretha Meixmer}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Meixmer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Catharina}}}}, was born on 31 Mar 1798 in Baden-Wuerttemberg, Germany and died on 4 Jun 1838 in Steinreinach, Baden-Wuerttemberg, Germany, at age 40. Wuerttemberg, Germany.}
\marriage{Margaretha married \href{#}{\textcolor{accent}{\textbf{\underline{David Kamm}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Heinrich Kamm}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Kohler}}}}, on 5 Oct 1828 in Korb,}
\dividerline

\entry{106}{Philipp Heinrich Bockel}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Adam Bockel}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catharina Magdalena Heumajer}}}}, was born on 6 Jul 1795 in Schrondorf, Baden-Wuerttemberg, Germany and died on 24 Jun 1848 in Schrondorf, Baden- Wuerttemberg, Germany, at age 52. Lutz, on 12 Apr 1842 in Schrondorf, Baden-Wuerttemberg, Germany.}
\marriage{Philipp married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Margaretha "Maggie" Vogel}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Christian Gottlob Vogel}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Sara}}}}}
\childrenheading
\childentrylinked{53}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Margarethe "Mary" Bockel}}}}}
\dividerline

\entry{107}{Marie Margaretha "Maggie" Vogel}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Christian Gottlob Vogel}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Sara Lutz}}}}, was born on 6 Dec 1815 in Oppenweiler, Baden-Wuerttemberg, Germany and died on 30 Aug 1874 in Waupeton, Clayton, IA, at age 58. Heumajer, on 12 Apr 1842 in Schrondorf, Baden-Wuerttemberg, Germany.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Philipp Heinrich Bockel}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Adam Bockel}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catharina Magdalena}}}}}
\dividerline

\entry{110}{Andrei Jeosek was born about 1815 in Germany.}{}
\marriage{Andrei married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Bajrovik.}}}}}
\childrenheading
\childentrylinked{55}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Amelia Jesse}}}}}
\dividerline

\entry{111}{Marie Anne Bajrovik was born in May 1815 in Germany and died in 1910 in La Porte Co.}{IN, at age 95.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Andrei Jeosek.}}}}}
\dividerline

\entry{112}{Andreas Heinrich "Andrew" Leik}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Konrad Leik}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Eichenauer}}}}, was born on 27 Apr 1813 in Darmstadt, Darmstadt, Hessen, Germany and died on 30 Apr 1871 in Yorkana, York, PA, at age 58. General Notes: In 1880, they lived in Lower Windsor, York, PA, where he worked as a shoemaker.}
\marriage{Andreas married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Elizabeth Fiedler.}}}}}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Henry B}}}} Leik was born on 9 Jan 1844 in Darmstadt, Darmstadt, Hessen, Germany and died on 14}
\childentryplain{May 1914 in Yorkana}{ii}{, York, PA, at age 70.}
\childentry{}{56 ii. Conrad Leik}
\dividerline

\entry{113}{Anna Elizabeth Fiedler was born on 3 Nov 1805 in Darmstadt}{Darmstadt, Hessen, Germany and died on 15 Nov 1884 in Yorkana, York, PA, at age 79.}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Andreas Heinrich "Andrew" Leik}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Konrad Leik}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Eichenauer}}}}.}
\dividerline

\entry{114}{Andrew Shaffer}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Christopher Shaffer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth}}}}, was born about 1807 in Martinsburg, Berkeley, WV and died on 9 Feb 1883, about age 76. General Notes: In 1850, he and his family lived in North Beaver, Lawrence, PA, where he worked as a laborer. In 1860, they owned a farm there worth $3500 and had a personal estate of $600, which shows that they were fairly successful for the time. They continued to farm there in 1870 with a farm worth $4000 and a personal estate of $1000 showing that they had continued success. In 1880, they lived in Moravia, Lawrence, PA, where he worked as a laborer.}
\marriage{Andrew married \href{#}{\textcolor{accent}{\textbf{\underline{Nancy M. Pitcher}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Michael K}}}}. Pitzer and Catherine Boshaar.}
\childrenheading
\childentrylinked{57}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Emmaline Shaffer}}}}}
\dividerline

\entry{115}{Nancy M. Pitcher}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Michael K}}}}. Pitzer and Catherine Boshaar, was born about 1813 in Pennsylvania and died on 15 Sep 1886, about age 73.}
\marriage{Nancy married \href{#}{\textcolor{accent}{\textbf{\underline{Andrew Shaffer}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Christopher Shaffer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth}}}}.}
\dividerline

\entry{116}{William W. Parker}{son of \href{#}{\textcolor{accent}{\textbf{\underline{George A}}}}. Parker and Susanna Hawley, was born about 1830 in Austinville, Wythe, VA and died on 17 May 1916 in Dubuque, Dubuque, IA, about age 86. General Notes: In 1860, he and his family lived in Julien, Dubuque, IA, where he worked as a miner. In 1880, they lived in Center, Dubuque, IA, where he continued in the same line of work. 1850 in Wythe Co., VA.}
\marriage{William married \href{#}{\textcolor{accent}{\textbf{\underline{Mary Fry}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Zinnara Surratt "Zimery" Fry}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Hannah Walton}}}}, on 9 Nov}
\childrenheading
\childentrylinked{58}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{William Howard Parker}}}}}
\dividerline

\entry{117}{Mary Fry}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Zinnara Surratt "Zimery" Fry}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Hannah Walton}}}}, was born in May 1827 in Virginia and died in Dubuque, Dubuque, IA. Co., VA.}
\marriage{Mary married \href{#}{\textcolor{accent}{\textbf{\underline{William W. Parker}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{George A}}}}. Parker and Susanna Hawley, on 9 Nov 1850 in Wythe}
\dividerline

\entry{118}{Friedrich Ulrich Christoph Schaumburg}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Christian Gotthard Schaumburg}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Sophie Catherine Elizabeth Ohde}}}}, was born on 18 Nov 1813 in Perlin, Mecklenburg-Schwerin, Germany and died on 24 Sep 1891 in Dubuque Co., IA, at age 77. General Notes: In 1860, he and his family owned a farm in Jefferson, Dubuque, IA, worth $600 and had a personal estate of $170. In 1870, their farm there was worth $1600 and they had a personal estate of $600, indicating they had been successful in developing their farmland. They continued to farm there in 1880.}
\marriage{Friedrich married \href{#}{\textcolor{accent}{\textbf{\underline{Christina Puls.}}}}}
\childrenrenheading
\childentrylinked{59}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Anna Elizabeth Schaumburg}}}}}
\childentryplain{119. Christina Puls was born about 1829 in Grabnitz}{ii}{, Ludwiglust-Parchim, Mecklenburg-Vorpommern, Germany}
\childentryplain{and died on 17 May 1891 in Dubuque Co.}{iii}{, IA, about age 62.}
\childentryplain{Christina married Friedrich Ulrich Christoph Schaumburg}{iv}{, son of Johann Christian Gotthard}
\childentry{}{Schaumburg and Sophie Catherine Elizabeth Ohde.}
\dividerline

\entry{120}{Christoph Muller}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Christoph Muller}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Eva Maria Gengenbach}}}}, was born on 17 Sep 1815 in Haugstatt, Baden-Wuerttemberg, Germany and died on 2 Jul 1871 in Haugstatt, Baden-Wuerttemberg, Germany, at age 55.}
\marriage{Christoph married \href{#}{\textcolor{accent}{\textbf{\underline{Julia Weis.}}}}}
\childrenheading
\childentrylinked{60}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Christoph Jakob Muller}}}}}
\dividerline

\entry{121}{Julia Weis was born on 5 Mar 1821 in Baden-Wuerttemberg}{Germany and died on 11 Jan 1898 in Baden- Wuerttemberg, Germany, at age 76.}
\marriage{Julia married \href{#}{\textcolor{accent}{\textbf{\underline{Christoph Muller}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Christoph Muller}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Eva Maria Gengenbach}}}}.}
\dividerline

\entry{122}{Johann Georg Jakob Hellenschmitt}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Matthaus Hellenschmitt}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaretha Barbara Schmitz}}}}, was born on 23 Aug 1807 in Ernsbach, Hohenlohekreis, Baden-Wuerttemberg, Germany and died on 9 Dec 1870 in Germany, at age 63. Katharine Mohler, on 18 Feb 1835 in Ernsbach, Hohenlohekreis, Baden-Wuerttemberg, Germany.}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Elisabethe Charlotte Wild}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Christian Eberhardt Wild}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Christiane}}}}}
\childrenheading
\childentrylinked{61}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Christine Sofie Hellenschmitt}}}}}
\dividerline

\entry{123}{Elisabethe Charlotte Wild}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Christian Eberhardt Wild}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Christiane Katharine Mohler}}}}, was born on 13 Aug 1812 in Ernsbach, Hohenlohekreis, Baden-Wuerttemberg, Germany and died on 4 Feb 1875 in Germany, at age 62. Margaretha Barbara Schmitz, on 18 Feb 1835 in Ernsbach, Hohenlohekreis, Baden-Wuerttemberg, Germany.}
\marriage{Elisabethe married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Jakob Hellenschmitt}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Matthaus Hellenschmitt and}}}}}
\dividerline

\entry{124}{Joseph Anton Ospelt}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Anton Ospelt}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Magdalena Rheinburger}}}}, was born on 12 Oct 1825 in Vaduz, Liechtenstein.}
\marriage{Joseph married \href{#}{\textcolor{accent}{\textbf{\underline{Magdalena Falk.}}}}}
\childrenheading
\childentrylinked{62}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Emil Anton Ospelt}}}}}
\dividerline

\entry{125}{Magdalena Falk was born on 19 Jul 1829 in Schaan}{Liechtenstein.}
\marriage{Magdalena married \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Anton Ospelt}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Anton Ospelt}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Magdalena Rheinburger}}}}.}
\dividerline

\entry{126}{Johann Taescher was born on 28 Nov 1815 in Switzerland.}{}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Dorothea Krattli}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Christian Krattli}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Ursula Groll}}}}.}
\childrenheading
\childentrylinked{63}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Maria Ursula Taescher}}}}}
\dividerline

\generationtitle{Eighth Generation}
\entry{127}{Dorothea Krattli}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Christian Krattli}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Ursula Groll}}}}, was born on 4 Apr 1819 in Switzerland.}
\marriage{Dorothea married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Taescher.}}}}}

\entry{132}{Joseph Lean Sr. son of Stephen Lean Jr. and Mary Sarah Varley}{was born on 5 Aug 1781 in Camborne, Cornwall, England and died on 13 Jul 1847 in Mineral Point, Iowa, WI, at age 65. General Notes: He and his son, George, faced trial on Apr 7, 1835, with the charges of assault of a "peace officer." He was acquitted, but George was sentenced to 3 months in prison. This may have played a role in the family leaving Cornwall. He emigrated to the United States and settled in what was then, Wisconsin Territory. Joseph and his family appear there in the 1840 census with a household that included: 1 male under age 5, 1 male age 15-19, 1 male age 20-29, 1 male age 50-59, 1 female age 20-29, and 1 female age 50-59. Three people, including Joseph, were employed as miners. [Wisconsin Tribune, Nov 10, 1848]: He was murdered in Mineral Point, WI, July 13, 1847, in the grocery of William Terrell. According to an eye witness who testified in court, he overheard a conversation between Lean and the assailant David J. Odell: Odell: You are a damned imposter and a thief! Lean: How can you prove that? Odell: I have a mind to cut your damn guts out. Lean: Cut away and be damned! "The witness said he next heard the rocks and gravel rattle as Odell made a plunge with the knife, and Lean cried, 'O murder!' He was well acquainted with both and knew their voices; got up immediately and went to the window; saw Lean going toward's Terrell's grocery and Odell towards Col. Nichol's bar room door; witness went down immediately, went out the bar room door, and went over to Terrell's grocery; saw a man holding Lean, and Samuel Terrell holding a wound in Lean's thigh." Joseph was thus killed when his femoral artery was cut in two by a large knife. Odell was sentenced to six years confinement and hard labor in the State Prison for manslaughter for the crime. Gov. Dewey (of Wisconsin) pardoned Odell of the crime in late 1850 [Wisconsin Tribune, Nov 24, 1848; Potosi Republican, Dec 14, 1848; The Telegraph- Courier, Kenosha, Dec 27, 1850]. in Camborne, Cornwall, England.}
\marriage{Joseph married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Ann Trewren}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{George Trewren}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Hall}}}}, on 30 Mar 1807}
\childrenrenheading
\childentrylinked{66}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{George Trewren Lean}}}}}
\childentrylinked{--}{ii}{\href{#}{\textcolor{accent}{\textbf{\underline{Joseph Lean was born on 3 Oct 1812 in Camborne, Cornwall, England}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 21 Apr 1815 in}}}}}
\childentryplain{Camborne}{iii}{, Cornwall, England, at age 2.}
\childentrylinked{--}{iv}{\href{#}{\textcolor{accent}{\textbf{\underline{Catherine Lean was born on 30 Jul 1814 in Camborne, Cornwall, England}}}}}
\childentrylinked{--}{v}{\href{#}{\textcolor{accent}{\textbf{\underline{Jane Lean was born in Cornwall, England}}}}}
\childentrylinked{--}{vi}{\href{#}{\textcolor{accent}{\textbf{\underline{Joseph Lean Jr}}}} was born on 23 Mar 1816 in Camborne, Cornwall, England and died on 15 Mar}
\childentryplain{1869 in Rockland}{vii}{, Ontonagon, MI, at age 52.}
\childentrylinked{--}{viii}{\href{#}{\textcolor{accent}{\textbf{\underline{John Lean was born on 9 Sep 1820 in Cornwall, England}}}}}
\childentrylinked{--}{ix}{\href{#}{\textcolor{accent}{\textbf{\underline{Robert Trewren Lean was born on 4 May 1822 in Camborne, Cornwall, England}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died in}}}}}
\childentry{}{Wisconsin.}
\childentrylinked{--}{xi}{\href{#}{\textcolor{accent}{\textbf{\underline{William Henry Lean was born on 2 Jul 1825 in Camborne, Cornwall, England}}}}}
\childentrylinked{--}{xii}{\href{#}{\textcolor{accent}{\textbf{\underline{William Lean was born on 6 Jun 1828 in Camborne, Cornwall, England}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 3 Jul 1882 in}}}}}
\childentryplain{Shasta Co.}{xiii}{, CA, at age 54.}
\dividerline

\entry{133}{Elizabeth Ann Trewren}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{George Trewren}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Hall}}}}, was born on 21 Mar 1782 in Ludgvan, Cornwall, England and died after 1842 in Mineral Point, Iowa, WI. Camborne, Cornwall, England.}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Lean Sr.}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Stephen Lean Jr}}}}. and Mary Sarah Varley, on 30 Mar 1807 in}
\dividerline

\entry{134}{Richard Jones was born about 1766 in Gwinear}{Cornwall, England and died in Dec 1846 in Roseworthy, Cornwall, England, about age 80. Gwinear, Cornwall, England.}
\marriage{Richard married \href{#}{\textcolor{accent}{\textbf{\underline{Jenefer Jane Perry}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Perry}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Pascha Rutter}}}}, on 5 Dec 1789 in}
\childrenheading
\childentrylinked{67}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Susanna Perry Jones}}}}}
\dividerline

\entry{135}{Jenefer Jane Perry}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Perry}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Pascha Rutter}}}}, was born about 1772 in Sithney, Cornwall, England and died in Jan 1857 in Truro, Cornwall, England, about age 85.}
\marriage{Jenefer married \href{#}{\textcolor{accent}{\textbf{\underline{Richard Jones on 5 Dec 1789 in Gwinear}}}}, Cornwall, England.}
\dividerline

\entry{136}{Johann Peter Ruppert was born on 12 May 1742 in Oberdonven}{Grevenmacher, Luxembourg and died on 2 Jan 1829 in Oberdonven, Grevenmacher, Luxembourg, at age 86.}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Schmit}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Theodore Diderich Schmit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Muller}}}}.}
\childrenheading
\childentrylinked{68}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Franz Ruppert}}}}}
\dividerline

\entry{137}{Margaret Schmit}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Theodore Diderich Schmit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Muller}}}}, died on 13 Jan 1809 in Oberdonven, Grevenmacher, Luxembourg.}
\marriage{Margaret married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Peter Ruppert.}}}}}
\dividerline

\entry{138}{Peter Kieffer .}{}
\marriage{Peter married \href{#}{\textcolor{accent}{\textbf{\underline{Louisa.}}}}}
\childrenrenheading
\childentrylinked{69}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Claris Kieffer}}}}}
\childentry{}{139. Louisa .}
\childentry{}{Louisa married Peter Kieffer.}
\dividerline

\entry{140}{Nicolas Ley .}{}
\marriage{Nicolas married \href{#}{\textcolor{accent}{\textbf{\underline{Catharina Wagner.}}}}}
\childrenheading
\childentrylinked{70}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Peter Ley}}}}}
\dividerline

\entry{141}{Catharina Wagner .}{}
\marriage{Catharina married \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Ley.}}}}}
\dividerline

\entry{142}{Wilhelmus Reiff}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Peter Reiff}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Susanna Ludwig}}}}, was born on 17 Sep 1778 in Niederdonven, Grevenmacher, Luxembourg and died on 15 Mar 1851 in Belgium, Ozaukee, WI, at age 72. Niederdonven, Grevenmacher, Luxembourg.}
\marriage{Wilhelmus married \href{#}{\textcolor{accent}{\textbf{\underline{Barbara Bastian}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Peter Bastian}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Holtz}}}}, on 7 Jan 1805 in}
\childrenheading
\childentrylinked{71}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Reiff}}}}}
\dividerline

\entry{143}{Barbara Bastian}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Peter Bastian}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Holtz}}}}, was born about 1788 in Rehlingen, Saarlouis, Saarland, Germany and died on 17 Feb 1830 in Niederdonven, Grevenmacher, Luxembourg, about age 42. Grevenmacher, Luxembourg.}
\marriage{Barbara married \href{#}{\textcolor{accent}{\textbf{\underline{Wilhelmus Reiff}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Peter Reiff}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Susanna Ludwig}}}}, on 7 Jan 1805 in Niederdonven,}
\dividerline

\entry{200}{Joseph Amable Demers}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Demers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Josephe Larocque}}}}, was born on 4 Jan 1750 in Chambly, Quebec, Canada and died on 3 Jun 1800 in Chambly, Quebec, Canada, at age 50.}
\marriage{Joseph married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Favreau}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Simon Favreau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Jeanne Banlier}}}}.}
\childrenheading
\childentrylinked{100}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Antoine Demers}}}}}
\dividerline

\entry{201}{Marie Anne Favreau}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Simon Favreau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Jeanne Banlier}}}}, was born on 25 Oct 1750 in Chambly, Quebec, Canada and died on 12 Jul 1809 in Chambly, Quebec, Canada, at age 58.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Amable Demers}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Demers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Josephe Larocque}}}}.}
\dividerline

\entry{202}{Jean Baptiste Proteau}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Proteau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Bruneau}}}}, was born on 26 Sep 1736 in Charlesbourg, Quebec, Canada and died on 6 Feb 1810 in Chambly, Quebec, Canada, at age 73. Chambly, Quebec, Canada.}
\marriage{Jean married \href{#}{\textcolor{accent}{\textbf{\underline{Elisabeth Benoit}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Louis Benoit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Reine Lavoie}}}}, on 8 Apr 1788 in}
\childrenrenheading
\childentrylinked{101}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Catherine Proteau}}}}}
\childentryplain{203. Elisabeth Benoit}{ii}{, daughter of Louis Benoit and Marie Reine Lavoie, was born on 2 Apr 1770 in Chambly,}
\childentryplain{Quebec}{iii}{, Canada and died on 22 Jul 1817 in Chambly, Quebec, Canada, at age 47.}
\childentryplain{Elisabeth married Jean Baptiste Proteau}{iv}{, son of Jean Baptiste Proteau and Marie Madeleine Bruneau, on}
\childentryplain{8 Apr 1788 in Chambly}{v}{, Quebec, Canada.}
\dividerline

\entry{204}{Christian Euder was born in Switzerland.}{}
\marriage{Christian married \href{#}{\textcolor{accent}{\textbf{\underline{Anne Benneger.}}}}}
\childrenheading
\childentrylinked{102}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Ulric Euder}}}}}
\dividerline

\entry{205}{Anne Benneger .}{}
\marriage{Anne married \href{#}{\textcolor{accent}{\textbf{\underline{Christian Euder.}}}}}
\dividerline

\entry{206}{Pierre Noel Morin}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Maurice Morin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Josephte Miville}}}}, was born on 17 Feb 1769 in Terrebonne, Les Moulins, Quebec, Canada and died on 20 Apr 1850 in St. Jean, Ile d'Orleans, Quebec, Canada, at age}
\dividerline

\entry{81}{Pierre married Marie Louise Panneton}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Amable Panneton}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Josephe Landry}}}}, on 15 Jul 1794 in L'Assomption, Quebec, Canada.}
\childrenheading
\childentrylinked{103}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Morin}}}}}
\dividerline

\entry{207}{Marie Louise Panneton}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Amable Panneton}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Josephe Landry}}}}, was born in 1775 in Repentigny, Assomption, Quebec, Canada. in L'Assomption, Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Noel Morin}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Maurice Morin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Josephte Miville}}}}, on 15 Jul 1794}
\dividerline

\entry{208}{Heinrich Kamm}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Heinrich Kamm}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Barbara Schlegel}}}}, was born on 3 Oct 1750 in Steinreinach, Baden-Wuerttemberg, Germany and died on 10 Feb 1808 in Steinreinach, Baden-Wuerttemberg, Germany, at age 57. Ohmden, Baden-Wuerttemberg, Germany.}
\marriage{Heinrich married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Kohler}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Martin Kohler}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth}}}}, on 7 Mar 1776 in}
\childrenheading
\childentrylinked{104}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{David Kamm}}}}}
\dividerline

\entry{209}{Anna Maria Kohler}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Martin Kohler}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth}}}}, was born about 1752 in Ohmden, Baden- Wuerttemberg, Germany and died on 10 Jan 1792 in Steinreinach, Baden-Wuerttemberg, Germany, about age 40. Baden-Wuerttemberg, Germany.}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Heinrich Kamm}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Heinrich Kamm}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Barbara Schlegel}}}}, on 7 Mar 1776 in Ohmden,}
\dividerline

\entry{210}{Johann Georg Meixmer .}{}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Catharina.}}}}}
\childrenheading
\childentrylinked{105}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Margaretha Meixmer}}}}}
\dividerline

\entry{211}{Anna Catharina .}{}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Meixmer.}}}}}
\dividerline

\entry{212}{Johann Adam Bockel}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Adam Bockel}}}}, was born on 28 May 1752 in Schrondorf, Baden- Wuerttemberg, Germany and died on 19 Feb 1828 in Schrondorf, Baden-Wuerttemberg, Germany, at age 75. Catharina Rothfuss, on 21 Nov 1776.}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Catharina Magdalena Heumajer}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Leonhard Heumajer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria}}}}}
\childrenheading
\childentrylinked{106}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Philipp Heinrich Bockel}}}}}
\dividerline

\entry{213}{Catharina Magdalena Heumajer}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Leonhard Heumajer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Catharina Rothfuss}}}}, was born on 23 Dec 1765 in Schrondorf, Baden-Wuerttemberg, Germany and died on 15 Apr 1834 in Schrondorf, Baden-Wuerttemberg, Germany, at age 68.}
\marriage{Catharina married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Adam Bockel}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Adam Bockel}}}}, on 21 Nov 1776.}
\dividerline

\entry{214}{Christian Gottlob Vogel}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Heinrich Vogel}}}}, was born about 1790 in Germany and died on 20 Nov 1856, about age 66.}
\marriage{Christian married \href{#}{\textcolor{accent}{\textbf{\underline{Maria Sara Lutz.}}}}}
\childrenheading
\childentrylinked{107}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Margaretha "Maggie" Vogel}}}}}
\dividerline

\entry{215}{Maria Sara Lutz was born about 1790 in Germany.}{}
\marriage{Maria married \href{#}{\textcolor{accent}{\textbf{\underline{Christian Gottlob Vogel}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Heinrich Vogel}}}}.}
\dividerline

\entry{224}{Konrad Leik}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Leik}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Marie Schmidt}}}}, was born on 25 Nov 1789 in Angersbach, Vogelsbergkreis, Hessen, Germany and died on 7 May 1831 in Angersbach, Vogelsbergkreis, Hessen, Germany, at age}
\dividerline

\entry{41}{Konrad married Anna Maria Eichenauer}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Eichenauer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Margaretha Rausch}}}}, on 22 Dec 1816 in Angersbach, Vogelsbergkreis, Hessen, Germany.}
\childrenheading
\childentrylinked{112}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Andreas Heinrich "Andrew" Leik}}}}}
\dividerline

\entry{225}{Anna Maria Eichenauer}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Eichenauer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Margaretha Rausch}}}}, was born on 5 Feb 1793 in Angersbach, Vogelsbergkreis, Hessen, Germany and died in Pennsylvania. Angersbach, Vogelsbergkreis, Hessen, Germany. 228. Christopher Shaffer, son of \href{#}{\textcolor{accent}{\textbf{\underline{Martin Shaffer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Barbara}}}}, was born in 1785 in Martinsburg, Berkeley, WV and died in 1857 in Beaver City, Beaver, PA, at age 72.}
\marriage{Christopher married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth.}}}}}
\childrenheading
\childentrylinked{114}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Andrew Shaffer}}}}}
\dividerline

\entry{229}{Elizabeth died on 6 Sep 1857 in Beaver Co.}{PA.}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{Christopher Shaffer}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Martin Shaffer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Barbara}}}}.}
\dividerline

\entry{230}{Michael K. Pitzer}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Michael Pitzer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Sophia Scharlotta Boshaar}}}}, was born in 1756 and died on 22 Jun 1847 in North Beaver, Lawrence, PA, at age 91. General Notes: In 1800, he and his family lived in Earl Twp., Lancaster, PA. In 1810, they lived in Berkeley Co., WV. In 1820, they ran a farm in Middletown, Berkeley, WV. In 1830, they lived in North Beaver, Lawrence, PA. In 1840, they lived in Berkeley Co., WV, where at least one member of the family was engaged in some kind of manufacturing or trade. Mar 1794 in Berkeley Co., WV.}
\marriage{Michael married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Boshaar}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Balthazar Boshaar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Johanna Dorothea Weider}}}}, on 11}
\childrenheading
\childentrylinked{115}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Nancy M. Pitcher}}}}}
\dividerline

\entry{231}{Catherine Boshaar}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Balthazar Boshaar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Johanna Dorothea Weider}}}}, was born in 1760 in Lancaster, Lancaster, PA and died on 12 Feb 1827 in Berkeley Co., WV, at age 67. 1794 in Berkeley Co., WV.}
\marriage{Catherine married \href{#}{\textcolor{accent}{\textbf{\underline{Michael K. Pitzer}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Michael Pitzer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Sophia Scharlotta Boshaar}}}}, on 11 Mar}
\dividerline

\entry{232}{George A. Parker was born about 1800 in Wythe Co.}{VA. General Notes: In 1850, he and his family lived in Wythe Co., VA, where he worked as a laborer.}
\marriage{George married \href{#}{\textcolor{accent}{\textbf{\underline{Susanna Hawley on 25 Jul 1816 in Harrison Co.}}}}, WV.}
\childrenheading
\childentrylinked{116}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{William W. Parker}}}}}
\dividerline

\entry{233}{Susanna Hawley was born about 1805 in Lead Mines}{Wythe, VA.}
\marriage{Susanna married \href{#}{\textcolor{accent}{\textbf{\underline{George A. Parker on 25 Jul 1816 in Harrison Co.}}}}, WV.}
\dividerline

\entry{234}{Zinnara Surratt "Zimery" Fry}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Zinnara Fry}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Valentine}}}}, was born about 1797 in North Carolina and died in 1860 in Claiborne Co., TN, about age 63. General Notes: In 1820, he and his family lived in Evesham, Surry, VA, where they ran a farm.}
\marriage{Zinnara married \href{#}{\textcolor{accent}{\textbf{\underline{Hannah Walton}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{George Walton}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Parkin}}}}.}
\childrenheading
\childentrylinked{117}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Mary Fry}}}}}
\dividerline

\entry{235}{Hannah Walton}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{George Walton}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Parkin}}}}, was born in 1799 in England and died in Wythe Co., VA.}
\marriage{Hannah married \href{#}{\textcolor{accent}{\textbf{\underline{Zinnara Surratt "Zimery" Fry}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Zinnara Fry}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Valentine}}}}.}
\dividerline

\entry{236}{Johann Christian Gotthard Schaumburg}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Christoph Schaumburg}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Christina Homann}}}}, was born on 24 Nov 1781 in Buelow, Mecklenburg-Vorpommern, Germany and died on 13 Feb 1860 in Warlitz, Mecklenburg-Schwerin, Germany, at age 78. Catharina, on 1 Jul 1813 in Schwerin, Mecklenburg-Schwerin, Germany.}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Sophie Catherine Elizabeth Ohde}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Christian Ohde}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Sophia}}}}}
\childrenheading
\childentrylinked{118}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Friedrich Ulrich Christoph Schaumburg}}}}}
\dividerline

\entry{237}{Sophie Catherine Elizabeth Ohde}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Christian Ohde}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Sophia Catharina}}}}, was born on 1 Oct 1791 and died on 24 Oct 1816 in Muehlen Eichsen, Mecklenburg-Schwerin, Germany, at age 25. Christina Homann, on 1 Jul 1813 in Schwerin, Mecklenburg-Schwerin, Germany.}
\marriage{Sophie married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Christian Gotthard Schaumburg}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Christoph Schaumburg}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria}}}}}
\dividerline

\entry{240}{Christoph Muller}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Michael Muller}}}}, was born about 1780 in Cramonshagen, Mecklenburg- Vorpommern, Germany.}
\marriage{Christoph married \href{#}{\textcolor{accent}{\textbf{\underline{Eva Maria Gengenbach}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Michael Gengenbach}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Regina Keppler}}}}.}
\childrenheading
\childentrylinked{120}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Christoph Muller}}}}}
\dividerline

\entry{241}{Eva Maria Gengenbach}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Michael Gengenbach}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Regina Keppler}}}}, was born on 13 Jan 1794 in Haugstatt, Baden-Wuerttemberg, Germany and died on 28 Nov 1835 in Haugstatt, Baden-Wuerttemberg, Germany, at age 41.}
\marriage{Eva married \href{#}{\textcolor{accent}{\textbf{\underline{Christoph Muller}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Michael Muller}}}}.}
\dividerline

\entry{244}{Johann Matthaus Hellenschmitt}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johannes Hellenschmitt}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaretha Barbara Albrecht}}}}, was born on 2 Jun 1764 in Baden-Wuerttemberg, Germany and died on 26 May 1819 in Baden-Wuerttemberg, Germany, at age 54. Meisen.}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Margaretha Barbara Schmitz}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Peter Schmitz}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria}}}}}
\childrenheading
\childentrylinked{122}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Jakob Hellenschmitt}}}}}
\dividerline

\entry{245}{Margaretha Barbara Schmitz}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Peter Schmitz}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Meisen}}}}, died on 8 Mar 1837 in Kreis Cochem-Zell, Rheinland-Pfalz, Germany. Barbara Albrecht. 246. Christian Eberhardt Wild, son of \href{#}{\textcolor{accent}{\textbf{\underline{Eberhard Wild}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elisabethe Diez}}}}, was born on 30 Oct 1767 in Jagsthausen, Heilbronn, Baden-Wuerttemberg, Germany and died on 16 Dec 1820 in Ernsbach, Hohenlohekreis, Baden-Wuerttemberg, Germany, at age 53. Edelmann, on 9 May 1810 in Ernsbach, Hohenlohekreis, Baden-Wuerttemberg, Germany.}
\marriage{Christian married \href{#}{\textcolor{accent}{\textbf{\underline{Christiane Katharine Mohler}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Michael Mohler}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Charlotte}}}}}
\childrenheading
\childentrylinked{123}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elisabethe Charlotte Wild}}}}}
\dividerline

\entry{247}{Christiane Katharine Mohler}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Michael Mohler}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Charlotte Edelmann}}}}, was born on 6 Feb 1780 in Ernsbach, Hohenlohekreis, Baden-Wuerttemberg, Germany and died on 31 Jul 1840, at age 60. in Ernsbach, Hohenlohekreis, Baden-Wuerttemberg, Germany.}
\marriage{Christiane married \href{#}{\textcolor{accent}{\textbf{\underline{Christian Eberhardt Wild}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Eberhard Wild}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elisabethe Diez}}}}, on 9 May 1810}
\dividerline

\entry{248}{Joseph Anton Ospelt .}{}
\marriage{Joseph married \href{#}{\textcolor{accent}{\textbf{\underline{Magdalena Rheinburger.}}}}}
\childrenheading
\childentrylinked{124}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Joseph Anton Ospelt}}}}}
\dividerline

\entry{249}{Magdalena Rheinburger .}{}
\marriage{Magdalena married \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Anton Ospelt.}}}}}
\dividerline

\entry{254}{Christian Krattli .}{}
\marriage{Christian married \href{#}{\textcolor{accent}{\textbf{\underline{Ursula Groll.}}}}}
\childrenheading
\childentrylinked{127}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Dorothea Krattli}}}}}
\dividerline

\generationtitle{Ninth Generation}
\entry{255}{Ursula Groll .}{}
\marriage{Ursula married \href{#}{\textcolor{accent}{\textbf{\underline{Christian Krattli.}}}}}

\entry{264}{Stephen Lean Jr. son of Stephen Lean Sr. and Thomasin Michell}{was born on 3 Apr 1751 in Camborne, Cornwall, England and died in May 1804 in Camborne, Cornwall, England, at age 53. Camborne, Cornwall, England.}
\marriage{Stephen married \href{#}{\textcolor{accent}{\textbf{\underline{Mary Sarah Varley}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Varley}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Robinson}}}}, on 13 Oct 1773 in}
\childrenrenheading
\childentrylinked{132}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Joseph Lean Sr.}}}}}
\childentryplain{265. Mary Sarah Varley}{ii}{, daughter of Joseph Varley and Anne Robinson, was born on 19 May 1752 in Gwinear,}
\childentryplain{Cornwall}{iii}{, England and died in Dec 1820 in Camborne, Cornwall, England, at age 68.}
\childentryplain{Mary married Stephen Lean Jr.}{iv}{, son of Stephen Lean Sr. and Thomasin Michell, on 13 Oct 1773 in}
\childentryplain{Camborne}{v}{, Cornwall, England.}
\dividerline

\entry{266}{George Trewren}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Trewren}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Thomasin Blight}}}}, was born on 31 May 1752 in Ludgvan, Cornwall, England and died in May 1815 in Ludgvan, Cornwall, England, at age 63. Cornwall, England.}
\marriage{George married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Hall}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Hall}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Tresise}}}}, on 7 Feb 1774 in Ludgvan,}
\childrenheading
\childentrylinked{133}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Ann Trewren}}}}}
\dividerline

\entry{267}{Catherine Hall}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Hall}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Tresise}}}}, was born on 11 Mar 1752 in Ludgvan, Cornwall, England and died on 2 Feb 1818 in Camborne, Cornwall, England, at age 65. Ludgvan, Cornwall, England.}
\marriage{Catherine married \href{#}{\textcolor{accent}{\textbf{\underline{George Trewren}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Trewren}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Thomasin Blight}}}}, on 7 Feb 1774 in}
\dividerline

\entry{270}{Richard Perry}{son of \href{#}{\textcolor{accent}{\textbf{\underline{John Perry}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret John}}}}, was born about 1740 in Wendron, Cornwall, England and died in Nov 1798 in Wendron, Cornwall, England, about age 58. Cornwall, England.}
\marriage{Richard married \href{#}{\textcolor{accent}{\textbf{\underline{Pascha Rutter}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Rutter}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jane Webber}}}}, on 25 Jun 1763 in Sithney,}
\childrenheading
\childentrylinked{135}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jenefer Jane Perry}}}}}
\dividerline

\entry{271}{Pascha Rutter}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Rutter}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jane Webber}}}}, was born in Sithney, Cornwall, England and died in Jul 1782. England.}
\marriage{Pascha married \href{#}{\textcolor{accent}{\textbf{\underline{Richard Perry}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{John Perry}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret John}}}}, on 25 Jun 1763 in Sithney, Cornwall,}
\dividerline

\entry{274}{Theodore Diderich Schmit}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Henri Philippen Schmit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Johanna Weyland}}}}, was born on 7 Jul 1716 in Remich, Luxembourg and died on 14 Oct 1779 in Gostingen, Grevenmacher, Luxembourg, at age 63.}
\marriage{Theodore married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Muller.}}}}}
\childrenheading
\childentrylinked{137}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Margaret Schmit}}}}}
\dividerline

\entry{275}{Marie Muller was born in Gostingen}{Grevenmacher, Luxembourg and died on 17 Sep 1788 in Gostingen, Grevenmacher, Luxembourg.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Theodore Diderich Schmit}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Henri Philippen Schmit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Johanna Weyland}}}}.}
\dividerline

\entry{284}{Peter Reiff}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Reiff}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Gertrude Klein}}}}, was born on 17 Sep 1738 in Niederdonven, Grevenmacher, Luxembourg and died on 30 Mar 1812 in Niederdonven, Grevenmacher, Luxembourg, at age 73. Niederdonven, Grevenmacher, Luxembourg.}
\marriage{Peter married \href{#}{\textcolor{accent}{\textbf{\underline{Susanna Ludwig}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Ludwig}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Dorothea}}}}, on 7 Sep 1775 in}
\childrenheading
\childentrylinked{142}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Wilhelmus Reiff}}}}}
\dividerline

\entry{285}{Susanna Ludwig}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Ludwig}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Dorothea}}}}, was born about 1757 in Canach, Remich, Grevenmacher, Luxembourg and died on 9 Jun 1812 in Niederdonven, Grevenmacher, Luxembourg, about age 55. Grevenmacher, Luxembourg.}
\marriage{Susanna married \href{#}{\textcolor{accent}{\textbf{\underline{Peter Reiff}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Reiff}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Gertrude Klein}}}}, on 7 Sep 1775 in Niederdonven,}
\dividerline

\entry{286}{Peter Bastian}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johannes Bastian}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Theresiae Michaeli}}}}, was born about 1750 in Rehlingen, Saarlouis, Saarland, Germany.}
\marriage{Peter married \href{#}{\textcolor{accent}{\textbf{\underline{Maria Holtz.}}}}}
\childrenheading
\childentrylinked{143}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Barbara Bastian}}}}}
\dividerline

\entry{287}{Maria Holtz was born in Muhlfeld}{Saarbrucken, Saarland, Germany.}
\marriage{Maria married \href{#}{\textcolor{accent}{\textbf{\underline{Peter Bastian}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johannes Bastian}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Theresiae Michaeli}}}}.}
\dividerline

\entry{400}{Francois Demers}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Demers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Jette}}}}, was born on 5 Mar 1712 in Montreal, Quebec, Canada and died on 20 Oct 1775 in Chambly, Quebec, Canada, at age 63. Boivin.}
\marriage{Francois married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Josephe Larocque}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Guillaume Larocque}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Jeanne}}}}}
\childrenheading
\childentrylinked{200}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Joseph Amable Demers}}}}}
\dividerline

\entry{401}{Marie Josephe Larocque}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Guillaume Larocque}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Jeanne Boivin}}}}, was born on 13 Nov 1719 in Montreal, Quebec, Canada and died on 27 Aug 1774 in Quebec City, Quebec, Canada, at age 54.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Francois Demers}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Demers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Jette}}}}.}
\dividerline

\entry{402}{Simon Favreau}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Favreau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Marie Lacoste}}}}, was born on 8 Mar 1727 in Boucherville, Chambly, Quebec, Canada and died on 21 May 1801 in Chambly, Quebec, Canada, at age 74.}
\marriage{Simon married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Jeanne Banlier}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Banlier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Neveu}}}}.}
\childrenheading
\childentrylinked{201}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Favreau}}}}}
\dividerline

\entry{403}{Marie Anne Jeanne Banlier}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Banlier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Neveu}}}}, was born on 21 Jul 1726 in Varennes, Monteregie, Quebec, Canada and died on 21 Jul 1794 in Chambly, Quebec, Canada, at age 68. 404. Jean Baptiste Proteau, son of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Proteau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Boure}}}}, was born on 10 Oct 1708 in Charlesbourg, Quebec, Canada and died on 11 Dec 1758 in Charlesbourg, Quebec, Canada, at age 50. on 25 Oct 1734 in Beauport, Quebec, Canada.}
\marriage{Jean married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Bruneau}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Bruneau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Bourgouin}}}},}
\childrenheading
\childentrylinked{202}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Proteau}}}}}
\dividerline

\entry{405}{Marie Madeleine Bruneau}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Bruneau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Bourgouin}}}}, was born on 24 Jan 1715 in Beauport, Quebec, Canada and died on 18 Mar 1798 in Chambly, Quebec, Canada, at age 83. 1734 in Beauport, Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Proteau}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Proteau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Boure}}}}, on 25 Oct}
\dividerline

\entry{406}{Louis Benoit}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Benoit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Charlotte Charles}}}}, was born in 1742 in Montmorency, Ile d'Orleans, Quebec, Canada and died on 6 May 1799 in Chambly, Quebec, Canada, at age 57.}
\marriage{Louis married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Reine Lavoie}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Augustin Lavoie}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Angelique Duchesne}}}}.}
\childrenheading
\childentrylinked{203}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elisabeth Benoit}}}}}
\dividerline

\entry{407}{Marie Reine Lavoie}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Augustin Lavoie}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Angelique Duchesne}}}}, was born on 17 Jan 1746 in Saint-Joachim, Quebec, Canada and died on 12 Aug 1788 in Chambly, Quebec, Canada, at age 42.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Louis Benoit}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Benoit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Charlotte Charles}}}}.}
\dividerline

\entry{412}{Jean Maurice Morin}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Joseph Morin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Charlotte Dube}}}}, was born on 15 Feb 1733 in La Pocatiere, Kamouraska, Quebec, Canada and died on 10 Apr 1790 in Quebec, Canada, at age 57. La Pocatiere, Kamouraska, Quebec, Canada.}
\marriage{Jean married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Josephte Miville}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Roy}}}}, on 10 Feb 1755 in}
\childrenheading
\childentrylinked{206}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Pierre Noel Morin}}}}}
\dividerline

\entry{413}{Marie Josephte Miville}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Roy}}}}, was born on 14 Feb 1738 in La Pocatiere, Kamouraska, Quebec, Canada and died on 10 Apr 1809 in Quebec, Canada, at age 71. 1755 in La Pocatiere, Kamouraska, Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Jean Maurice Morin}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Joseph Morin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Charlotte Dube}}}}, on 10 Feb}
\dividerline

\entry{414}{Amable Panneton}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Claude Panneton}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Petronille Senecal}}}}, was born on 7 Apr 1740 in Varennes, Monteregie, Quebec, Canada and died in 1787 in L'Assomption, Quebec, Canada, at age 47.}
\marriage{Amable married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Josephe Landry on 24 Jul 1769 in L'Assomption}}}}, Quebec, Canada.}
\childrenrenheading
\childentrylinked{207}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Louise Panneton}}}}}
\childentry{}{415. Marie Josephe Landry .}
\childentryplain{Marie married Amable Panneton}{iii}{, son of Claude Panneton and Petronille Senecal, on 24 Jul 1769 in}
\childentryplain{L'Assomption}{iv}{, Quebec, Canada.}
\dividerline

\entry{416}{Heinrich Kamm was born about 1728 in Korb}{Wuerttemberg, Germany and died in Steinreinach, Baden- Wuerttemberg, Germany.}
\marriage{Heinrich married \href{#}{\textcolor{accent}{\textbf{\underline{Barbara Schlegel.}}}}}
\childrenheading
\childentrylinked{208}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Heinrich Kamm}}}}}
\dividerline

\entry{417}{Barbara Schlegel .}{}
\marriage{Barbara married \href{#}{\textcolor{accent}{\textbf{\underline{Heinrich Kamm.}}}}}
\dividerline

\entry{418}{Martin Kohler .}{}
\marriage{Martin married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth.}}}}}
\childrenheading
\childentrylinked{209}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Kohler}}}}}
\dividerline

\entry{419}{Elizabeth .}{}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{Martin Kohler.}}}}}
\dividerline

\entry{424}{Johann Adam Bockel .}{His child was: 212 i. Johann Adam Bockel}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{someone.}}}}}
\dividerline

\entry{426}{Johann Leonhard Heumajer .}{}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Maria Catharina Rothfuss.}}}}}
\childrenheading
\childentrylinked{213}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Catharina Magdalena Heumajer}}}}}
\dividerline

\entry{427}{Maria Catharina Rothfuss .}{}
\marriage{Maria married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Leonhard Heumajer.}}}}}
\dividerline

\entry{428}{Johann Heinrich Vogel .}{His child was: 214 i. Christian Gottlob Vogel}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{someone.}}}}}
\dividerline

\entry{448}{Johann Georg Leik .}{}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Marie Schmidt.}}}}}
\childrenheading
\childentrylinked{224}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Konrad Leik}}}}}
\dividerline

\entry{449}{Anna Marie Schmidt .}{}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Leik.}}}}}
\dividerline

\entry{450}{Johann Georg Eichenauer .}{}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Margaretha Rausch.}}}}}
\childrenheading
\childentrylinked{225}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Eichenauer}}}}}
\dividerline

\entry{451}{Anna Margaretha Rausch .}{}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Eichenauer.}}}}}
\dividerline

\entry{456}{Martin Shaffer}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Martin Schaffer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Catherine Lautenschlager}}}}, was born on 5 Apr 1752 in Lancaster Co., PA and died on 27 Feb 1845 in North Beaver, Lawrence, PA, at age 92. General Notes: In 1790, he and his family lived in Earl Twp., Lancaster Co., PA. There was one non-white free person living in their household at the time.}
\marriage{Martin married \href{#}{\textcolor{accent}{\textbf{\underline{Barbara.}}}}}
\childrenheading
\childentrylinked{228}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Christopher Shaffer}}}}}
\dividerline

\entry{457}{Barbara .}{}
\marriage{Barbara married \href{#}{\textcolor{accent}{\textbf{\underline{Martin Shaffer}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Martin Schaffer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Catherine Lautenschlager}}}}.}
\dividerline

\entry{460}{Michael Pitzer}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Conrad Bitzer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Barbara Hauser}}}}, was born on 20 Feb 1734 in Tailfingen, Boblingen, Baden-Wuerttemberg, Germany and died on 17 May 1822 in Berkeley Co., WV, at age 88. Weider, in Mar 1755 in Lancaster Co., PA.}
\marriage{Michael married \href{#}{\textcolor{accent}{\textbf{\underline{Sophia Scharlotta Boshaar}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Balthazar Boshaar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Johanna Dorothea}}}}}
\childrenrenheading
\childentrylinked{230}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Michael K. Pitzer}}}}}
\childentryplain{461. Sophia Scharlotta Boshaar}{ii}{, daughter of Balthazar Boshaar and Johanna Dorothea Weider, was born on 24}
\childentryplain{Mar 1739 in New Holland}{iii}{, Lancaster, PA.}
\childentryplain{Sophia married Michael Pitzer}{iv}{, son of Conrad Bitzer and Maria Barbara Hauser, in Mar 1755 in Lancaster}
\childentryplain{Co.}{v}{, PA.}
\dividerline

\entry{462}{Balthazar Boshaar}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johan Jorg Boshaar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Wennerich}}}}, was born on 31 Jul 1720 in Kingston, Ulster, NY and died on 19 Nov 1791 in Earl Twp., Lancaster, PA, at age 71.}
\marriage{Balthazar married \href{#}{\textcolor{accent}{\textbf{\underline{Johanna Dorothea Weider.}}}}}
\childrenrenheading
\childentrylinked{461}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Sophia Scharlotta Boshaar}}}}}
\childentry{}{231 ii. Catherine Boshaar}
\dividerline

\entry{463}{Johanna Dorothea Weider was born on 17 Apr 1719 in Leacock}{Lancaster, PA and died on 23 Feb 1746 in Earl Twp., Lancaster, PA, at age 26.}
\marriage{Johanna married \href{#}{\textcolor{accent}{\textbf{\underline{Balthazar Boshaar}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johan Jorg Boshaar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Wennerich}}}}.}
\dividerline

\entry{468}{Zinnara Fry was born about 1760.}{}
\marriage{Zinnara married \href{#}{\textcolor{accent}{\textbf{\underline{Valentine.}}}}}
\childrenheading
\childentrylinked{234}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Zinnara Surratt "Zimery" Fry}}}}}
\dividerline

\entry{469}{Valentine was born in Pennsylvania.}{}
\marriage{Valentine married \href{#}{\textcolor{accent}{\textbf{\underline{Zinnara Fry.}}}}}
\dividerline

\entry{470}{George Walton}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Christopher Walton}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Hannah Burton}}}}, was born about 1769 in Knock, Westmoreland, England and died on 5 Aug 1850 in St. Francois, St. Francois, MO, about age 81. Knock, Westmoreland, England.}
\marriage{George married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Parkin}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Parkin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Janet Atkinson}}}}, on 6 Mar 1797 in}
\childrenheading
\childentrylinked{235}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Hannah Walton}}}}}
\dividerline

\entry{471}{Elizabeth Parkin}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Parkin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Janet Atkinson}}}}, was born in Knock, Westmoreland, England and died in St. Francois, St. Francois, MO. Knock, Westmoreland, England.}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{George Walton}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Christopher Walton}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Hannah Burton}}}}, on 6 Mar 1797 in}
\dividerline

\entry{472}{Christoph Schaumburg}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Wilhelm Hinrich Schaumburg}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Dorothea Elisabeth Druesedow}}}}, was born in Jul 1751 in Mecklenburg-Schwerin, Germany and died on 10 Oct 1835 in Barner Stuck, Mecklenburg- Vorpommern, Germany, at age 84.}
\marriage{Christoph married \href{#}{\textcolor{accent}{\textbf{\underline{Maria Christina Homann}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Michel Homann}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Lena Cracow}}}}.}
\childrenheading
\childentrylinked{236}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Johann Christian Gotthard Schaumburg}}}}}
\dividerline

\entry{473}{Maria Christina Homann}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Michel Homann}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Lena Cracow}}}}, was born on 14 Sep 1759 in Golchen, Mecklenburg-Schwerin, Germany and died on 10 Jun 1832 in Barner Stuck, Mecklenburg-Vorpommern, Germany, at age 72. Druesedow.}
\marriage{Maria married \href{#}{\textcolor{accent}{\textbf{\underline{Christoph Schaumburg}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Wilhelm Hinrich Schaumburg}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Dorothea Elisabeth}}}}}
\dividerline

\entry{474}{Johann Christian Ohde .}{}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Sophia Catharina.}}}}}
\childrenheading
\childentrylinked{237}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Sophie Catherine Elizabeth Ohde}}}}}
\dividerline

\entry{475}{Sophia Catharina .}{}
\marriage{Sophia married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Christian Ohde.}}}}}
\dividerline

\entry{480}{Johann Michael Muller was born on 13 Mar 1760 in Germany.}{His child was: 240 i. Christoph Muller}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{someone.}}}}}
\dividerline

\entry{482}{Michael Gengenbach was born about 1770 in Haugstatt}{Baden-Wuerttemberg, Germany.}
\marriage{Michael married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Regina Keppler}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Egidius Keppler}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Luz}}}}.}
\childrenheading
\childentrylinked{241}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Eva Maria Gengenbach}}}}}
\dividerline

\entry{483}{Anna Regina Keppler}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Egidius Keppler}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Luz}}}}, was born on 9 Dec 1771 in Wurzbach, Baden-Wuerttemberg, Germany and died on 10 Feb 1827 in Haugstatt, Baden-Wuerttemberg, Germany, at age 55.}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Michael Gengenbach.}}}}}
\dividerline

\entry{488}{Johannes Hellenschmitt}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Hellenschmitt}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Barbara Hahn}}}}, was born on 25 Dec 1740 in Baden-Wuerttemberg, Germany and died in Spielbach, Baden-Wuerttemberg, Germany. Glaser.}
\marriage{Johannes married \href{#}{\textcolor{accent}{\textbf{\underline{Margaretha Barbara Albrecht}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jakob Albrecht}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaretha Barbara}}}}}
\childrenrenheading
\childentrylinked{244}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Johann Matthaus Hellenschmitt}}}}}
\childentryplain{489. Margaretha Barbara Albrecht}{ii}{, daughter of Jakob Albrecht and Margaretha Barbara Glaser, was born about}
\childentry{}{1745 in Germany.}
\childentryplain{Margaretha married Johannes Hellenschmitt}{iv}{, son of Johann Hellenschmitt and Maria Barbara Hahn.}
\dividerline

\entry{490}{Johann Peter Schmitz was born on 24 May 1758 in Mullenbach}{Cochem-Zell, Rheinland-Pfalz, Germany and died on 9 Mar 1814 in Cochem-Zell, Rheinland-Pfalz, Germany, at age 55. Germany.}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Meisen on 24 Feb 1784 in Mullenbach}}}}, Cochem-Zell, Rheinland-Pfalz,}
\childrenheading
\childentrylinked{245}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Margaretha Barbara Schmitz}}}}}
\dividerline

\entry{491}{Anna Maria Meisen was born on 27 Apr 1764 in Masburg}{Cochem-Zell, Rheinland-Pfalz, Germany and died on 9 Apr 1814 in Mullenbach, Cochem-Zell, Rheinland-Pfalz, Germany, at age 49. Germany.}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Peter Schmitz on 24 Feb 1784 in Mullenbach}}}}, Cochem-Zell, Rheinland-Pfalz,}
\dividerline

\entry{492}{Eberhard Wild}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Wild}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catharina Dorothea}}}}, was born about 1725 in Baden-Wuerttemberg, Germany.}
\marriage{Eberhard married \href{#}{\textcolor{accent}{\textbf{\underline{Elisabethe Diez.}}}}}
\childrenheading
\childentrylinked{246}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Christian Eberhardt Wild}}}}}
\dividerline

\entry{493}{Elisabethe Diez .}{}
\marriage{Elisabethe married \href{#}{\textcolor{accent}{\textbf{\underline{Eberhard Wild}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Wild}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catharina Dorothea}}}}.}
\dividerline

\entry{494}{Johann Michael Mohler was born on 2 Sep 1742 in Berlichingen}{Hohenlohekreis, Baden-Wuerttemberg, Germany.}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Charlotte Edelmann.}}}}}
\childrenheading
\childentrylinked{247}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Christiane Katharine Mohler}}}}}
\dividerline

\generationtitle{Tenth Generation}
\entry{495}{Marie Charlotte Edelmann .}{}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Michael Mohler.}}}}}

\entry{528}{Stephen Lean Sr. son of John Lean and Elizabeth Polkinghorn}{was born on 11 Sep 1721 in Gwennap, Cornwall, England and died in 1763 in Camborne, Cornwall, England, at age 42. Camborne, Cornwall, England.}
\marriage{Stephen married \href{#}{\textcolor{accent}{\textbf{\underline{Thomasin Michell}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Michell}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joan Upton}}}}, on 31 Dec 1744 in}
\childrenheading
\childentrylinked{264}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Stephen Lean Jr.}}}}}
\dividerline

\entry{529}{Thomasin Michell}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Michell}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joan Upton}}}}, was born in Jun 1717 in Phillack, Cornwall, England and died on 19 Feb 1791 in Camborne, Cornwall, England, at age 73. Camborne, Cornwall, England.}
\marriage{Thomasin married \href{#}{\textcolor{accent}{\textbf{\underline{Stephen Lean Sr.}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{John Lean}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Polkinghorn}}}}, on 31 Dec 1744 in}
\dividerline

\entry{530}{Joseph Varley was born about 1720 in Cornwall}{England and died on 29 Aug 1769 in Camborne, Cornwall, England, about age 49.}
\marriage{Joseph married \href{#}{\textcolor{accent}{\textbf{\underline{Anne Robinson.}}}}}
\childrenheading
\childentrylinked{265}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Mary Sarah Varley}}}}}
\dividerline

\entry{531}{Anne Robinson .}{}
\marriage{Anne married \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Varley.}}}}}
\dividerline

\entry{532}{Joseph Trewren}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Trewren}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Couch}}}}, was born on 15 Apr 1721 in St. Hilary, Cornwall, England and died on 1 Jul 1768 in Ludgvan, Cornwall, England, at age 47. Ludgvan, Cornwall, England.}
\marriage{Joseph married \href{#}{\textcolor{accent}{\textbf{\underline{Thomasin Blight}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Ephraim Blight}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jane Sampson}}}}, on 19 Oct 1745 in}
\childrenheading
\childentrylinked{266}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{George Trewren}}}}}
\dividerline

\entry{533}{Thomasin Blight}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Ephraim Blight}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jane Sampson}}}}, was born on 23 Dec 1715 in Ludgvan, Cornwall, England and died in 1796 in Marazian, Cornwall, England, at age 81. Ludgvan, Cornwall, England.}
\marriage{Thomasin married \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Trewren}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Trewren}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Couch}}}}, on 19 Oct 1745 in}
\dividerline

\entry{534}{John Hall}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Hall}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Gomer}}}}, was born on 9 May 1725 in Lelant, Cornwall, England and died on 18 Aug 1761 in Cornwall, England, at age 36. Lelant, Cornwall, England.}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Tresise}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Tresise}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Loveday Trenbath}}}}, on 5 Feb 1753 in}
\childrenheading
\childentrylinked{267}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Catherine Hall}}}}}
\dividerline

\entry{535}{Elizabeth Tresise}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Tresise}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Loveday Trenbath}}}}, was born on 13 Apr 1729 in Penwith, Cornwall, England and died in 1797 in Cornwall, England, at age 68. England.}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{John Hall}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Hall}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Gomer}}}}, on 5 Feb 1753 in Lelant, Cornwall,}
\dividerline

\entry{540}{John Perry}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Zacharias Perry}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Jenkin}}}}, was born about 1700 in Wendron, Cornwall, England and died in Nov 1766 in Wendron, Cornwall, England, about age 66. England.}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Margaret John}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Gye John}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Ann Shoal}}}}, on 13 Feb 1725 in Wendron, Cornwall,}
\childrenheading
\childentrylinked{270}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Richard Perry}}}}}
\dividerline

\entry{541}{Margaret John}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Gye John}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Ann Shoal}}}}, died in Apr 1769 in Wendron, Cornwall, England. Cornwall, England.}
\marriage{Margaret married \href{#}{\textcolor{accent}{\textbf{\underline{John Perry}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Zacharias Perry}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Jenkin}}}}, on 13 Feb 1725 in Wendron,}
\dividerline

\entry{542}{William Rutter}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Bartholomew Rutter}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Katherine John}}}}, was born on 26 May 1702 in Wendron, Cornwall, England and died on 26 Apr 1761 in Wendron, Cornwall, England, at age 58. Cornwall, England.}
\marriage{William married \href{#}{\textcolor{accent}{\textbf{\underline{Jane Webber}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Webber}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jane Pascoe}}}}, on 7 Oct 1722 in Helston,}
\childrenheading
\childentrylinked{271}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Pascha Rutter}}}}}
\dividerline

\entry{543}{Jane Webber}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Webber}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jane Pascoe}}}}. Cornwall, England.}
\marriage{Jane married \href{#}{\textcolor{accent}{\textbf{\underline{William Rutter}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Bartholomew Rutter}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Katherine John}}}}, on 7 Oct 1722 in Helston,}
\dividerline

\entry{548}{Henri Philippen Schmit}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Michael Schmit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaretha}}}}, was born on 17 May 1683 in Remich, Luxembourg and died in Feb 1726 in Gostingen, Grevenmacher, Luxembourg, at age 42.}
\marriage{Henri married \href{#}{\textcolor{accent}{\textbf{\underline{Johanna Weyland.}}}}}
\childrenheading
\childentrylinked{274}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Theodore Diderich Schmit}}}}}
\dividerline

\entry{549}{Johanna Weyland was born in Gostingen}{Grevenmacher, Luxembourg and died in 1752 in Luxembourg.}
\marriage{Johanna married \href{#}{\textcolor{accent}{\textbf{\underline{Henri Philippen Schmit}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Michael Schmit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaretha}}}}.}
\dividerline

\entry{568}{Pierre Reiff was born about 1713 in Niederdonven}{Grevenmacher, Luxembourg and died in 1760 in Luxembourg, about age 47.}
\marriage{Pierre married \href{#}{\textcolor{accent}{\textbf{\underline{Gertrude Klein.}}}}}
\childrenrenheading
\childentrylinked{284}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Peter Reiff}}}}}
\childentry{}{569. Gertrude Klein .}
\childentry{}{Gertrude married Pierre Reiff.}
\dividerline

\entry{570}{Francois Ludwig was born in Luxembourg.}{}
\marriage{Francois married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Dorothea.}}}}}
\childrenheading
\childentrylinked{285}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Susanna Ludwig}}}}}
\dividerline

\entry{571}{Anna Dorothea .}{}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Francois Ludwig.}}}}}
\dividerline

\entry{572}{Johannes Bastian .}{}
\marriage{Johannes married \href{#}{\textcolor{accent}{\textbf{\underline{Theresiae Michaeli.}}}}}
\childrenheading
\childentrylinked{286}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Peter Bastian}}}}}
\dividerline

\entry{573}{Theresiae Michaeli .}{}
\marriage{Theresiae married \href{#}{\textcolor{accent}{\textbf{\underline{Johannes Bastian.}}}}}
\dividerline

\entry{800}{Robert Demers}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Andre Demers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Chefdeville}}}}, was born on 11 Jan 1671 in Boucherville, Chambly, Quebec, Canada and died on 22 May 1741 in Montreal, Quebec, Canada, at age 70. 1694.}
\marriage{Robert married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Jette}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Urbain Jette}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Catherine Charles}}}}, on 26 Apr}
\childrenheading
\childentrylinked{400}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Francois Demers}}}}}
\dividerline

\entry{801}{Marie Madeleine Jette}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Urbain Jette}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Catherine Charles}}}}, was born on 10 Dec 1673 in Montreal, Quebec, Canada and died on 9 Jul 1737 in Montreal, Quebec, Canada, at age 63.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Robert Demers}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Andre Demers}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Chefdeville}}}}, on 26 Apr 1694.}
\dividerline

\entry{802}{Guillaume Larocque}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Larocque}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Morel}}}}, was born on 10 Feb 1682 in Marsac-sur- Tarn, Albi, Languedoc, France and died on 14 Dec 1759 in Montreal, Quebec, Canada, at age 77. 21 Mar 1717 in Montreal, Quebec, Canada.}
\marriage{Guillaume married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Jeanne Boivin}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Michel Boivin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Francoise Lorrain}}}}, on}
\childrenheading
\childentrylinked{401}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Josephe Larocque}}}}}
\dividerline

\entry{803}{Catherine Jeanne Boivin}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Michel Boivin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Francoise Lorrain}}}}, was born on 31 Mar 1699 in Montreal, Quebec, Canada and died on 15 May 1758 in Chambly, Quebec, Canada, at age 59. Montreal, Quebec, Canada.}
\marriage{Catherine married \href{#}{\textcolor{accent}{\textbf{\underline{Guillaume Larocque}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Larocque}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Morel}}}}, on 21 Mar 1717 in}
\dividerline

\entry{804}{Nicolas Favreau}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Favreau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Barbe Meunier}}}}, was born on 1 Mar 1701 in Boucherville, Chambly, Quebec, Canada and died on 10 Nov 1729 in Boucherville, Chambly, Quebec, Canada, at age 28.}
\marriage{Nicolas married \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Marie Lacoste}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Alexandre Lacoste}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Marguerite Deniau}}}}.}
\childrenheading
\childentrylinked{402}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Simon Favreau}}}}}
\dividerline

\entry{805}{Marguerite Marie Lacoste}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Alexandre Lacoste}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Marguerite Deniau}}}}, was born on 14 Jun 1705 in Chambly, Quebec, Canada and died in 1788 in Contrecoeur, Lajemmerais, Quebec, Canada, at age 83.}
\marriage{Marguerite married \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Favreau}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Favreau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Barbe Meunier}}}}.}
\dividerline

\entry{806}{Jean Baptiste Banlier}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Mathurin Banlier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Denise Vernin}}}}, was born on 29 Mar 1682 in Richelieu, Quebec, Canada and died on 9 Jul 1728 in Quebec City, Quebec, Canada, at age 46.}
\marriage{Jean married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Neveu}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Neveu}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Chaudillon}}}}.}
\childrenheading
\childentrylinked{403}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Jeanne Banlier}}}}}
\dividerline

\entry{807}{Marie Neveu}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Neveu}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Chaudillon}}}}, was born in 1688 in Quebec City, Quebec, Canada and died on 25 Feb 1747 in Varennes, Monteregie, Quebec, Canada, at age 59.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Banlier}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Mathurin Banlier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Denise Vernin}}}}.}
\dividerline

\entry{808}{Jean Baptiste Proteau}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Proteau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Seguin}}}}, was born on 13 Nov 1677 in Quebec, Canada and died on 2 Dec 1733 in Charlesbourg, Quebec, Canada, at age 56. Charlesbourg, Quebec, Canada.}
\marriage{Jean married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Boure}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Gilles Boure}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Bellehache}}}}, on 2 May 1707 in}
\childrenheading
\childentrylinked{404}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Proteau}}}}}
\dividerline

\entry{809}{Marie Anne Boure}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Gilles Boure}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Bellehache}}}}, was born on 26 Jan 1689 in Charlesbourg, Quebec, Canada and died on 2 Feb 1745 in Quebec City, Quebec, Canada, at age 56. Charlesbourg, Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Proteau}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Proteau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Seguin}}}}, on 2 May 1707 in}
\dividerline

\entry{810}{Francois Bruneau}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Bruneau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Prevost}}}}, was born on 21 Jun 1675 in Beaupre, Montmorency, Quebec, France and died on 23 Jul 1731 in Beauport, Quebec, Canada, at age 56. Feb 1702 in Beauport, Quebec, Canada.}
\marriage{Francois married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Bourgouin}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Bourgouin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Basset}}}}, on 21}
\childrenrenheading
\childentrylinked{405}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Bruneau}}}}}
\childentryplain{811. Marie Madeleine Bourgouin}{ii}{, daughter of Pierre Bourgouin and Catherine Basset, was born on 24 Oct 1683}
\childentryplain{in Quebec City}{iii}{, Quebec, Canada and died on 14 Jun 1722 in Beauport, Quebec, Canada, at age 38.}
\childentryplain{Marie married Francois Bruneau}{iv}{, son of Francois Bruneau and Marie Prevost, on 21 Feb 1702 in}
\childentryplain{Beauport}{v}{, Quebec, Canada.}
\dividerline

\entry{812}{Etienne Benoit}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Benoit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Jeanne Campeau}}}}, was born on 15 Feb 1702 in Longueuil, Quebec, Canada and died on 3 Dec 1757 in Chambly, Quebec, Canada, at age 55.}
\marriage{Etienne married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Charlotte Charles}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Clement Charles}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie-Madeleine Dupre}}}}.}
\childrenheading
\childentrylinked{406}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Louis Benoit}}}}}
\dividerline

\entry{813}{Marie Charlotte Charles}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Clement Charles}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie-Madeleine Dupre}}}}, was born on 13 Jun 1709 in Laval, Laval, Quebec, Canada and died on 8 Jul 1746 in Chambly, Quebec, Canada, at age 37.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Benoit}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Benoit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Jeanne Campeau}}}}.}
\dividerline

\entry{814}{Augustin Lavoie}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Francois Lavoie}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie-Madeleine Boucher}}}}, was born on 17 Feb 1704 in Montmorency, Ile d'Orleans, Quebec, Canada and died on 16 Oct 1770 in Kamouraska, Kamouraska, Quebec, Canada, at age 66.}
\marriage{Augustin married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Angelique Duchesne.}}}}}
\childrenheading
\childentrylinked{407}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Reine Lavoie}}}}}
\dividerline

\entry{815}{Marie Angelique Duchesne was born on 29 Mar 1710 in Saint-Francois}{Ile d'Orleans, Montmorency, Quebec and died on 27 Aug 1795 in Chambly, Quebec, Canada, at age 85.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Augustin Lavoie}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Francois Lavoie}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie-Madeleine Boucher}}}}.}
\dividerline

\entry{824}{Pierre Joseph Morin}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Morin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Mignier}}}}, was born on 18 Nov 1698 in Riviere- Ouelle, Kamouraska, Quebec, Canada and died on 23 Dec 1769 in La Pocatiere, Kamouraska, Quebec, Canada, at age}
\dividerline

\entry{71}{Pierre married Marie Charlotte Dube}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Mathurin Dube}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Miville}}}}, on 7 Jan 1722 in La Pocatiere, Kamouraska, Quebec, Canada.}
\childrenheading
\childentrylinked{412}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jean Maurice Morin}}}}}
\dividerline

\entry{825}{Marie Charlotte Dube}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Mathurin Dube}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Miville}}}}, was born on 17 May 1696 in Riviere- Ouelle, Kamouraska, Quebec, Canada and died on 19 Oct 1758 in Quebec, Canada, at age 62. Pocatiere, Kamouraska, Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Joseph Morin}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Morin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Mignier}}}}, on 7 Jan 1722 in La}
\dividerline

\entry{826}{Jacques Miville}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Charles Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Marthe Vallee}}}}, was born on 6 Apr 1709 in Riviere-Ouelle, Kamouraska, Quebec, Canada and died on 30 Nov 1789 in La Pocatiere, Kamouraska, Quebec, Canada, at age 80. Pocatiere, Kamouraska, Quebec, Canada.}
\marriage{Jacques married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Roy}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Roy}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Angelique Autin}}}}, on 26 Oct 1735 in La}
\childrenheading
\childentrylinked{413}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Josephte Miville}}}}}
\dividerline

\entry{827}{Marie Anne Roy}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Roy}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Angelique Autin}}}}, was born on 16 Dec 1713 in Riviere-Ouelle, Kamouraska, Quebec, Canada and died on 2 Apr 1799 in La Pocatiere, Kamouraska, Quebec, Canada, at age 85. Pocatiere, Kamouraska, Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Miville}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Charles Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Marthe Vallee}}}}, on 26 Oct 1735 in La}
\dividerline

\entry{828}{Claude Panneton}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Claude Panneton}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Doison}}}}, was born on 18 Sep 1698 in Quebec City, Quebec, Canada and died on 28 Feb 1780 in L'Assomption, Quebec, Canada, at age 81. Varennes, Monteregie, Quebec, Canada.}
\marriage{Claude married \href{#}{\textcolor{accent}{\textbf{\underline{Petronille Senecal}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Senecal}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Petronille Millault}}}}, on 1 Sep 1727 in}
\childrenheading
\childentrylinked{414}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Amable Panneton}}}}}
\dividerline

\entry{829}{Petronille Senecal}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Senecal}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Petronille Millault}}}}, was born on 26 Aug 1708 in Varennes, Monteregie, Quebec, Canada and died on 5 Apr 1781 in L'Assomption, Quebec, Canada, at age 72. Varennes, Monteregie, Quebec, Canada.}
\marriage{Petronille married \href{#}{\textcolor{accent}{\textbf{\underline{Claude Panneton}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Claude Panneton}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Doison}}}}, on 1 Sep 1727 in}
\dividerline

\entry{912}{Johann Martin Schaffer}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Adam Schaeffer}}}}, was born on 30 Aug 1724 in Starkenburg, Hesse, Germany and died on 9 Oct 1809 in Lower Milford, Lehigh, PA, at age 85. and Anna Elisabeth Seitz, on 29 Apr 1749 in Starkenburg, Hesse, Germany.}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Catherine Lautenschlager}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Henrick "Hans" Lautenschlager}}}}}
\childrenheading
\childentrylinked{456}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Martin Shaffer}}}}}
\dividerline

\entry{913}{Elizabeth Catherine Lautenschlager}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Henrick "Hans" Lautenschlager}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Elisabeth Seitz}}}}, was born on 27 Jan 1729 in Laudenau, Starkenburg, Hesse, Germany and died on 7 Oct 1809 in Lower Milford, Lehigh, PA, at age 80. Hesse, Germany.}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Martin Schaffer}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Adam Schaeffer}}}}, on 29 Apr 1749 in Starkenburg,}
\dividerline

\entry{920}{Conrad Bitzer}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Jacob Bitzer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherina Conzelmann}}}}, was born on 16 Dec 1684 in Tailfingen, Boblingen, Baden-Wuerttemberg, Germany and died on 12 Feb 1762 in Tailfingen, Boblingen, Baden-Wuerttemberg, Germany, at age 77. 26 Jun 1713 in Tailfingen, Boblingen, Baden-Wuerttemberg, Germany.}
\marriage{Conrad married \href{#}{\textcolor{accent}{\textbf{\underline{Maria Barbara Hauser}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Balthas Hauser}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Martha Comper}}}}, on}
\childrenrenheading
\childentrylinked{460}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Michael Pitzer}}}}}
\childentryplain{921. Maria Barbara Hauser}{ii}{, daughter of Hans Balthas Hauser and Anna Martha Comper, was born on 19 Nov}
\childentryplain{1700 in Tailfingen}{iii}{, Boblingen, Baden-Wuerttemberg, Germany and died on 27 Apr 1736 in Tailfingen, Boblingen,}
\childentryplain{Baden-Wuerttemberg}{iv}{, Germany, at age 35.}
\childentryplain{Maria married Conrad Bitzer}{v}{, son of Jacob Bitzer and Catherina Conzelmann, on 26 Jun 1713 in}
\childentryplain{Tailfingen}{vi}{, Boblingen, Baden-Wuerttemberg, Germany.}
\dividerline

\entry{922}{Balthazar Boshaar}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johan Jorg Boshaar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Wennerich}}}}, was born on 31 Jul 1720 in Kingston, Ulster, NY and died on 19 Nov 1791 in Earl Twp., Lancaster, PA, at age 71. (Duplicate. See Person 462 on Page 1)}
\dividerline

\entry{923}{Johanna Dorothea Weider was born on 17 Apr 1719 in Leacock}{Lancaster, PA and died on 23 Feb 1746 in Earl Twp., Lancaster, PA, at age 26. (Duplicate. See Person 463 on Page 1)}
\dividerline

\entry{924}{Johan Jorg Boshaar}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johan Jacob Boshaar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Christina Maurer}}}}, was born on 7 Jun 1694 in Zweibrucken, Zweibruckem, Rheinland-Pfalz, Germany and died on 8 Mar 1734 in Earl Twp., Lancaster, PA, at age}
\dividerline

\entry{39}{General Notes: He emigrated to the United States and disembarked in New York}{NY, in 1711. Kingston, Ulster, NY.}
\marriage{Johan married \href{#}{\textcolor{accent}{\textbf{\underline{Maria Wennerich}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Balthazar Wennerich}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Elizabeth}}}}, on 6 Aug 1716 in}
\childrenheading
\childentrylinked{462}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Balthazar Boshaar}}}}}
\dividerline

\entry{925}{Maria Wennerich}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Balthazar Wennerich}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Elizabeth}}}}, was born about 1693 in Edigheim, Ludwigschafen-am-Rhein, Rheinland-Pfalz, Germany and died in 1779 in Leacock, Lancaster, PA, about age 86. 1716 in Kingston, Ulster, NY.}
\marriage{Maria married \href{#}{\textcolor{accent}{\textbf{\underline{Johan Jorg Boshaar}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johan Jacob Boshaar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Christina Maurer}}}}, on 6 Aug}
\dividerline

\entry{940}{Christopher Walton was born on 1 Jan 1731 in Marton}{Lancashire, England and died on 15 Dec 1782 in Marton, Lancashire, England, at age 51.}
\marriage{Christopher married \href{#}{\textcolor{accent}{\textbf{\underline{Hannah Burton.}}}}}
\childrenheading
\childentrylinked{470}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{George Walton}}}}}
\dividerline

\entry{941}{Hannah Burton .}{}
\marriage{Hannah married \href{#}{\textcolor{accent}{\textbf{\underline{Christopher Walton.}}}}}
\dividerline

\entry{942}{Thomas Parkin}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Anthony Parkin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Robertson}}}}, was born on 24 Jun 1725 in Ravenstonedale, Westmoreland, England and died on 23 Nov 1782 in Knock, Westmoreland, England, at age 57.}
\marriage{Thomas married \href{#}{\textcolor{accent}{\textbf{\underline{Janet Atkinson}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{George Atkinson}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Thornborrow}}}}.}
\childrenrenheading
\childentrylinked{471}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Parkin}}}}}
\childentryplain{943. Janet Atkinson}{ii}{, daughter of George Atkinson and Catherine Thornborrow, was born on 6 Oct 1735 in}
\childentryplain{Dufton}{iii}{, Westmoreland, England.}
\childentryplain{Janet married Thomas Parkin}{iv}{, son of Anthony Parkin and Elizabeth Robertson.}
\dividerline

\entry{944}{Wilhelm Hinrich Schaumburg .}{}
\marriage{Wilhelm married \href{#}{\textcolor{accent}{\textbf{\underline{Dorothea Elisabeth Druesedow.}}}}}
\childrenheading
\childentrylinked{472}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Christoph Schaumburg}}}}}
\dividerline

\entry{945}{Dorothea Elisabeth Druesedow .}{}
\marriage{Dorothea married \href{#}{\textcolor{accent}{\textbf{\underline{Wilhelm Hinrich Schaumburg.}}}}}
\dividerline

\entry{946}{Michel Homann .}{}
\marriage{Michel married \href{#}{\textcolor{accent}{\textbf{\underline{Lena Cracow.}}}}}
\childrenheading
\childentrylinked{473}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Maria Christina Homann}}}}}
\dividerline

\entry{947}{Lena Cracow .}{}
\marriage{Lena married \href{#}{\textcolor{accent}{\textbf{\underline{Michel Homann.}}}}}
\dividerline

\entry{966}{Egidius Keppler .}{}
\marriage{Egidius married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Luz.}}}}}
\childrenheading
\childentrylinked{483}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Anna Regina Keppler}}}}}
\dividerline

\entry{967}{Anna Maria Luz .}{}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Egidius Keppler.}}}}}
\dividerline

\entry{976}{Johann Hellenschmitt}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Leonhard Hellenschmitt}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Sophia Botsch}}}}, was born on 17 Mar 1720 in Baden-Wuerttemberg, Germany and died about 1780, about age 60.}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Maria Barbara Hahn.}}}}}
\childrenheading
\childentrylinked{488}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Johannes Hellenschmitt}}}}}
\dividerline

\entry{977}{Maria Barbara Hahn was born on 26 Apr 1719 in Baden-Wuerttemberg}{Germany and died on 30 Sep 1808 in Germany, at age 89.}
\marriage{Maria married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Hellenschmitt}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Leonhard Hellenschmitt}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Sophia Botsch}}}}.}
\dividerline

\entry{978}{Jakob Albrecht was born about 1709 in Stuttgart}{Baden-Wuerttemberg, Germany and died on 19 Jan 1775 in Bitzfeld, Baden-Wuerttemberg, Germany, about age 66.}
\marriage{Jakob married \href{#}{\textcolor{accent}{\textbf{\underline{Margaretha Barbara Glaser on 13 Sep 1735 in Baden-Wuerttemberg}}}}, Germany.}
\childrenheading
\childentrylinked{489}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Margaretha Barbara Albrecht}}}}}
\dividerline

\entry{979}{Margaretha Barbara Glaser .}{}
\marriage{Margaretha married \href{#}{\textcolor{accent}{\textbf{\underline{Jakob Albrecht on 13 Sep 1735 in Baden-Wuerttemberg}}}}, Germany.}
\dividerline

\entry{984}{Johann Wild was born about 1700 in Baden-Wuerttemberg}{Germany.}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Catharina Dorothea.}}}}}
\childrenheading
\childentrylinked{492}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Eberhard Wild}}}}}
\dividerline

\entry{985}{Catharina Dorothea .}{11th Generation}
\marriage{Catharina married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Wild.}}}}}
\dividerline

\entry{1056}{John Lean}{son of \href{#}{\textcolor{accent}{\textbf{\underline{William Lean}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joan}}}}, was born on 7 Jun 1702 in Gwennap, Cornwall, England and died on 23 Jun 1728 in Gwennap, Cornwall, England, at age 26. Cornwall, England.}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Polkinghorn}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Stephen Polkinghorn}}}}, on 29 Jan 1721 in Gwennap,}
\childrenheading
\childentrylinked{528}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Stephen Lean Sr.}}}}}
\dividerline

\entry{1057}{Elizabeth Polkinghorn}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Stephen Polkinghorn}}}}, was born on 30 Sep 1694 in Gwennap, Cornwall, England and died on 20 Mar 1789 in Gwennap, Cornwall, England, at age 94. England.}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{John Lean}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{William Lean}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joan}}}}, on 29 Jan 1721 in Gwennap, Cornwall,}
\dividerline

\entry{1058}{John Michell was born about 1685 in Cornwall}{England.}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Joan Upton on 1 Nov 1709 in Phillack}}}}, Cornwall, England.}
\childrenrenheading
\childentrylinked{529}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Thomasin Michell}}}}}
\childentry{}{1059. Joan Upton .}
\childentryplain{Joan married John Michell on 1 Nov 1709 in Phillack}{iii}{, Cornwall, England.}
\dividerline

\entry{1064}{Joseph Trewren}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Trewren}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Seyley}}}}, was born on 29 Mar 1670 in Sancreed, Cornwall, England and died on 18 Aug 1733 in St. Hilary, Cornwall, England, at age 63. Cornwall, England.}
\marriage{Joseph married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Couch}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Couch}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Frethy}}}}, on 23 Nov 1714 in St. Hilary,}
\childrenheading
\childentrylinked{532}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Joseph Trewren}}}}}
\dividerline

\entry{1065}{Elizabeth Couch}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Couch}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Frethy}}}}, was born in St. Hilary, Cornwall, England and died on 18 Aug 1754 in Constantine, Cornwall, England. Hilary, Cornwall, England.}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{Joseph Trewren}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Trewren}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Seyley}}}}, on 23 Nov 1714 in St.}
\dividerline

\entry{1066}{Ephraim Blight}{son of \href{#}{\textcolor{accent}{\textbf{\underline{George Blight}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Philippa James}}}}, was born on 8 Oct 1682 in Ludgvan, Cornwall, England and died on 3 Feb 1759 in Ludgvan, Cornwall, England, at age 76. in Ludgvan, Cornwall, England.}
\marriage{Ephraim married \href{#}{\textcolor{accent}{\textbf{\underline{Jane Sampson}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Samuel Sampson}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margery Christopher}}}}, on 24 Oct 1707}
\childrenheading
\childentrylinked{533}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Thomasin Blight}}}}}
\dividerline

\entry{1067}{Jane Sampson}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Samuel Sampson}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margery Christopher}}}}, was born on 29 May 1684 in Ludgvan, Cornwall, England and died on 13 Oct 1765 in Ludgvan, Cornwall, England, at age 81. Cornwall, England.}
\marriage{Jane married \href{#}{\textcolor{accent}{\textbf{\underline{Ephraim Blight}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{George Blight}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Philippa James}}}}, on 24 Oct 1707 in Ludgvan,}
\dividerline

\entry{1068}{Thomas Hall}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Hall}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Nicholls}}}}, was born on 27 Dec 1694 in Madron, Cornwall, England and died in 1766 in Paul, Cornwall, England, at age 72. Paul, Cornwall, England.}
\marriage{Thomas married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Gomer}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Gomer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Sampson}}}}, on 1 Dec 1716 in}
\childrenheading
\childentrylinked{534}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{John Hall}}}}}
\dividerline

\entry{1069}{Elizabeth Gomer}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Gomer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Sampson}}}}, was born on 20 Oct 1695 in Paul, Cornwall, England and died in Nov 1779 in Paul, Cornwall, England, at age 84. England.}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Hall}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Hall}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Nicholls}}}}, on 1 Dec 1716 in Paul, Cornwall,}
\dividerline

\entry{1070}{William Tresise}{son of \href{#}{\textcolor{accent}{\textbf{\underline{John Tresise}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Wallish}}}}, was born on 25 Apr 1696 in Penwith, Cornwall, England and died on 1 Feb 1766 in Penwith, Cornwall, England, at age 69.}
\marriage{William married \href{#}{\textcolor{accent}{\textbf{\underline{Loveday Trenbath}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Emanuel Trenbath}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Warrin}}}}.}
\childrenheading
\childentrylinked{535}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Tresise}}}}}
\dividerline

\entry{1071}{Loveday Trenbath}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Emanuel Trenbath}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Warrin}}}}, was born on 2 Oct 1699 in Penwith, Cornwall, England and died on 1 Feb 1766 in Penwith, Cornwall, England, at age 66.}
\marriage{Loveday married \href{#}{\textcolor{accent}{\textbf{\underline{William Tresise}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{John Tresise}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Wallish}}}}.}
\dividerline

\entry{1080}{Zacharias Perry}{son of \href{#}{\textcolor{accent}{\textbf{\underline{William Perry}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Symons}}}}, was born on 17 Nov 1662 in Wendron, Cornwall, England and died in Mar 1735 in Wendron, Cornwall, England, at age 72.}
\marriage{Zacharias married \href{#}{\textcolor{accent}{\textbf{\underline{Anne Jenkin}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Matthew Jenkin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Alice Clise}}}}.}
\childrenheading
\childentrylinked{540}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{John Perry}}}}}
\dividerline

\entry{1081}{Anne Jenkin}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Matthew Jenkin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Alice Clise}}}}, was born about 1667 in Wendron, Cornwall, England and died in Sep 1746 in Wendron, Cornwall, England, about age 79.}
\marriage{Anne married \href{#}{\textcolor{accent}{\textbf{\underline{Zacharias Perry}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{William Perry}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Symons}}}}.}
\dividerline

\entry{1082}{Gye John}{son of \href{#}{\textcolor{accent}{\textbf{\underline{James John}}}}, was born about 1672 in Wendron, Cornwall, England and died on 19 Apr 1746 in Wendron, Cornwall, England, about age 74.}
\marriage{Gye married \href{#}{\textcolor{accent}{\textbf{\underline{Ann Shoal}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Shoal}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jane}}}}.}
\childrenheading
\childentrylinked{541}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Margaret John}}}}}
\dividerline

\entry{1083}{Ann Shoal}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Shoal}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jane}}}}.}
\marriage{Ann married \href{#}{\textcolor{accent}{\textbf{\underline{Gye John}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{James John}}}}.}
\dividerline

\entry{1084}{Bartholomew Rutter}{son of \href{#}{\textcolor{accent}{\textbf{\underline{William Rutter}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Katherine Pruste}}}}, was born about 1670 in Wendron, Cornwall, England and died on 16 Feb 1724 in Wendron, Cornwall, England, about age 54.}
\marriage{Bartholomew married \href{#}{\textcolor{accent}{\textbf{\underline{Katherine John}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Nicholas John}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joan}}}}.}
\childrenheading
\childentrylinked{542}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{William Rutter}}}}}
\dividerline

\entry{1085}{Katherine John}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Nicholas John}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joan}}}}, was born on 1 Apr 1669 in Wendron, Cornwall, England and died in Dec 1742 in Cornwall, England, at age 73.}
\marriage{Katherine married \href{#}{\textcolor{accent}{\textbf{\underline{Bartholomew Rutter}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{William Rutter}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Katherine Pruste}}}}.}
\dividerline

\entry{1086}{William Webber .}{}
\marriage{William married \href{#}{\textcolor{accent}{\textbf{\underline{Jane Pascoe}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Pascoe}}}}.}
\childrenheading
\childentrylinked{543}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jane Webber}}}}}
\dividerline

\entry{1087}{Jane Pascoe}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Pascoe}}}}.}
\marriage{Jane married \href{#}{\textcolor{accent}{\textbf{\underline{William Webber.}}}}}
\dividerline

\entry{1096}{Michael Schmit was born in Luxembourg.}{}
\marriage{Michael married \href{#}{\textcolor{accent}{\textbf{\underline{Margaretha.}}}}}
\childrenheading
\childentrylinked{548}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Henri Philippen Schmit}}}}}
\dividerline

\entry{1097}{Margaretha .}{}
\marriage{Margaretha married \href{#}{\textcolor{accent}{\textbf{\underline{Michael Schmit.}}}}}
\dividerline

\entry{1600}{Andre Demers was born on 3 Feb 1628 in Dieppe}{Seine-Maritime, Haute-Normandie, France and died on 17 Jul 1711 in Montreal, Quebec, Canada, at age 83.}
\marriage{Andre married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Chefdeville on 11 Dec 1653.}}}}}
\childrenheading
\childentrylinked{800}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Robert Demers}}}}}
\dividerline

\entry{1601}{Marie Chefdeville was born on 5 Jun 1631 in Villers-sous-Saint-Leu}{Oise, Picardie, France and died on 23 Nov 1708 in Montreal, Quebec, Canada, at age 77.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Andre Demers on 11 Dec 1653.}}}}}
\dividerline

\entry{1602}{Urbain Jette was born on 20 Oct 1626 in La Fleche}{Ille-et-Vilaine, Bretagne, France and died on 13 May 1684 in Montreal, Quebec, Canada, at age 57.}
\marriage{Urbain married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Catherine Charles.}}}}}
\childrenheading
\childentrylinked{801}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Jette}}}}}
\dividerline

\entry{1603}{Marie Catherine Charles died on 2 Dec 1691 in Montreal}{Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Urbain Jette.}}}}}
\dividerline

\entry{1604}{Antoine Larocque was born on 1 Jan 1656 in Marsac-sur-Tarn}{Albi, Languedoc, France and died in Aug 1720 in Chateau Richer, Montmorency, Quebec, Canada, at age 64.}
\marriage{Antoine married \href{#}{\textcolor{accent}{\textbf{\underline{Anne Morel}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Guillaume Morel}}}}.}
\childrenrenheading
\childentrylinked{802}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Guillaume Larocque}}}}}
\childentryplain{1605. Anne Morel}{ii}{, daughter of Guillaume Morel, died on 1 Aug 1720 in Chateau Richer, Montmorency, Quebec,}
\childentry{}{Canada.}
\childentry{}{Anne married Antoine Larocque.}
\dividerline

\entry{1606}{Michel Boivin}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Boivin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Blois}}}}, was born on 11 Dec 1666 in Montreal, Quebec, Canada and died on 16 Jun 1703 in Montreal, Quebec, Canada, at age 36.}
\marriage{Michel married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Francoise Lorrain}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Lorrain}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Saulnier}}}}.}
\childrenheading
\childentrylinked{803}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Catherine Jeanne Boivin}}}}}
\dividerline

\entry{1607}{Marie Francoise Lorrain}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Lorrain}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Saulnier}}}}, was born on 9 Sep 1680 in Montreal, Quebec, Canada and died on 7 Feb 1750 in Montreal, Quebec, Canada, at age 69.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Michel Boivin}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Boivin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Blois}}}}.}
\dividerline

\entry{1608}{Nicolas Favreau}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Favreau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Benoit}}}}, was born in 1668 in Contrecoeur, Lajemmerais, Quebec, Canada and died on 11 Jan 1731 in Vercheres, Lajemmerais, Quebec, Canada, at age 63. in Boucherville, Chambly, Quebec, Canada.}
\marriage{Nicolas married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Barbe Meunier}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Meunier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Barbe Richaume}}}}, on 20 Apr 1700}
\childrenheading
\childentrylinked{804}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Favreau}}}}}
\dividerline

\entry{1609}{Marie Barbe Meunier}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Meunier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Barbe Richaume}}}}, was born on 10 Apr 1683 in Richelieu, Quebec, Canada and died on 15 Jul 1742 in Boucherville, Chambly, Quebec, Canada, at age 59. Boucherville, Chambly, Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Favreau}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Favreau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Benoit}}}}, on 20 Apr 1700 in}
\dividerline

\entry{1610}{Alexandre Lacoste was born about 1668 in Arles}{Bouches-du-Rhone, Provence-Alpes Cote d'Azur, France and died on 10 Apr 1737 in Boucherville, Chambly, Quebec, Canada, about age 69.}
\marriage{Alexandre married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Marguerite Deniau}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Deniau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Helene Daudin}}}}.}
\childrenheading
\childentrylinked{805}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Marie Lacoste}}}}}
\dividerline

\entry{1611}{Marie Marguerite Deniau}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Deniau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Helene Daudin}}}}, was born on 5 Jul 1671 in Montreal, Quebec, Canada and died on 16 Oct 1737 in Chambly, Quebec, Canada, at age 66.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Alexandre Lacoste.}}}}}
\dividerline

\entry{1612}{Mathurin Banlier was born about 1641 in Poitiers}{Vienne, Nouvelle-Aquitaine, France and died on 21 Jan 1720 in Contrecoeur, Lajemmerais, Quebec, Canada, about age 79. Oct 1670 in Quebec, Canada.}
\marriage{Mathurin married \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Denise Vernin}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Vernin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Martaguet}}}}, on 11}
\childrenheading
\childentrylinked{806}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Banlier}}}}}
\dividerline

\entry{1613}{Francoise Denise Vernin}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Vernin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Martaguet}}}}, was born about 1651 in Angouleme, Charente, Poitou-Charentes, France and died on 27 Mar 1732 in Quebec, Canada, about age 81.}
\marriage{Francoise married \href{#}{\textcolor{accent}{\textbf{\underline{Mathurin Banlier on 11 Oct 1670 in Quebec}}}}, Canada.}
\dividerline

\entry{1614}{Francois Neveu}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Daniel Neveu}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Sain}}}}, was born on 5 Aug 1666 in Coutances, Manche, Basse- Normandie, France and died on 11 Jul 1694 in Richelieu, Quebec, Canada, at age 27.}
\marriage{Francois married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Chaudillon}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Chaudillon}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Francoise}}}}.}
\childrenheading
\childentrylinked{807}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Neveu}}}}}
\dividerline

\entry{1615}{Catherine Chaudillon}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Chaudillon}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Francoise}}}}, was born in Feb 1672 in Montreal, Quebec, Canada and died on 22 Oct 1745 in Varennes, Monteregie, Quebec, Canada, at age 73.}
\marriage{Catherine married \href{#}{\textcolor{accent}{\textbf{\underline{Francois Neveu}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Daniel Neveu}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Sain}}}}.}
\dividerline

\entry{1616}{Etienne Proteau}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Proteau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Sautret}}}}, was born in Nov 1639 in Montreuil, Maine- et-Loire, Pays de la Loire, France and died on 20 Jan 1693 in Quebec City, Quebec, Canada, at age 53.}
\marriage{Etienne married \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Seguin}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Seguin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Simone Verret}}}}.}
\childrenheading
\childentrylinked{808}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Proteau}}}}}
\dividerline

\entry{1617}{Marguerite Seguin}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Seguin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Simone Verret}}}}, was born on 24 Sep 1644 in Poitiers, Vienne, Nouvelle-Aquitaine, France and died on 18 Feb 1702 in Charlesbourg, Quebec, Canada, at age 57.}
\marriage{Marguerite married \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Proteau}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Proteau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Sautret}}}}.}
\dividerline

\entry{1618}{Gilles Boure was born in 1642 in France and died on 8 Feb 1726 in Charlesbourg}{Quebec, Canada, at age 84. Charlesbourg, Quebec, Canada.}
\marriage{Gilles married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Bellehache}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Bellehache}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Burelle}}}}, on 9 Sep 1673 in}
\childrenheading
\childentrylinked{809}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Boure}}}}}
\dividerline

\entry{1619}{Marie Bellehache}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Bellehache}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Burelle}}}}, was born on 10 Jun 1655 in Ecos, Eure, Haute-Normandie, France and died on 7 Dec 1718 in Charlesbourg, Quebec, Canada, at age 63.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Gilles Boure on 9 Sep 1673 in Charlesbourg}}}}, Quebec, Canada.}
\dividerline

\entry{1620}{Francois Bruneau}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Bruneau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Charbonnier}}}}, was born in 1643 in Saintes, Charente-Maritime, Poitou-Charentes, France and died in 1679 in Quebec, Canada, at age 36. Quebec, Canada.}
\marriage{Francois married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Prevost}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Prevost}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie}}}}, on 9 Oct 1669 in Quebec City,}
\childrenheading
\childentrylinked{810}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Francois Bruneau}}}}}
\dividerline

\entry{1621}{Marie Prevost}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Prevost}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie}}}}, was born about 1651 in Orleans, Loiret, Centre, France and died on 19 Feb 1711 in Quebec City, Quebec, Canada, about age 60. Quebec City, Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Francois Bruneau}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Bruneau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Charbonnier}}}}, on 9 Oct 1669 in}
\dividerline

\entry{1622}{Pierre Bourgouin}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Bourgouin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Andree}}}}, was born about 1641 in Fontenay-le-Comte, Vendee, Pays de la Loire, France and died on 12 Sep 1719 in Beauport, Quebec, Canada, about age 78. Quebec City, Quebec, Canada.}
\marriage{Pierre married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Basset}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Guillaume Basset}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Carrier}}}}, on 17 Oct 1667 in}
\childrenheading
\childentrylinked{811}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Bourgouin}}}}}
\dividerline

\entry{1623}{Catherine Basset}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Guillaume Basset}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Carrier}}}}, was born about 1637 in Darnetal, Seine-Maritime, Haute-Normandie, France and died on 16 Nov 1716 in Beauport, Quebec, Canada, about age 79. City, Quebec, Canada.}
\marriage{Catherine married \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Bourgouin}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Bourgouin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Andree}}}}, on 17 Oct 1667 in Quebec}
\dividerline

\entry{1624}{Etienne Benoit}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Paul Benoit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elisabeth Isabelle Gobinet}}}}, was born on 25 Dec 1662 in Montreal, Quebec, Canada and died on 21 Mar 1746 in Longueuil, Quebec, Canada, at age 83.}
\marriage{Etienne married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Jeanne Campeau}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Campeau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Paulo}}}}.}
\childrenheading
\childentrylinked{812}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Etienne Benoit}}}}}
\dividerline

\entry{1625}{Marie Jeanne Campeau}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Campeau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Paulo}}}}, was born on 1 Jun 1679 in Montreal, Quebec, Canada and died on 30 Jun 1721 in Longueuil, Quebec, Canada, at age 42.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Benoit}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Paul Benoit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elisabeth Isabelle Gobinet}}}}.}
\dividerline

\entry{1626}{Clement Charles}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Charles}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Madeleine Niel}}}}, was born on 28 Oct 1671 in Ste-Famille Boucherville, Chambly, Quebec, Canada and died on 13 Feb 1743 in St-Louis-de-Terrebonne, Terrebonne, Quebec, Canada, at age 71. 1700 in Chambly, Quebec, Canada.}
\marriage{Clement married \href{#}{\textcolor{accent}{\textbf{\underline{Marie-Madeleine Dupre}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Dupre}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elisabeth Valiquet}}}}, on 4 Jan}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Clement Charles was born on 9 Feb 1705 in Boucherville, Quebec, Canada}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 15 Mar 1779}}}}}
\childentryplain{in L'Assomption}{ii}{, Quebec, Canada, at age 74.}
\childentry{}{813 ii. Marie Charlotte Charles}
\childentryplain{1627. Marie-Madeleine Dupre}{iv}{, daughter of Antoine Dupre and Elisabeth Valiquet, was born on 14 Feb 1682 in}
\childentryplain{Boucherville}{v}{, Quebec, Canada and died on 11 Apr 1747 in Terrebonne, Les Moulins, Quebec, Canada, at age 65.}
\childentryplain{Marie-Madeleine married Clement Charles}{vi}{, son of Etienne Charles and Madeleine Niel, on 4 Jan 1700 in}
\childentryplain{Chambly}{vii}{, Quebec, Canada.}
\dividerline

\entry{1628}{Jean Francois Lavoie}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Rene de Lavoie}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Godin}}}}, was born in Jun 1660 in Ste Anne de Beaupre, Quebec, Canada and died on 8 Dec 1721 in Riviere-Ouelle, Kamouraska, Quebec, Canada, at age 61. 4 Nov 1683 in Ste Anne de Beaupre, Quebec, Canada.}
\marriage{Jean married \href{#}{\textcolor{accent}{\textbf{\underline{Marie-Madeleine Boucher}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean-Galeran Boucher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Helene Leclerc}}}}, on}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Lavoie was born on 22 Oct 1693 in Riviere-Ouelle, Kamouraska, Quebec, Canada and}}}}}
\childentryplain{died on 4 Jan 1773 in Riviere-Ouelle}{ii}{, Kamouraska, Quebec, Canada, at age 79.}
\childentry{}{814 ii. Augustin Lavoie}
\dividerline

\entry{1629}{Marie-Madeleine Boucher}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean-Galeran Boucher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Helene Leclerc}}}}, was born on 21 Jun 1670 in L'Ange Gardien, Beauce, Quebec, Canada and died on 3 Mar 1723 in Riviere-Ouelle, Kamouraska, Quebec, Canada, at age 52. Ste Anne de Beaupre, Quebec, Canada.}
\marriage{Marie-Madeleine married \href{#}{\textcolor{accent}{\textbf{\underline{Jean Francois Lavoie}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Rene de Lavoie}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Godin}}}}, on 4 Nov 1683 in}
\dividerline

\entry{1648}{Robert Morin}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Noel Morin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Helene Desportes}}}}, was born about 1674 in Champagne, Dordogne, Aquitaine, France and died on 28 Aug 1729 in Quebec, Canada, about age 55.}
\marriage{Robert married \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Mignier}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Andre Mignier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jacquette Michel}}}}.}
\childrenheading
\childentrylinked{824}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Pierre Joseph Morin}}}}}
\dividerline

\entry{1649}{Francoise Mignier}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Andre Mignier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jacquette Michel}}}}, was born on 27 Jun 1674 in Charlesbourg, Quebec, Canada and died on 29 Sep 1750 in La Pocatiere, Kamouraska, Quebec, Canada, at age 76.}
\marriage{Francoise married \href{#}{\textcolor{accent}{\textbf{\underline{Robert Morin}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Noel Morin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Helene Desportes}}}}.}
\dividerline

\entry{1650}{Mathurin Dube}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Mathurin Dube}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Marie Campion}}}}, was born on 27 Jan 1672 in I'lle d'Orleans, Montmorency, Quebec, Canada and died on 22 Nov 1725 in St Roch des Aulnaies, L'Islet, Quebec, Canada, at age 53. Langlois, on 13 May 1691 in Riviere-Ouelle, Kamouraska, Quebec, Canada.}
\marriage{Mathurin married \href{#}{\textcolor{accent}{\textbf{\underline{Anne Miville}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie}}}}}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Augustin Zacharie Dube was born on 13 Jan 1695 in Riviere-Ouelle,}}}}}
\childentryplain{Kamouraska}{ii}{, Quebec, Canada and died on 12 Nov 1779 in Riviere-Ouelle,}
\childentryplain{Kamouraska}{iii}{, Quebec, Canada, at age 84.}
\childentry{}{825 ii. Marie Charlotte Dube}
\childentryplain{1651. Anne Miville}{v}{, daughter of Francois Miville and Marie Langlois, was born on 27 Mar 1673 in Levis,}
\childentryplain{Chaudiere-Appalaches}{vi}{, Quebec, Canada and died on 11 Mar 1717 in La Pocatiere, Kamouraska, Quebec, Canada, at}
\childentry{}{age 43.}
\childentryplain{Anne married Mathurin Dube}{viii}{, son of Mathurin Dube and Catherine Marie Campion, on 13 May 1691 in}
\childentryplain{Riviere-Ouelle}{ix}{, Kamouraska, Quebec, Canada.}
\dividerline

\entry{1652}{Charles Miville}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Baillon}}}}, was born on 14 Aug 1677 in Quebec City, Quebec, Canada and died on 11 Feb 1758 in La Pocatiere, Kamouraska, Quebec, Canada, at age 80. Kamouraska, Quebec, Canada.}
\marriage{Charles married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Marthe Vallee}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Vallee}}}}, on 28 Aug 1702 in Riviere-Ouelle,}
\childrenheading
\childentrylinked{826}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jacques Miville}}}}}
\dividerline

\entry{1653}{Marie Marthe Vallee}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Vallee}}}}, was born on 24 Apr 1683 in Beauport, Quebec, Canada and died on 21 Mar 1748 in La Pocatiere, Kamouraska, Quebec, Canada, at age 64. Ouelle, Kamouraska, Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Charles Miville}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Baillon}}}}, on 28 Aug 1702 in Riviere-}
\dividerline

\entry{1654}{Pierre Roy}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Roy}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Major}}}}, was born in 1669 in Batiscan, Champlain, Quebec, Canada and died on 29 Apr 1734 in Repentigny, Assomption, Quebec, Canada, at age 65. Riviere-Ouelle, Kamouraska, Quebec, Canada.}
\marriage{Pierre married \href{#}{\textcolor{accent}{\textbf{\underline{Angelique Autin}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Autin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Boucher}}}}, on 25 Nov 1710 in}
\childrenheading
\childentrylinked{827}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Anne Roy}}}}}
\dividerline

\entry{1655}{Angelique Autin}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Autin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Boucher}}}}, was born on 9 Aug 1691 in Riviere-Ouelle, Kamouraska, Quebec, Canada and died on 17 Jun 1721 in Kamouraska, Kamouraska, Quebec, Canada, at age 29. Kamouraska, Quebec, Canada.}
\marriage{Angelique married \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Roy}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Roy}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Major}}}}, on 25 Nov 1710 in Riviere-Ouelle,}
\dividerline

\entry{1656}{Claude Panneton was born about 1664 in Lyon}{Auvergne-Rhone-Alpes, France and died on 9 Aug 1725 in Quebec City, Quebec, Canada, about age 61. 1687 in Sainte Famille, L'Ile-d'Orleans, Quebec, Canada.}
\marriage{Claude married \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Doison}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Sebastian Doison}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Marechal}}}}, on 30 Oct}
\childrenheading
\childentrylinked{828}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Claude Panneton}}}}}
\dividerline

\entry{1657}{Marguerite Doison}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Sebastian Doison}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Marechal}}}}, was born on 8 Feb 1671 in Sainte Famille, L'Ile-d'Orleans, Quebec, Canada and died on 31 Mar 1751 in Trois Rivieres, Kamouraska, Quebec, Canada, at age 80. 1658. Etienne Senecal, son of \href{#}{\textcolor{accent}{\textbf{\underline{Adrien Senecal}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne le Compte}}}}, was born on 16 Nov 1672 in Trois Rivieres, Kamouraska, Quebec, Canada and died on 20 Jun 1733 in Varennes, Monteregie, Quebec, Canada, at age 60. Varennes, Monteregie, Quebec, Canada.}
\marriage{Etienne married \href{#}{\textcolor{accent}{\textbf{\underline{Petronille Millault}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Millault}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Hebert}}}}, on 22 Apr 1694 in}
\childrenheading
\childentrylinked{829}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Petronille Senecal}}}}}
\dividerline

\entry{1659}{Petronille Millault}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Millault}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Hebert}}}}, was born on 24 Nov 1671 in Montreal, Quebec, Canada and died on 5 Nov 1758 in Varennes, Monteregie, Quebec, Canada, at age 86. Varennes, Monteregie, Quebec, Canada.}
\marriage{Petronille married \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Senecal}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Adrien Senecal}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne le Compte}}}}, on 22 Apr 1694 in}
\dividerline

\entry{1824}{Johann Adam Schaeffer .}{His child was: 912 i. Johann Martin Schaffer}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{someone.}}}}}
\dividerline

\entry{1826}{Johann Henrick "Hans" Lautenschlager}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Peter Lautenschlaeger}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Hoff}}}}, was born on 1 Jul 1694 in Laudenau, Starkenburg, Hesse, Germany and died on 20 Nov 1750 in Laudenau, Starkenburg, Hesse, Germany, at age 56.}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Elisabeth Seitz.}}}}}
\childrenheading
\childentrylinked{913}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Catherine Lautenschlager}}}}}
\dividerline

\entry{1827}{Anna Elisabeth Seitz was born in May 1696 in Gadernheim}{Bergestrasse, Hessen, Germany and died on 31 Jan 1729 in Laudenau, Starkenburg, Hesse, Germany, at age 32. Hoff.}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Henrick "Hans" Lautenschlager}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Peter Lautenschlaeger}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna}}}}}
\dividerline

\entry{1840}{Jacob Bitzer}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Caspar Bitzer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Hauser}}}}, was born on 10 Aug 1645 in Tailfingen, Boblingen, Baden-Wuerttemberg, Germany and died on 31 May 1693 in Tailfingen, Boblingen, Baden-Wuerttemberg, Germany, at age 47. Jun 1669 in Tailfingen, Boblingen, Baden-Wuerttemberg, Germany.}
\marriage{Jacob married \href{#}{\textcolor{accent}{\textbf{\underline{Catherina Conzelmann}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Georg Conzelmann}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Dorothea Fessler}}}}, on 19}
\childrenheading
\childentrylinked{920}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Conrad Bitzer}}}}}
\dividerline

\entry{1841}{Catherina Conzelmann}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Georg Conzelmann}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Dorothea Fessler}}}}, was born on 27 Apr 1652 in Tailfingen, Boblingen, Baden-Wuerttemberg, Germany and died on 12 Dec 1706 in Tailfingen, Boblingen, Baden-Wuerttemberg, Germany, at age 54. Boblingen, Baden-Wuerttemberg, Germany.}
\marriage{Catherina married \href{#}{\textcolor{accent}{\textbf{\underline{Jacob Bitzer}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Caspar Bitzer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Hauser}}}}, on 19 Jun 1669 in Tailfingen,}
\dividerline

\entry{1842}{Hans Balthas Hauser .}{}
\marriage{Hans married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Martha Comper.}}}}}
\childrenheading
\childentrylinked{921}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Maria Barbara Hauser}}}}}
\dividerline

\entry{1843}{Anna Martha Comper .}{}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Hans Balthas Hauser.}}}}}
\dividerline

\entry{1848}{Johan Jacob Boshaar}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Albert Boshaar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Margaretha Delagrevis}}}}, was born about 1647 in Zweibrucken, Zweibruckem, Rheinland-Pfalz, Germany and died on 6 Dec 1719 in Hurley, Ulster, NY, about age 72. in Breitenbach, Zweibrucken, Rheinland-Pfalz, Germany.}
\marriage{Johan married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Christina Maurer}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Conrad Maurer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Knoell}}}}, on 30 Jul 1693}
\childrenheading
\childentrylinked{924}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Johan Jorg Boshaar}}}}}
\dividerline

\entry{1849}{Anna Christina Maurer}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Conrad Maurer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Knoell}}}}, was born on 27 Dec 1673 in Hornbach, Pirmasens, Rheinland-Pfalz, Germany and died on 16 Mar 1730 in Hurley, Ulster, NY, at age 56. Delagrevis, on 30 Jul 1693 in Breitenbach, Zweibrucken, Rheinland-Pfalz, Germany.}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Johan Jacob Boshaar}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Albert Boshaar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Margaretha}}}}}
\dividerline

\entry{1850}{Balthazar Wennerich}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Wennerich}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Magdalena Elizabetha Krafft}}}}, was born about 1670 in Edigheim, Ludwigschafen-am-Rhein, Rheinland-Pfalz, Germany and died on 4 Aug 1725 in Tulphocken, Berkshire, PA, about age 55.}
\marriage{Balthazar married \href{#}{\textcolor{accent}{\textbf{\underline{Maria Elizabeth.}}}}}
\childrenheading
\childentrylinked{925}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Maria Wennerich}}}}}
\dividerline

\entry{1851}{Maria Elizabeth .}{}
\marriage{Maria married \href{#}{\textcolor{accent}{\textbf{\underline{Balthazar Wennerich}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Wennerich}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Magdalena Elizabetha Krafft}}}}.}
\dividerline

\entry{1884}{Anthony Parkin}{son of \href{#}{\textcolor{accent}{\textbf{\underline{James Parkin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Moore}}}}, was born about 1690 in St. Lawrence, Westmoreland, England and died on 1 Oct 1730 in St. Lawrence, Westmoreland, England, about age 40.}
\marriage{Anthony married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Robertson on 2 Jun 1709 in Ravenstonedale}}}}, Westmoreland, England.}
\childrenrenheading
\childentrylinked{942}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Thomas Parkin}}}}}
\childentryplain{1885. Elizabeth Robertson was born on 9 Oct 1684 in Ravenstonedale}{ii}{, Westmoreland, England and died in Jun}
\childentryplain{1736}{iii}{, at age 51.}
\childentryplain{Elizabeth married Anthony Parkin}{iv}{, son of James Parkin and Mary Moore, on 2 Jun 1709 in}
\childentryplain{Ravenstonedale}{v}{, Westmoreland, England.}
\dividerline

\entry{1886}{George Atkinson was born about 1710 in Westmoreland}{England.}
\marriage{George married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Thornborrow}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Thornborrow}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jennet Bellas}}}}.}
\childrenheading
\childentrylinked{943}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Janet Atkinson}}}}}
\dividerline

\entry{1887}{Catherine Thornborrow}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Thornborrow}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jennet Bellas}}}}, was born on 8 Apr 1711 in Dufton, Westmoreland, England and died on 29 Jul 1793 in Knock, Westmoreland, England, at age 82.}
\marriage{Catherine married \href{#}{\textcolor{accent}{\textbf{\underline{George Atkinson.}}}}}
\dividerline

\entry{1952}{Johann Georg Leonhard Hellenschmitt}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Georg Hellenschmitt}}}}, was born about 1690 in Schmalfelden, Schwabisch Hall, Baden-Wuerttemberg, Germany. Schmalfelden, Schwabisch Hall, Baden-Wuerttemberg, Germany.}
\marriage{Johann married \href{#}{\textcolor{accent}{\textbf{\underline{Sophia Botsch}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Caspar Botsch}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Eva Wirth}}}}, on 2 May 1713 in}
\childrenheading
\childentrylinked{976}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Johann Hellenschmitt}}}}}
\dividerline

\entry{1953}{Sophia Botsch}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Caspar Botsch}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Eva Wirth}}}}, was born on 17 Dec 1690 in Gerabronn, Schwabisch Hall, Baden-Wuerttemberg, Germany. in Schmalfelden, Schwabisch Hall, Baden-Wuerttemberg, Germany. 12th Generation}
\marriage{Sophia married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Georg Leonhard Hellenschmitt}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Georg Hellenschmitt}}}}, on 2 May 1713}
\dividerline

\entry{2112}{William Lean}{son of \href{#}{\textcolor{accent}{\textbf{\underline{John Leane}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Constance Treloar}}}}, was born on 8 Apr 1666 in Gwennap, Cornwall, England and died on 23 May 1738 in Gwennap, Cornwall, England, at age 72.}
\marriage{William married \href{#}{\textcolor{accent}{\textbf{\underline{Joan.}}}}}
\childrenheading
\childentrylinked{1056}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{John Lean}}}}}
\dividerline

\entry{2113}{Joan died on 15 May 1756 in Gwennap}{Cornwall, England.}
\marriage{Joan married \href{#}{\textcolor{accent}{\textbf{\underline{William Lean}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{John Leane}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Constance Treloar}}}}.}
\dividerline

\entry{2114}{Stephen Polkinghorn}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Samuel Polkinghorne}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Carter}}}}, was born about 1670 in Breage, Cornwall, England. His child was: 1057 i. Elizabeth Polkinghorn}
\marriage{Stephen married \href{#}{\textcolor{accent}{\textbf{\underline{someone.}}}}}
\dividerline

\entry{2128}{Thomas Trewren}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Trewren}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Harris}}}}, was born on 27 Apr 1639 in Sancreed, Cornwall, England and died on 22 Dec 1689 in Sancreed, Cornwall, England, at age 50. Cornwall, England.}
\marriage{Thomas married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Seyley}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Peter Ceely}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Honour Praed}}}}, on 2 Oct 1657 in Sancreed,}
\childrenheading
\childentrylinked{1064}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Joseph Trewren}}}}}
\dividerline

\entry{2129}{Catherine Seyley}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Peter Ceely}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Honour Praed}}}}, died in 1724 in Helston, Cornwall, England. Sancreed, Cornwall, England.}
\marriage{Catherine married \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Trewren}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Trewren}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Harris}}}}, on 2 Oct 1657 in}
\dividerline

\entry{2130}{John Couch}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Couch}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Dorothy Hurrell}}}}, was born about 1658 in Cornwall, England and died about 1695 in Lezant, Cornwall, England, about age 37. Cornwall, England.}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Mary Frethy}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Frethy}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Stephen}}}}, on 30 Apr 1681 in Roche,}
\childrenheading
\childentrylinked{1065}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Couch}}}}}
\dividerline

\entry{2131}{Mary Frethy}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Frethy}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Stephen}}}}, was born on 25 May 1658 in St. Veep, Cornwall, England and died in Nov 1730 in St. Austell, Cornwall, England, at age 72. England.}
\marriage{Mary married \href{#}{\textcolor{accent}{\textbf{\underline{John Couch}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Couch}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Dorothy Hurrell}}}}, on 30 Apr 1681 in Roche, Cornwall,}
\dividerline

\entry{2132}{George Blight}{son of \href{#}{\textcolor{accent}{\textbf{\underline{George Blight}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joane Sampson}}}}, was born about 1655 in Cornwall, England and died on 9 Apr 1710 in Ludgvan, Cornwall, England, about age 55. Illogan, Cornwall, England.}
\marriage{George married \href{#}{\textcolor{accent}{\textbf{\underline{Philippa James}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Ephraim James}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jane Christover}}}}, on 22 Sep 1674 in}
\childrenheading
\childentrylinked{1066}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Ephraim Blight}}}}}
\dividerline

\entry{2133}{Philippa James}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Ephraim James}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jane Christover}}}}, was born on 20 Aug 1657 in Ludgvan, Cornwall, England and died in Mar 1698 in Ludgvan, Cornwall, England, at age 40. Cornwall, England.}
\marriage{Philippa married \href{#}{\textcolor{accent}{\textbf{\underline{George Blight}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{George Blight}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joane Sampson}}}}, on 22 Sep 1674 in Illogan,}
\dividerline

\entry{2134}{Samuel Sampson was born about 1650 in Ludgvan}{Cornwall, England and died on 4 Sep 1713 in Ludgvan, Cornwall, England, about age 63. Ludgvan, Cornwall, England.}
\marriage{Samuel married \href{#}{\textcolor{accent}{\textbf{\underline{Margery Christopher}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Christopher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joie}}}}, on 30 Jun 1672 in}
\childrenheading
\childentrylinked{1067}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jane Sampson}}}}}
\dividerline

\entry{2135}{Margery Christopher}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Christopher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joie}}}}, was born on 22 Jan 1647 in Ludgvan, Cornwall, England and died on 10 Apr 1689 in Ludgvan, Cornwall, England, at age 42.}
\marriage{Margery married \href{#}{\textcolor{accent}{\textbf{\underline{Samuel Sampson on 30 Jun 1672 in Ludgvan}}}}, Cornwall, England.}
\dividerline

\entry{2136}{Richard Hall}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Hall}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marion Carnepessack}}}}, was born on 9 Oct 1665 in Madron, Cornwall, England and died on 29 Apr 1761 in Madron, Cornwall, England, at age 95. Redbourn, Hertfordshire, England.}
\marriage{Richard married \href{#}{\textcolor{accent}{\textbf{\underline{Mary Nicholls}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Nicholls}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Amy Morish}}}}, on 21 Sep 1704 in}
\childrenheading
\childentrylinked{1068}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Thomas Hall}}}}}
\dividerline

\entry{2137}{Mary Nicholls}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Nicholls}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Amy Morish}}}}, was born on 14 Jul 1667 in Gulval, Cornwall, England and died in Gulval, Cornwall, England. Hertfordshire, England.}
\marriage{Mary married \href{#}{\textcolor{accent}{\textbf{\underline{Richard Hall}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Hall}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marion Carnepessack}}}}, on 21 Sep 1704 in Redbourn,}
\dividerline

\entry{2138}{John Gomer}{son of \href{#}{\textcolor{accent}{\textbf{\underline{John Gomer}}}}, was born about 1670 in Paul, Cornwall, England and died about 1723, about age 53. Cornwall, England.}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Sampson}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Sampson}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth}}}}, on 27 Nov 1686 in Paul,}
\childrenheading
\childentrylinked{1069}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Gomer}}}}}
\dividerline

\entry{2139}{Elizabeth Sampson}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Sampson}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth}}}}, was born in Jan 1666 in Paul, Cornwall, England and died on 3 Aug 1742 in Surrey, England, at age 76.}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{John Gomer}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{John Gomer}}}}, on 27 Nov 1686 in Paul, Cornwall, England.}
\dividerline

\entry{2140}{John Tresise}{son of \href{#}{\textcolor{accent}{\textbf{\underline{John Tresise}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joan Paine}}}}, was born on 1 Feb 1660 in Penwith, Cornwall, England and died in 1724 in Penwith, Cornwall, England, at age 64. Cornwall, England.}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Mary Wallish}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{George Wallish}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Shepard}}}}, on 11 Jan 1689 in Penwith,}
\childrenheading
\childentrylinked{1070}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{William Tresise}}}}}
\dividerline

\entry{2141}{Mary Wallish}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{George Wallish}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Shepard}}}}, was born on 20 Apr 1667 in Penwith, Cornwall, England and died about 1745, about age 78. England.}
\marriage{Mary married \href{#}{\textcolor{accent}{\textbf{\underline{John Tresise}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{John Tresise}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joan Paine}}}}, on 11 Jan 1689 in Penwith, Cornwall,}
\dividerline

\entry{2142}{Emanuel Trenbath}{son of \href{#}{\textcolor{accent}{\textbf{\underline{John Trenbath}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary James}}}}, was born on 9 May 1668 in Penwith, Cornwall, England and died in Nov 1729 in Penwith, Cornwall, England, at age 61.}
\marriage{Emanuel married \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Warrin}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Warrin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Ann White}}}}.}
\childrenheading
\childentrylinked{1071}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Loveday Trenbath}}}}}
\dividerline

\entry{2143}{Margaret Warrin}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Warrin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Ann White}}}}, was born on 16 Apr 1665 in Penwith, Cornwall, England and died in Nov 1729 in Cornwall, England, at age 64.}
\marriage{Margaret married \href{#}{\textcolor{accent}{\textbf{\underline{Emanuel Trenbath}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{John Trenbath}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary James}}}}.}
\dividerline

\entry{2160}{William Perry}{son of \href{#}{\textcolor{accent}{\textbf{\underline{William Perry}}}}, was born about 1622 in Wendron, Cornwall, England and died in 1691, about age 69.}
\marriage{William married \href{#}{\textcolor{accent}{\textbf{\underline{Mary Symons}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Symons}}}}.}
\childrenheading
\childentrylinked{1080}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Zacharias Perry}}}}}
\dividerline

\entry{2161}{Mary Symons}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Symons}}}}, was born about 1633 in Wendron, Cornwall, England.}
\marriage{Mary married \href{#}{\textcolor{accent}{\textbf{\underline{William Perry}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{William Perry}}}}.}
\dividerline

\entry{2162}{Matthew Jenkin}{son of \href{#}{\textcolor{accent}{\textbf{\underline{John Jenkin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Dunstone}}}}, was born on 24 Feb 1643 in Wendron, Cornwall, England and died about 1700 in Cornwall, England, about age 57. Cornwall, England.}
\marriage{Matthew married \href{#}{\textcolor{accent}{\textbf{\underline{Alice Clise}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{James Clise}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Grace Moore}}}}, on 24 Nov 1664 in Wendron,}
\childrenheading
\childentrylinked{1081}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Anne Jenkin}}}}}
\dividerline

\entry{2163}{Alice Clise}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{James Clise}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Grace Moore}}}}, was born on 9 May 1645 in Breage, Cornwall, England and died on 28 Jan 1699 in Breage, Cornwall, England, at age 53. Cornwall, England.}
\marriage{Alice married \href{#}{\textcolor{accent}{\textbf{\underline{Matthew Jenkin}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{John Jenkin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Dunstone}}}}, on 24 Nov 1664 in Wendron,}
\dividerline

\entry{2164}{James John .}{His child was: 1082 i. Gye John}
\marriage{James married \href{#}{\textcolor{accent}{\textbf{\underline{someone.}}}}}
\dividerline

\entry{2166}{William Shoal .}{}
\marriage{William married \href{#}{\textcolor{accent}{\textbf{\underline{Jane.}}}}}
\childrenheading
\childentrylinked{1083}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Ann Shoal}}}}}
\dividerline

\entry{2167}{Jane .}{}
\marriage{Jane married \href{#}{\textcolor{accent}{\textbf{\underline{William Shoal.}}}}}
\dividerline

\entry{2168}{William Rutter was born about 1650 in Wendron}{Cornwall, England and died about 1690 in Cornwall, England, about age 40.}
\marriage{William married \href{#}{\textcolor{accent}{\textbf{\underline{Katherine Pruste}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Hugh Pruste}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Wadland}}}}.}
\childrenheading
\childentrylinked{1084}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Bartholomew Rutter}}}}}
\dividerline

\entry{2169}{Katherine Pruste}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Hugh Pruste}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Wadland}}}}, was born about 1651 in Wendron, Cornwall, England and died in 1689 in Cornwall, England, about age 38.}
\marriage{Katherine married \href{#}{\textcolor{accent}{\textbf{\underline{William Rutter.}}}}}
\dividerline

\entry{2170}{Nicholas John was born on 10 Dec 1628 in Wendron}{Cornwall, England and died on 12 Oct 1702 in Wendron, Cornwall, England, at age 73.}
\marriage{Nicholas married \href{#}{\textcolor{accent}{\textbf{\underline{Joan.}}}}}
\childrenheading
\childentrylinked{1085}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Katherine John}}}}}
\dividerline

\entry{2171}{Joan .}{}
\marriage{Joan married \href{#}{\textcolor{accent}{\textbf{\underline{Nicholas John.}}}}}
\dividerline

\entry{2174}{Thomas Pascoe .}{His child was: 1087 i. Jane Pascoe}
\marriage{Thomas married \href{#}{\textcolor{accent}{\textbf{\underline{someone.}}}}}
\dividerline

\entry{3210}{Guillaume Morel was born on 15 Nov 1630 in Saint-Germain-sur-Ille}{Ille-et-Vilaine, Bretagne, France and died on 30 Oct 1679 in Beaupre, Montmorency, Quebec, France, at age 48. His child was: 1605 i. Anne Morel 3212. Jacques Boivin was born about 1620 in France and died on 24 Jul 1704 in Montreal, Quebec, Canada, about age 84.}
\marriage{Jacques married \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Blois}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Blois}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Masson}}}}.}
\childrenheading
\childentrylinked{1606}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Michel Boivin}}}}}
\dividerline

\entry{3213}{Marguerite Blois}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Blois}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Masson}}}}, was born in Sarthe, Pays-de-la-Loire, France and died on 16 Dec 1723 in Montreal, Quebec, Canada.}
\marriage{Marguerite married \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Boivin.}}}}}
\dividerline

\entry{3214}{Pierre Lorrain was born on 1 Jan 1629 in Angers}{Maine-et-Loire, Pays-de-la-Loire, France and died on 7 Oct 1687 in Montreal, Quebec, Canada, at age 58.}
\marriage{Pierre married \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Saulnier.}}}}}
\childrenheading
\childentrylinked{1607}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Francoise Lorrain}}}}}
\dividerline

\entry{3215}{Francoise Saulnier was born about 1638 in Paris}{Ile-de-France, France and died on 3 Nov 1706 in Quebec, Canada, about age 68.}
\marriage{Francoise married \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Lorrain.}}}}}
\dividerline

\entry{3216}{Pierre Favreau}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Martin Favreau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Lecour}}}}, was born on 13 Jun 1636 in Dole, Jura, Franche-Comte, France and died on 26 May 1708 in Contrecoeur, Lajemmerais, Quebec, Canada, at age 71. Vercheres, Lajemmerais, Quebec, Canada.}
\marriage{Pierre married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Benoit}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Benoit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Christine}}}}, on 4 Jan 1666 in}
\childrenheading
\childentrylinked{1608}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Favreau}}}}}
\dividerline

\entry{3217}{Marie Madeleine Benoit}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Benoit}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Christine}}}}, died on 11 Dec 1733 in Montreal, Quebec, Canada. Lajemmerais, Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Favreau}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Martin Favreau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Lecour}}}}, on 4 Jan 1666 in Vercheres,}
\dividerline

\entry{3218}{Pierre Meunier}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Noel Meunier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Antoinette Guibourg}}}}, was born on 1 Jan 1643 in Rennes, Ille-et- Vilaine, Bretagne, France and died on 4 Jan 1695 in Boucherville, Chambly, Quebec, Canada, at age 52.}
\marriage{Pierre married \href{#}{\textcolor{accent}{\textbf{\underline{Barbe Richaume}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Richaume}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marthe Marie Arnus}}}}.}
\childrenheading
\childentrylinked{1609}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Barbe Meunier}}}}}
\dividerline

\entry{3219}{Barbe Richaume}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Richaume}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marthe Marie Arnus}}}}, was born on 22 Jun 1659 in Montreal, Quebec, Canada and died on 17 Jan 1725 in Contrecoeur, Lajemmerais, Quebec, Canada, at age 65.}
\marriage{Barbe married \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Meunier}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Noel Meunier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Antoinette Guibourg}}}}.}
\dividerline

\entry{3222}{Jean Deniau}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Deniau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Gaudet}}}}, was born about 1630 in St. Croix, Nantes, Bretagne, France and died on 12 Aug 1695 in Boucherville, Chambly, Quebec, Canada, about age 65.}
\marriage{Jean married \href{#}{\textcolor{accent}{\textbf{\underline{Helene Daudin.}}}}}
\childrenheading
\childentrylinked{1611}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Marguerite Deniau}}}}}
\dividerline

\entry{3223}{Helene Daudin was born on 25 Aug 1643 in Ile-de-Rhe}{Charente-Maritime, Poitou-Charentes, France.}
\marriage{Helene married \href{#}{\textcolor{accent}{\textbf{\underline{Jean Deniau}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Deniau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Gaudet}}}}.}
\dividerline

\entry{3226}{Jacques Vernin was born about 1621 in Angouleme}{Charente, Poitou-Charentes, France and died in 1681 in Richelieu, Quebec, Canada, about age 60.}
\marriage{Jacques married \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Martaguet.}}}}}
\childrenheading
\childentrylinked{1613}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Francoise Denise Vernin}}}}}
\dividerline

\entry{3227}{Francoise Martaguet was born about 1618 in France and died on 17 Oct 1678}{about age 60.}
\marriage{Francoise married \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Vernin.}}}}}
\dividerline

\entry{3228}{Daniel Neveu was born about 1645 in Coutances}{Manche, Basse-Normandie, France and died in Coutances, Manche, Basse-Normandie, France.}
\marriage{Daniel married \href{#}{\textcolor{accent}{\textbf{\underline{Anne Sain.}}}}}
\childrenheading
\childentrylinked{1614}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Francois Neveu}}}}}
\dividerline

\entry{3229}{Anne Sain .}{}
\marriage{Anne married \href{#}{\textcolor{accent}{\textbf{\underline{Daniel Neveu.}}}}}
\dividerline

\entry{3230}{Antoine Chaudillon}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Claude Chaudillon}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Antoinette Tin}}}}, was born about 1643 in Bourbonnais, France and died on 6 Oct 1707 in Pointe-aux-Trembles, Quebec, Canada, about age 64.}
\marriage{Antoine married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Francoise.}}}}}
\childrenheading
\childentrylinked{1615}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Catherine Chaudillon}}}}}
\dividerline

\entry{3231}{Marie Francoise .}{3232. Nicolas Proteau, son of \href{#}{\textcolor{accent}{\textbf{\underline{Thierry Proteau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Madeleine Parisot}}}}, was born about 1615 in Montreuil, Maine- et-Loire, Pays de la Loire, France and died on 13 Mar 1672 in Avize, Marne, Champagne-Ardenne, France, about age}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Chaudillon}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Claude Chaudillon}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Antoinette Tin}}}}.}
\dividerline

\entry{57}{Nicolas married Francoise Sautret}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Sautret}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Perette Fournier}}}}.}
\childrenheading
\childentrylinked{1616}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Etienne Proteau}}}}}
\dividerline

\entry{3233}{Francoise Sautret}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Sautret}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Perette Fournier}}}}, died on 24 Jun 1691.}
\marriage{Francoise married \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Proteau}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Thierry Proteau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Madeleine Parisot}}}}.}
\dividerline

\entry{3234}{Francois Seguin was born on 23 Jan 1614 in Beauvais}{L'Oise, Picardie, France and died on 9 May 1704 in Hotel Dieu, Quebec, Canada, at age 90.}
\marriage{Francois married \href{#}{\textcolor{accent}{\textbf{\underline{Simone Verret.}}}}}
\childrenheading
\childentrylinked{1617}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Seguin}}}}}
\dividerline

\entry{3235}{Simone Verret .}{}
\marriage{Simone married \href{#}{\textcolor{accent}{\textbf{\underline{Francois Seguin.}}}}}
\dividerline

\entry{3238}{Francois Bellehache was born about 1630 in Rouen}{Seine-Maritime, Haute-Normandie, France.}
\marriage{Francois married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Burelle.}}}}}
\childrenheading
\childentrylinked{1619}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Bellehache}}}}}
\dividerline

\entry{3239}{Marie Burelle was born in Mar 1636 in Rouen}{Seine-Maritime, Haute-Normandie, France and died in 1698 in Rouen, Seine-Maritime, Haute-Normandie, France, at age 62.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Francois Bellehache.}}}}}
\dividerline

\entry{3240}{Robert Bruneau .}{}
\marriage{Robert married \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Charbonnier.}}}}}
\childrenheading
\childentrylinked{1620}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Francois Bruneau}}}}}
\dividerline

\entry{3241}{Francoise Charbonnier .}{}
\marriage{Francoise married \href{#}{\textcolor{accent}{\textbf{\underline{Robert Bruneau.}}}}}
\dividerline

\entry{3242}{Antoine Prevost was born about 1620 in France.}{}
\marriage{Antoine married \href{#}{\textcolor{accent}{\textbf{\underline{Marie.}}}}}
\childrenheading
\childentrylinked{1621}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Prevost}}}}}
\dividerline

\entry{3243}{Marie .}{}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Prevost.}}}}}
\dividerline

\entry{3244}{Francois Bourgouin .}{}
\marriage{Francois married \href{#}{\textcolor{accent}{\textbf{\underline{Andree.}}}}}
\childrenheading
\childentrylinked{1622}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Pierre Bourgouin}}}}}
\dividerline

\entry{3245}{Andree .}{}
\marriage{Andree married \href{#}{\textcolor{accent}{\textbf{\underline{Francois Bourgouin.}}}}}
\dividerline

\entry{3246}{Guillaume Basset .}{}
\marriage{Guillaume married \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Carrier.}}}}}
\childrenheading
\childentrylinked{1623}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Catherine Basset}}}}}
\dividerline

\entry{3247}{Marguerite Carrier .}{}
\marriage{Marguerite married \href{#}{\textcolor{accent}{\textbf{\underline{Guillaume Basset.}}}}}
\dividerline

\entry{3248}{Paul Benoit was born on 26 Jan 1626 in Chatillon}{Allier, Auvergne, France and died on 1 Jan 1686 in Longueuil, Quebec, Canada, at age 59. Sep 1658 in Montreal, Quebec, Canada.}
\marriage{Paul married \href{#}{\textcolor{accent}{\textbf{\underline{Elisabeth Isabelle Gobinet}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Gobinet}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Lorgeleux}}}}, on 16}
\childrenheading
\childentrylinked{1624}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Etienne Benoit}}}}}
\dividerline

\entry{3249}{Elisabeth Isabelle Gobinet}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Gobinet}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Lorgeleux}}}}, was born about 1642 in Paris, Ile-de-France, France and died on 3 Apr 1715 in Longueuil, Quebec, Canada, about age 73.}
\marriage{Elisabeth married \href{#}{\textcolor{accent}{\textbf{\underline{Paul Benoit on 16 Sep 1658 in Montreal}}}}, Quebec, Canada.}
\dividerline

\entry{3250}{Etienne Campeau was born on 3 Apr 1638 in Brive-la-Gaillarde Limoges}{Limousin, France and died on 24 Sep 1692 in Montreal, Quebec, Canada, at age 54.}
\marriage{Etienne married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Paulo.}}}}}
\childrenrenheading
\childentrylinked{1625}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Jeanne Campeau}}}}}
\childentryplain{3251. Catherine Paulo was born about 1646 in La Rochelle}{ii}{, Manche, Basse-Normandie, France and died on 16 Apr}
\childentryplain{1721 in Montreal}{iii}{, Quebec, Canada, about age 75.}
\childentry{}{Catherine married Etienne Campeau.}
\dividerline

\entry{3252}{Etienne Charles}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Charles}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Colombe Regnault}}}}, was born on 11 Jun 1643 in Creteil, Paris, Ile-de-France, France and died on 16 May 1724 in Le Tremblay, Dorchester, Quebec, France, at age 80.}
\marriage{Etienne married \href{#}{\textcolor{accent}{\textbf{\underline{Madeleine Niel on 24 Oct 1667 in Trois-Rivieres}}}}, Quebec, Canada.}
\childrenheading
\childentrylinked{1626}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Clement Charles}}}}}
\dividerline

\entry{3253}{Madeleine Niel was born in 1652 in Rouen}{Seine-Maritime, Haute-Normandie, France and died on 15 Aug 1732 in St Francois, Ile Jesus, Quebec, Canada, at age 80. Trois-Rivieres, Quebec, Canada.}
\marriage{Madeleine married \href{#}{\textcolor{accent}{\textbf{\underline{Etienne Charles}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Francois Charles}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Colombe Regnault}}}}, on 24 Oct 1667 in}
\dividerline

\entry{3254}{Antoine Dupre was born about 1645 in Lyon}{Rhone, Rhone-Alpes, France and died on 19 Sep 1689 in Chambly, Quebec, Canada, about age 44. Chambly, Quebec, Canada.}
\marriage{Antoine married \href{#}{\textcolor{accent}{\textbf{\underline{Elisabeth Valiquet}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Valiquet}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Renee Loppe}}}}, on 28 Apr 1681 in}
\childrenheading
\childentrylinked{1627}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie-Madeleine Dupre}}}}}
\dividerline

\entry{3255}{Elisabeth Valiquet}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Valiquet}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Renee Loppe}}}}, was born on 27 Apr 1665 in Montreal, Quebec, Canada and died on 22 Jul 1740 in Chambly, Quebec, Canada, at age 75.}
\marriage{Elisabeth married \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Dupre on 28 Apr 1681 in Chambly}}}}, Quebec, Canada.}
\dividerline

\entry{3256}{Rene de Lavoie}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Rene de Lavoie}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Isabelle Belanger}}}}, was born on 28 Nov 1628 in St Maclou, Rouen, Normandie, France and died on 11 Mar 1696 in Chateau-Richer, La Cote-de-Beaupre, Quebec, Canada, at age}
\dividerline

\entry{67}{Rene married Anne Godin}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Elie Gaudin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Esther Marie Ramage}}}}, on 19 Apr 1656 in Quebec City, Quebec, Canada.}
\childrenheading
\childentrylinked{1628}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jean Francois Lavoie}}}}}
\dividerline

\entry{3257}{Anne Godin}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Elie Gaudin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Esther Marie Ramage}}}}, was born on 16 Oct 1639 in La Rochelle, Manche, Basse-Normandie, France and died on 26 Feb 1678 in Ste Anne de Beaupre, Quebec, Canada, at age 38. City, Quebec, Canada.}
\marriage{Anne married \href{#}{\textcolor{accent}{\textbf{\underline{Rene de Lavoie}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Rene de Lavoie}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Isabelle Belanger}}}}, on 19 Apr 1656 in Quebec}
\dividerline

\entry{3258}{Jean-Galeran Boucher}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Marin Boucher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Julienne Baril}}}}, was born on 16 Feb 1632 in St Langis les Mortagne, Perche, France and died on 28 Mar 1714 in Riviere-Ouelle, Kamouraska, Quebec, Canada, at age 82. 1661 in Chateau-Richer, La Cote-de-Beaupre, Quebec, Canada.}
\marriage{Jean-Galeran married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Helene Leclerc}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jonas Leclerc}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Parmentier}}}}, on 10 Oct}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Boucher was born on 26 Feb 1663 in Chateau-Richer, La Cote-de-Beaupre, Quebec, Canada}}}}}
\childentryplain{and died in Nov 1704 in Riviere-Ouelle}{ii}{, Kamouraska, Quebec, Canada, at age 41.}
\childentry{}{1629 ii. Marie-Madeleine Boucher}
\dividerline

\entry{3259}{Marie Helene Leclerc}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jonas Leclerc}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Parmentier}}}}, was born on 13 Feb 1633 in Dieppe, Seine-Maritime, Haute-Normandie, France and died on 8 Oct 1702 in Chateau-Richer, La Cote-de-Beaupre, Quebec, Canada, at age 69. Chateau-Richer, La Cote-de-Beaupre, Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Jean-Galeran Boucher}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Marin Boucher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Julienne Baril}}}}, on 10 Oct 1661 in}
\dividerline

\entry{3296}{Noel Morin}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Claude Morin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Moreau}}}}, was born about 1616 in St-Etienne-de-Brie-Comte- Robert, Brie, France and died on 10 Feb 1679 in St-Francois-de-la-Riviere-de-Sud, Montmagny, Quebec, Canada, about age 63. Quebec, Canada.}
\marriage{Noel married \href{#}{\textcolor{accent}{\textbf{\underline{Helene Desportes}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Desportes}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Langlois}}}}, on 9 Jan 1640 in}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Agnes Morin was born on 21 Jan 1641 in Quebec, Canada}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 30 Aug 1687 in Quebec,}}}}}
\childentryplain{Canada}{ii}{, at age 46.}
\childentry{}{1648 ii. Robert Morin}
\dividerline

\entry{3297}{Helene Desportes}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Desportes}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Langlois}}}}, was born on 7 Jul 1620 in Lisieux, Calvados, Basse-Normandie, France and died on 24 Jun 1675 in Quebec, Canada, at age 54.}
\marriage{Helene married \href{#}{\textcolor{accent}{\textbf{\underline{Noel Morin}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Claude Morin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Moreau}}}}, on 9 Jan 1640 in Quebec, Canada.}
\dividerline

\entry{3298}{Andre Mignier}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Michel Mignier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Masson}}}}, was born about 1640 in France and died on 21 Nov 1727 in La Pocatiere, Kamouraska, Quebec, Canada, about age 87. Quebec City, Quebec, Canada.}
\marriage{Andre married \href{#}{\textcolor{accent}{\textbf{\underline{Jacquette Michel}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Michel}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Dupont}}}}, on 23 Oct 1668 in}
\childrenheading
\childentrylinked{1649}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Francoise Mignier}}}}}
\dividerline

\entry{3299}{Jacquette Michel}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Michel}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Dupont}}}}, died on 28 Nov 1710 in Riviere-Ouelle, Kamouraska, Quebec, Canada. City, Quebec, Canada.}
\marriage{Jacquette married \href{#}{\textcolor{accent}{\textbf{\underline{Andre Mignier}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Michel Mignier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Masson}}}}, on 23 Oct 1668 in Quebec}
\dividerline

\entry{3300}{Mathurin Dube was born about 1631 in Vendee}{Pays de la Loire, France and died on 28 Dec 1695 in Riviere- Ouelle, Kamouraska, Quebec, Canada, about age 64. and Marie Marguerite Henault, on 3 Sep 1670 in I'lle d'Orleans, Montmorency, Quebec, Canada.}
\marriage{Mathurin married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Marie Campion}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Campion}}}}}
\childrenheading
\childentrylinked{1650}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Mathurin Dube}}}}}
\dividerline

\entry{3301}{Catherine Marie Campion}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Campion}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Marguerite Henault}}}}, was born in Rouen, Seine-Maritime, Haute-Normandie, France and died on 28 Jan 1697 in Riviere-Ouelle, Kamouraska, Quebec, Canada. Montmorency, Quebec, Canada.}
\marriage{Catherine married \href{#}{\textcolor{accent}{\textbf{\underline{Mathurin Dube on 3 Sep 1670 in I'lle d'Orleans}}}},}
\dividerline

\entry{3302}{Francois Miville}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Maugis}}}}, was born on 16 May 1634 in Brouage, Charente-Maritime, Poitou-Charentes, France and died on 23 Nov 1711 in Riviere-Ouelle, Kamouraska, Quebec, Canada, at age 77. Quebec City, Quebec, Canada.}
\marriage{Francois married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Langlois}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Noel Langlois}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Grenier}}}}, on 23 Aug 1649 in}
\childrenheading
\childentrylinked{1651}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Anne Miville}}}}}
\dividerline

\entry{3303}{Marie Langlois}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Noel Langlois}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Grenier}}}}, was born on 18 Oct 1646 in Quebec City, Quebec, Canada and died on 14 Aug 1687 in Quebec City, Quebec, Canada, at age 40. City, Quebec, Canada.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Francois Miville}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Maugis}}}}, on 23 Aug 1649 in Quebec}
\dividerline

\entry{3304}{Jacques Miville}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Maugis}}}}, was born on 2 May 1639 in Brouage, Charente, Poitou-Charentes, France and died about 1688 in Riviere-Ouelle, Kamouraska, Quebec, Canada, about age 49. Quebec, Canada.}
\marriage{Jacques married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Baillon}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Alphonse Baillon}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Louise de Marle}}}}, on 12 Nov 1669 in}
\childrenheading
\childentrylinked{1652}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Charles Miville}}}}}
\dividerline

\entry{3305}{Catherine Baillon}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Alphonse Baillon}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Louise de Marle}}}}, was born about 1645 in Montfort, Chartres, Ille-et-Vilaine, Bretagne, France and died on 27 Jan 1688 in Riviere-Ouelle, Kamouraska, Quebec, Canada, about age 43. Canada.}
\marriage{Catherine married \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Miville}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Maugis}}}}, on 12 Nov 1669 in Quebec,}
\dividerline

\entry{3306}{Pierre Vallee}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Vallee}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Dumesnil}}}}, was born on 6 Jun 1636 in Saint-Saens, Seine-Maritime, Haute-Normandie, France and died on 21 Oct 1686 in Quebec City, Quebec, Canada, at age 50. His child was: 1653 i. Marie Marthe Vallee 3308. Antoine Roy, son of \href{#}{\textcolor{accent}{\textbf{\underline{Olivier Roy}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Boderge}}}}, was born on 23 Mar 1635 in Joigny, Yonne, Bourgogne, France and died on 10 Jul 1684 in Lachine, Montreal, Quebec, Canada, at age 49.}
\marriage{Antoine married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Major}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Major}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite le Pele}}}}.}
\childrenheading
\childentrylinked{1654}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Pierre Roy}}}}}
\dividerline

\entry{3309}{Marie Major}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Major}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite le Pele}}}}, was born on 26 Feb 1637 in Touques, Calvados, Basse-Normandie, France and died on 8 Dec 1689 in Quebec City, Quebec, Canada, at age 52.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Roy}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Olivier Roy}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Boderge}}}}.}
\dividerline

\entry{3310}{Francois Autin was born in 1660 in Champagne}{Dordogne, Aquitaine, France and died in 1725 in Controt, Fillion, Quebec, Canada, at age 65. 1675 in Quebec, Canada.}
\marriage{Francois married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Boucher}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean-Galeran Boucher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Helene Leclerc}}}}, on 14 Sep}
\childrenrenheading
\childentrylinked{1655}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Angelique Autin}}}}}
\childentrylinked{--}{ii}{\href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Autin was born on 22 Nov 1693 in Riviere-Ouelle, Kamouraska, Quebec, Canada}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died}}}}}
\childentryplain{on 8 Nov 1718 in Kamouraska}{iii}{, Kamouraska, Quebec, Canada, at age 24.}
\dividerline

\entry{3311}{Marie Boucher}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean-Galeran Boucher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Helene Leclerc}}}}, was born on 26 Feb 1663 in Chateau-Richer, La Cote-de-Beaupre, Quebec, Canada and died in Nov 1704 in Riviere-Ouelle, Kamouraska, Quebec, Canada, at age 41.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Francois Autin on 14 Sep 1675 in Quebec}}}}, Canada.}
\dividerline

\entry{3314}{Sebastian Doison}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Aubin Doison}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Chartier}}}}, was born about 1621 in Nantes, Haute, Bretagne, France and died on 1 Jan 1685 in Sainte Famille, L'Ile-d'Orleans, Quebec, Canada, about age 64. in Montmorency, Ile d'Orleans, Quebec, Canada.}
\marriage{Sebastian married \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Marechal}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Marechal}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Dubois}}}}, on 2 Nov 1669}
\childrenheading
\childentrylinked{1657}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Doison}}}}}
\dividerline

\entry{3315}{Marguerite Marechal}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Marechal}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Dubois}}}}, was born about 1636 in Bellac, Haute-Vienne, Limousin, France and died on 14 Mar 1698 in Quebec City, Quebec, Canada, about age 62. Montmorency, Ile d'Orleans, Quebec, Canada.}
\marriage{Marguerite married \href{#}{\textcolor{accent}{\textbf{\underline{Sebastian Doison}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Aubin Doison}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Chartier}}}}, on 2 Nov 1669 in}
\dividerline

\entry{3316}{Adrien Senecal}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Senecal}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Gertrude Petit}}}}, was born about 1620 in Benouville, Calvados, Basse-Normandie, France and died on 19 Aug 1688 in Boucherville, Chambly, Quebec, Canada, about age}
\dividerline

\entry{68}{Adrien married Jeanne le Compte}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Lecompte}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Monnette}}}}.}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Henri Senecal was born in 1672 in Trois Rivieres, Kamouraska, Quebec, Canada}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 27 Mar}}}}}
\childentryplain{1719 in Chambly}{ii}{, Quebec, Canada, at age 47.}
\childentry{}{1658 ii. Etienne Senecal}
\dividerline

\entry{3317}{Jeanne le Compte}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Lecompte}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Monnette}}}}, was born about 1637 in St Martin, Harfleur, Seine-Maritime, Normandie, France and died on 10 Feb 1694 in Varennes, Monteregie, Quebec, Canada, about age 57.}
\marriage{Jeanne married \href{#}{\textcolor{accent}{\textbf{\underline{Adrien Senecal}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Senecal}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Gertrude Petit}}}}.}
\dividerline

\entry{3318}{Jacques Millault was born about 1629 in Crouzille}{Le Mans, Maine, France and died on 15 Aug 1699 in Montreal, Quebec, Canada, about age 70.}
\marriage{Jacques married \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Hebert}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Augustin Hebert}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Adrienne du Vivier}}}}.}
\childrenheading
\childentrylinked{1659}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Petronille Millault}}}}}
\dividerline

\entry{3319}{Jeanne Hebert}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Augustin Hebert}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Adrienne du Vivier}}}}, was born in 1647 in Montreal, Quebec, Canada and died on 25 Mar 1687 in Montreal, Quebec, Canada, at age 40.}
\marriage{Jeanne married \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Millault.}}}}}
\dividerline

\entry{3652}{Johann Peter Lautenschlaeger}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Adam Lautenschlaeger}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Ihrig}}}}, was born on 14 May 1654 in Laudenau, Starkenburg, Hesse, Germany and died on 23 Dec 1710 in Laudenau, Starkenburg, Hesse, Germany, at age}
\dividerline

\entry{56}{Johann married Anna Hoff}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Georg Hoff}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catharina Kistler}}}}.}
\childrenheading
\childentrylinked{1826}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Johann Henrick "Hans" Lautenschlager}}}}}
\dividerline

\entry{3653}{Anna Hoff}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Georg Hoff}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catharina Kistler}}}}, was born about 1655 in Erbach, Hessen, Germany and died on 23 Dec 1710 in Laudenau, Starkenburg, Hesse, Germany, about age 55.}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Johann Peter Lautenschlaeger}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Adam Lautenschlaeger}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Ihrig}}}}.}
\dividerline

\entry{3680}{Hans Caspar Bitzer}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johannes Cunlius Bitzer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Huegin}}}}, was born about 1608 in Tailfingen, Boblingen, Baden-Wuerttemberg, Germany and died in 1694 in Tailfingen, Boblingen, Baden-Wuerttemberg, Germany, about age 86. Kaiserslautern, Rheinland-Pfalz, Germany.}
\marriage{Hans married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Hauser}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Michel Hauser}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Agnes}}}}, on 14 Jul 1632 in Vogelbach,}
\childrenheading
\childentrylinked{1840}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jacob Bitzer}}}}}
\dividerline

\entry{3681}{Anna Hauser}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Michel Hauser}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Agnes}}}}, was born about 1610 in Tailfingen, Boblingen, Baden- Wuerttemberg, Germany and died on 3 Dec 1676 in Tailfingen, Boblingen, Baden-Wuerttemberg, Germany, about age 66. Vogelbach, Kaiserslautern, Rheinland-Pfalz, Germany.}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Hans Caspar Bitzer}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johannes Cunlius Bitzer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Huegin}}}}, on 14 Jul 1632 in}
\dividerline

\entry{3682}{Hans Georg Conzelmann was born about 1616 in Baden}{Baden-Wuerttemberg, Germany and died on 13 Mar 1692 in Baden, Baden-Wuerttemberg, Germany, about age 76.}
\marriage{Hans married \href{#}{\textcolor{accent}{\textbf{\underline{Dorothea Fessler.}}}}}
\childrenheading
\childentrylinked{1841}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Catherina Conzelmann}}}}}
\dividerline

\entry{3683}{Dorothea Fessler died on 22 Aug 1679 in Tailfingen}{Boblingen, Baden-Wuerttemberg, Germany.}
\marriage{Dorothea married \href{#}{\textcolor{accent}{\textbf{\underline{Hans Georg Conzelmann.}}}}}
\dividerline

\entry{3696}{Hans Albert Boshaar}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Jacob Boshaar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Agnes Margaretha Pasour}}}}, was born on 1 Dec 1621 in Zweibrucken, Zweibruckem, Rheinland-Pfalz, Germany and died on 20 Jan 1680 in Zweibrucken, Zweibruckem, Rheinland-Pfalz, Germany, at age 58.}
\marriage{Hans married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Maria Margaretha Delagrevis.}}}}}
\childrenheading
\childentrylinked{1848}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Johan Jacob Boshaar}}}}}
\dividerline

\entry{3697}{Anna Maria Margaretha Delagrevis was born about 1620 in Breitenbach}{Zweibrucken, Rheinland-Pfalz, Germany and died in 1684 in Nassau, Degendorf, Bayern, Germany, about age 64.}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Hans Albert Boshaar}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Johann Jacob Boshaar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Agnes Margaretha Pasour}}}}.}
\dividerline

\entry{3698}{Hans Conrad Maurer}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Christian Maurer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Margaretha Arnoldt}}}}, was born on 2 Jan 1642 in Neckarhausen, Bergenstrasse, Hessen, Germany and died on 29 Feb 1720 in Grotzingen, Karlsruhe, Baden- Wuerttemberg, Germany, at age 78.}
\marriage{Hans married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Knoell.}}}}}
\childrenheading
\childentrylinked{1849}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Anna Christina Maurer}}}}}
\dividerline

\entry{3699}{Anna Knoell was born on 20 Sep 1635 in Wolfschlugen}{Esslingen, Baden-Wuerttemberg, Germany and died in 1720 in Grotzingen, Karlsruhe, Baden-Wuerttemberg, Germany, at age 85.}
\marriage{Anna married \href{#}{\textcolor{accent}{\textbf{\underline{Hans Conrad Maurer}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Christian Maurer}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Maria Margaretha Arnoldt}}}}.}
\dividerline

\entry{3700}{Thomas Wennerich}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Isaach Wennerich}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Rebecca Scharff}}}}, was born in Edigheim, Ludwigschafen- am-Rhein, Rheinland-Pfalz, Germany and died in 1678 in Mannheim, Baden-Wuerttemberg, Germany. Margaretha Stoehr.}
\marriage{Thomas married \href{#}{\textcolor{accent}{\textbf{\underline{Maria Magdalena Elizabetha Krafft}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Hans Conrad Krafft}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna}}}}}
\childrenrenheading
\childentrylinked{1850}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Balthazar Wennerich}}}}}
\childentryplain{3701. Maria Magdalena Elizabetha Krafft}{ii}{, daughter of Hans Conrad Krafft and Anna Margaretha Stoehr, was}
\childentryplain{born about 1642 in Edigheim}{iii}{, Ludwigschafen-am-Rhein, Rheinland-Pfalz, Germany.}
\childentryplain{Maria married Thomas Wennerich}{iv}{, son of Isaach Wennerich and Rebecca Scharff.}
\dividerline

\entry{3768}{James Parkin}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Parkin}}}}, was born about 1659 in Wickenslack, Westmoreland, England and died in 1700 in Wickenslack, Westmoreland, England, about age 41.}
\marriage{James married \href{#}{\textcolor{accent}{\textbf{\underline{Mary Moore.}}}}}
\childrenheading
\childentrylinked{1884}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Anthony Parkin}}}}}
\dividerline

\entry{3769}{Mary Moore .}{}
\marriage{Mary married \href{#}{\textcolor{accent}{\textbf{\underline{James Parkin}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Parkin}}}}.}
\dividerline

\entry{3774}{Richard Thornborrow}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Edmund Thornborrow}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Agnes Perkin}}}}, was born about 1664 in Dufton, Westmoreland, England and died on 6 Sep 1729 in Dufton, Westmoreland, England, about age 65.}
\marriage{Richard married \href{#}{\textcolor{accent}{\textbf{\underline{Jennet Bellas}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Bellas}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Green}}}}.}
\childrenheading
\childentrylinked{1887}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Catherine Thornborrow}}}}}
\dividerline

\entry{3775}{Jennet Bellas}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{William Bellas}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Green}}}}, was born about 1674 in Long Marton, Westmoreland, England and died on 22 Sep 1731 in Dufton, Westmoreland, England, about age 57.}
\marriage{Jennet married \href{#}{\textcolor{accent}{\textbf{\underline{Richard Thornborrow}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Edmund Thornborrow}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Agnes Perkin}}}}.}
\dividerline

\entry{3904}{Hans Georg Hellenschmitt .}{His child was: 1952 i. Johann Georg Leonhard Hellenschmitt}
\marriage{Hans married \href{#}{\textcolor{accent}{\textbf{\underline{someone.}}}}}
\dividerline

\entry{3906}{Hans Caspar Botsch}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Andres Botsch}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Barbara Meder}}}}, was born on 8 Apr 1664 in Hachtel, Main- Tauber-Kreis, Baden-Wuerttemberg, Germany and died on 19 Oct 1732 in Untereichenrot, Schwabisch Hall, Baden- Wuerttemberg, Germany, at age 68.}
\marriage{Hans married \href{#}{\textcolor{accent}{\textbf{\underline{Eva Wirth}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Georg Wirth}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Magdalena Vogt}}}}.}
\childrenheading
\childentrylinked{1953}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Sophia Botsch}}}}}
\dividerline

\entry{3907}{Eva Wirth}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Georg Wirth}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Magdalena Vogt}}}}, was born on 5 Jan 1661 and died on 18 Dec 1731 in Untereichenrot, Schwabisch Hall, Baden-Wuerttemberg, Germany, at age 70. 13th Generation}
\marriage{Eva married \href{#}{\textcolor{accent}{\textbf{\underline{Hans Caspar Botsch}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Andres Botsch}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Barbara Meder}}}}.}
\dividerline

\entry{4224}{John Leane}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Leane}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Christiane Scoble}}}}, was born about 1633 in Gwennap, Cornwall, England and died on 23 Apr 1691 in Gwennap, Cornwall, England, about age 58. Cornwall, England.}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Constance Treloar}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Treloar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Frances Cliff}}}}, on 27 Oct 1662 in Gwennap,}
\childrenheading
\childentrylinked{2112}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{William Lean}}}}}
\dividerline

\entry{4225}{Constance Treloar}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Treloar}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Frances Cliff}}}}, died on 28 Sep 1671 in Gwennap, Cornwall, England. Cornwall, England.}
\marriage{Constance married \href{#}{\textcolor{accent}{\textbf{\underline{John Leane}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Leane}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Christiane Scoble}}}}, on 27 Oct 1662 in Gwennap,}
\dividerline

\entry{4228}{Samuel Polkinghorne}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Stephen Polkinghorne}}}}, was born in Aug 1625 in Breage, Cornwall, England and died in Feb 1698 in Breage, Cornwall, England, at age 72.}
\marriage{Samuel married \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Carter.}}}}}
\childrenheading
\childentrylinked{2114}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Stephen Polkinghorn}}}}}
\dividerline

\entry{4229}{Margaret Carter .}{}
\marriage{Margaret married \href{#}{\textcolor{accent}{\textbf{\underline{Samuel Polkinghorne}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Stephen Polkinghorne}}}}.}
\dividerline

\entry{4256}{Richard Trewren}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Trewren}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jane Wise}}}}, was born on 15 Nov 1609 in Sancreed, Cornwall, England and died on 21 Mar 1682 in Sancreed, Cornwall, England, at age 72.}
\marriage{Richard married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Harris.}}}}}
\childrenheading
\childentrylinked{2128}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Thomas Trewren}}}}}
\dividerline

\entry{4257}{Elizabeth Harris .}{}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{Richard Trewren}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Trewren}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jane Wise}}}}.}
\dividerline

\entry{4258}{Peter Ceely}{son of \href{#}{\textcolor{accent}{\textbf{\underline{William Ceely}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Penrose}}}}, was born about 1618 in Cornwall, England and died on 10 Nov 1666 in Cornwall, England, about age 48.}
\marriage{Peter married \href{#}{\textcolor{accent}{\textbf{\underline{Honour Praed.}}}}}
\childrenheading
\childentrylinked{2129}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Catherine Seyley}}}}}
\dividerline

\entry{4259}{Honour Praed died in 1680 in Cornwall}{England.}
\marriage{Honour married \href{#}{\textcolor{accent}{\textbf{\underline{Peter Ceely}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{William Ceely}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Penrose}}}}.}
\dividerline

\entry{4260}{Robert Couch}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Couch}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Emma Lambe}}}}, was born about 1635 in St. German's, Cornwall, England and died in Jul 1689 in Roche, Cornwall, England, about age 54.}
\marriage{Robert married \href{#}{\textcolor{accent}{\textbf{\underline{Dorothy Hurrell.}}}}}
\childrenheading
\childentrylinked{2130}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{John Couch}}}}}
\dividerline

\entry{4261}{Dorothy Hurrell was born about 1617 in Tywardreath}{Cornwall, England and died on 14 Mar 1690 in Golant, Cornwall, England, about age 73.}
\marriage{Dorothy married \href{#}{\textcolor{accent}{\textbf{\underline{Robert Couch}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Couch}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Emma Lambe}}}}.}
\dividerline

\entry{4262}{John Frethy was born about 1615 in Cornwall}{England and died in St. Veep, Cornwall, England.}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Stephen.}}}}}
\childrenheading
\childentrylinked{2131}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Mary Frethy}}}}}
\dividerline

\entry{4263}{Elizabeth Stephen was born in Apr 1621 in Menheniot}{Cornwall, England and died about 1693 in Cornwall, England, about age 72.}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{John Frethy.}}}}}
\dividerline

\entry{4264}{George Blight was born about 1634 in Cornwall}{England.}
\marriage{George married \href{#}{\textcolor{accent}{\textbf{\underline{Joane Sampson}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Sampson}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joane Marke}}}}.}
\childrenheading
\childentrylinked{2132}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{George Blight}}}}}
\dividerline

\entry{4265}{Joane Sampson}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Sampson}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joane Marke}}}}.}
\marriage{Joane married \href{#}{\textcolor{accent}{\textbf{\underline{George Blight.}}}}}
\dividerline

\entry{4266}{Ephraim James}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Nicholas James}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Mary Saunders}}}}, was born about 1620 in Ludgvan, Cornwall, England and died on 9 Oct 1710 in Ludgvan, Cornwall, England, about age 90. England.}
\marriage{Ephraim married \href{#}{\textcolor{accent}{\textbf{\underline{Jane Christover}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Michael Christover}}}}, on 1 Oct 1656 in Ludgvan, Cornwall,}
\childrenrenheading
\childentrylinked{2133}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Philippa James}}}}}
\childentryplain{4267. Jane Christover}{ii}{, daughter of Michael Christover, was born on 18 Nov 1621 in Ludgvan, Cornwall, England}
\childentryplain{and died on 4 Nov 1703 in Ludgvan}{iii}{, Cornwall, England, at age 81.}
\childentryplain{Jane married Ephraim James}{iv}{, son of Nicholas James and Mary Saunders, on 1 Oct 1656 in Ludgvan,}
\childentryplain{Cornwall}{v}{, England.}
\dividerline

\entry{4270}{Robert Christopher}{son of \href{#}{\textcolor{accent}{\textbf{\underline{James Christopher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elinor Penrose}}}}, was born on 5 Aug 1610 in Cornwall, England.}
\marriage{Robert married \href{#}{\textcolor{accent}{\textbf{\underline{Joie.}}}}}
\childrenheading
\childentrylinked{2135}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Margery Christopher}}}}}
\dividerline

\entry{4271}{Joie .}{}
\marriage{Joie married \href{#}{\textcolor{accent}{\textbf{\underline{Robert Christopher}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{James Christopher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elinor Penrose}}}}.}
\dividerline

\entry{4272}{Thomas Hall was born about 1637 in Madron}{Cornwall, England and died in Apr 1695 in Madron, Cornwall, England, about age 58.}
\marriage{Thomas married \href{#}{\textcolor{accent}{\textbf{\underline{Marion Carnepessack}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Michael Carnepessack}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Cheston}}}}.}
\childrenheading
\childentrylinked{2136}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Richard Hall}}}}}
\dividerline

\entry{4273}{Marion Carnepessack}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Michael Carnepessack}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Cheston}}}}, was born in Jan 1642 in Madron, Cornwall, England and died on 2 Jun 1723 in Penwith, Cornwall, England, at age 81.}
\marriage{Marion married \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Hall.}}}}}
\dividerline

\entry{4274}{Richard Nicholls}{son of \href{#}{\textcolor{accent}{\textbf{\underline{John Nicholls}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Donithorne}}}}, was born on 24 Jan 1640 in Gulval, Cornwall, England and died on 5 Nov 1698 in Gulval, Cornwall, England, at age 58.}
\marriage{Richard married \href{#}{\textcolor{accent}{\textbf{\underline{Amy Morish}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Morish}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Nicholls}}}}.}
\childrenheading
\childentrylinked{2137}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Mary Nicholls}}}}}
\dividerline

\entry{4275}{Amy Morish}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Morish}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Nicholls}}}}, died on 14 Mar 1703 in Gulval, Cornwall, England.}
\marriage{Amy married \href{#}{\textcolor{accent}{\textbf{\underline{Richard Nicholls}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{John Nicholls}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Donithorne}}}}.}
\dividerline

\entry{4276}{John Gomer .}{His child was: 2138 i. John Gomer 4278. Richard Sampson, son of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Sampson}}}}, was born in Mar 1630 in Cornwall, England and died on 3 Jul 1680 in Paul, Cornwall, England, at age 50.}
\marriage{Richard married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth.}}}}}
\childrenheading
\childentrylinked{2139}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Sampson}}}}}
\dividerline

\entry{4279}{Elizabeth died on 7 Jan 1705 in Paul}{Cornwall, England.}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{Richard Sampson}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Sampson}}}}.}
\dividerline

\entry{4280}{John Tresise}{son of \href{#}{\textcolor{accent}{\textbf{\underline{John Tresise}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Grace Tonkin}}}}, was born in Jan 1635 in Penwith, Cornwall, England and died on 30 Oct 1695 in Penwith, Cornwall, England, at age 60.}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Joan Paine.}}}}}
\childrenheading
\childentrylinked{2140}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{John Tresise}}}}}
\dividerline

\entry{4281}{Joan Paine died in Aug 1695 in Penzance}{Cornwall, England.}
\marriage{Joan married \href{#}{\textcolor{accent}{\textbf{\underline{John Tresise}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{John Tresise}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Grace Tonkin}}}}.}
\dividerline

\entry{4282}{George Wallish}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Wallish}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Ellis}}}}, was born on 11 Oct 1635 in Penwith, Cornwall, England and died in Jun 1677 in Penwith, Cornwall, England, at age 41. Cornwall, England.}
\marriage{George married \href{#}{\textcolor{accent}{\textbf{\underline{Mary Shepard}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Shepard}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joan Moate}}}}, on 1 Nov 1649 in St. German's,}
\childrenheading
\childentrylinked{2141}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Mary Wallish}}}}}
\dividerline

\entry{4283}{Mary Shepard}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{John Shepard}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Joan Moate}}}}, was born in Penwith, Cornwall, England and died on 23 Sep 1690. Cornwall, England.}
\marriage{Mary married \href{#}{\textcolor{accent}{\textbf{\underline{George Wallish}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Wallish}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Ellis}}}}, on 1 Nov 1649 in St. German's,}
\dividerline

\entry{4284}{John Trenbath}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Trenbath}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Argentine Michell}}}}, was born about 1640 in Sancreed, Cornwall, England and died in Sep 1721 in Penwith, Cornwall, England, about age 81.}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Mary James.}}}}}
\childrenheading
\childentrylinked{2142}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Emanuel Trenbath}}}}}
\dividerline

\entry{4285}{Mary James was born on 5 Sep 1641 in Constantine}{Cornwall, England and died on 16 Nov 1687 in Penwith, Cornwall, England, at age 46.}
\marriage{Mary married \href{#}{\textcolor{accent}{\textbf{\underline{John Trenbath}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Richard Trenbath}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Argentine Michell}}}}.}
\dividerline

\entry{4286}{William Warrin}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Bartholomew Warrin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Honor James}}}}, was born on 1 Nov 1639 in Penwith, Cornwall, England and died about 1726 in Penwith, Cornwall, England, about age 87.}
\marriage{William married \href{#}{\textcolor{accent}{\textbf{\underline{Ann White}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{James White}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marjory}}}}.}
\childrenheading
\childentrylinked{2143}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Margaret Warrin}}}}}
\dividerline

\entry{4287}{Ann White}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{James White}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marjory}}}}, was born in Penwith, Cornwall, England.}
\marriage{Ann married \href{#}{\textcolor{accent}{\textbf{\underline{William Warrin}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Bartholomew Warrin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Honor James}}}}.}
\dividerline

\entry{4320}{William Perry .}{His child was: 2160 i. William Perry}
\marriage{William married \href{#}{\textcolor{accent}{\textbf{\underline{someone.}}}}}
\dividerline

\entry{4322}{John Symons .}{His child was: 2161 i. Mary Symons}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{someone.}}}}}
\dividerline

\entry{4324}{John Jenkin}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Jenkin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Perkins}}}}, was born on 10 Oct 1619 in Wendron, Cornwall, England and died about 1690 in Wendron, Cornwall, England, about age 71. Wendron, Cornwall, England.}
\marriage{John married \href{#}{\textcolor{accent}{\textbf{\underline{Anne Dunstone}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francis Dunstone}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Cheriers}}}}, on 19 Apr 1642 in}
\childrenheading
\childentrylinked{2162}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Matthew Jenkin}}}}}
\dividerline

\entry{4325}{Anne Dunstone}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Francis Dunstone}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Cheriers}}}}. Cornwall, England.}
\marriage{Anne married \href{#}{\textcolor{accent}{\textbf{\underline{John Jenkin}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Thomas Jenkin}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaret Perkins}}}}, on 19 Apr 1642 in Wendron,}
\dividerline

\entry{4326}{James Clise}{son of \href{#}{\textcolor{accent}{\textbf{\underline{James Clise}}}}, was born about 1600 in Breage, Cornwall, England and died in 1660 in Breage, Cornwall, England, about age 60. Cornwall, England.}
\marriage{James married \href{#}{\textcolor{accent}{\textbf{\underline{Grace Moore}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Moore}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Elinor Thomas}}}}, on 25 Nov 1626 in Breage,}
\childrenrenheading
\childentrylinked{2163}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Alice Clise}}}}}
\childentryplain{4327. Grace Moore}{ii}{, daughter of Robert Moore and Elinor Thomas, died in 1674 in Breage, Cornwall, England.}
\childentryplain{Grace married James Clise}{iii}{, son of James Clise, on 25 Nov 1626 in Breage, Cornwall, England.}
\dividerline

\entry{4338}{Hugh Pruste was born in Cornwall}{England.}
\marriage{Hugh married \href{#}{\textcolor{accent}{\textbf{\underline{Elizabeth Wadland.}}}}}
\childrenheading
\childentrylinked{2169}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Katherine Pruste}}}}}
\dividerline

\entry{4339}{Elizabeth Wadland died in 1690.}{}
\marriage{Elizabeth married \href{#}{\textcolor{accent}{\textbf{\underline{Hugh Pruste.}}}}}
\dividerline

\entry{6426}{Jacques Blois was born about 1600 in Maine}{Charente, Poitou-Charentes, France and died in 1659 in Ferte, Lemans, Maine, France, about age 59.}
\marriage{Jacques married \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Masson.}}}}}
\childrenheading
\childentrylinked{3213}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Blois}}}}}
\dividerline

\entry{6427}{Francoise Masson died in 1644 in Mamers}{Sarthe, Pays-de-la-Loire, France.}
\marriage{Francoise married \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Blois.}}}}}
\dividerline

\entry{6432}{Martin Favreau}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Favreau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Barbe Meunier}}}}, was born on 1 Jan 1608 in Saint Malo, Ille-et-Vilaine, Bretagne, France and died on 5 Jun 1659 in Dole, Jura, Franche-Comte, France, at age 51.}
\marriage{Martin married \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Lecour.}}}}}
\childrenheading
\childentrylinked{3216}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Pierre Favreau}}}}}
\dividerline

\entry{6433}{Marguerite Lecour was born about 1610 in Jura}{Franche-Comte, France and died on 1 Apr 1666 in Farges- les-chalon, Saone-et-Loire, Bourgogne, France, about age 56.}
\marriage{Marguerite married \href{#}{\textcolor{accent}{\textbf{\underline{Martin Favreau}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Favreau}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Barbe Meunier}}}}.}
\dividerline

\entry{6434}{Francois Benoit was born in Dole}{Jura, Franche-Comte, France.}
\marriage{Francois married \href{#}{\textcolor{accent}{\textbf{\underline{Christine.}}}}}
\childrenheading
\childentrylinked{3217}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Benoit}}}}}
\dividerline

\entry{6435}{Christine .}{}
\marriage{Christine married \href{#}{\textcolor{accent}{\textbf{\underline{Francois Benoit.}}}}}
\dividerline

\entry{6436}{Noel Meunier}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Rene Meunier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Fleuriat}}}}, was born on 7 Oct 1622 in Plancoet, Cotes'd'Armor, Bretagne, France and died on 12 Oct 1675 in Rennes, Ille-et-Vilaine, Bretagne, France, at age 53.}
\marriage{Noel married \href{#}{\textcolor{accent}{\textbf{\underline{Antoinette Guibourg}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Rene Mathurin Guibourg}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Julienne Jouaud}}}}.}
\childrenheading
\childentrylinked{3218}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Pierre Meunier}}}}}
\dividerline

\entry{6437}{Antoinette Guibourg}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Rene Mathurin Guibourg}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Julienne Jouaud}}}}, was born on 12 Jun 1627 in Saint-Aubin-du-Pavail, Ille-et-Vilaine, Bretagne, France and died in 1675 in Rennes, Ille-et-Vilaine, Bretagne, France, at age 48.}
\marriage{Antoinette married \href{#}{\textcolor{accent}{\textbf{\underline{Noel Meunier}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Rene Meunier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Fleuriat}}}}.}
\dividerline

\entry{6438}{Pierre Richaume}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Simon Richaume}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Belier}}}}, was born about 1635 in Saintonge, Charente-Maritime, Poitou-Charentes, France and died in Quebec, Canada.}
\marriage{Pierre married \href{#}{\textcolor{accent}{\textbf{\underline{Marthe Marie Arnus on 16 Sep 1658 in Repentigny}}}}, Assomption, Quebec, Canada.}
\childrenrenheading
\childentrylinked{3219}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Barbe Richaume}}}}}
\childentrylinked{--}{ii}{\href{#}{\textcolor{accent}{\textbf{\underline{Elisabeth Richaume was born on 31 Aug 1666 in Montreal, Quebec, Canada}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 4 Apr 1703}}}}}
\childentryplain{in Montreal}{iii}{, Quebec, Canada, at age 36.}
\childentrylinked{--}{iv}{\href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Richaume was born on 3 Dec 1668 in Repentigny, Assomption, Quebec, Canada}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on}}}}}
\childentryplain{6 Dec 1701 in Montreal}{v}{, Quebec, Canada, at age 33.}
\dividerline

\entry{6439}{Marthe Marie Arnus was born on 28 Mar 1632 in La Rochelle}{Aunis, Charente Maritime, France and died on 26 Aug 1700 in Montreal, Quebec, Canada, at age 68. Repentigny, Assomption, Quebec, Canada.}
\marriage{Marthe married \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Richaume}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Simon Richaume}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Belier}}}}, on 16 Sep 1658 in}
\dividerline

\entry{6444}{Pierre Deniau was born on 10 Apr 1602 in Nantes}{Haute, Bretagne, France and died on 19 Aug 1695 in Montreal, Quebec, Canada, at age 93.}
\marriage{Pierre married \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Gaudet.}}}}}
\childrenheading
\childentrylinked{3222}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jean Deniau}}}}}
\dividerline

\entry{6445}{Jeanne Gaudet .}{}
\marriage{Jeanne married \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Deniau.}}}}}
\dividerline

\entry{6460}{Claude Chaudillon was born about 1620 in Moulin}{Oise, Picardie, France and died on 26 May 1672 in Ygrande, Bourbonnais, France, about age 52.}
\marriage{Claude married \href{#}{\textcolor{accent}{\textbf{\underline{Antoinette Tin.}}}}}
\childrenheading
\childentrylinked{3230}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Antoine Chaudillon}}}}}
\dividerline

\entry{6461}{Antoinette Tin .}{}
\marriage{Antoinette married \href{#}{\textcolor{accent}{\textbf{\underline{Claude Chaudillon.}}}}}
\dividerline

\entry{6464}{Thierry Proteau .}{}
\marriage{Thierry married \href{#}{\textcolor{accent}{\textbf{\underline{Madeleine Parisot.}}}}}
\childrenheading
\childentrylinked{3232}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Proteau}}}}}
\dividerline

\entry{6465}{Madeleine Parisot .}{}
\marriage{Madeleine married \href{#}{\textcolor{accent}{\textbf{\underline{Thierry Proteau.}}}}}
\dividerline

\entry{6466}{Jean Sautret .}{}
\marriage{Jean married \href{#}{\textcolor{accent}{\textbf{\underline{Perette Fournier.}}}}}
\childrenheading
\childentrylinked{3233}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Francoise Sautret}}}}}
\dividerline

\entry{6467}{Perette Fournier .}{}
\marriage{Perette married \href{#}{\textcolor{accent}{\textbf{\underline{Jean Sautret.}}}}}
\dividerline

\entry{6498}{Nicolas Gobinet was born about 1610 in Gonset}{Vexin, Ile-de-France, France and died on 16 Sep 1658 in Gonesse, Val-d'Oise, Ile-de-France, France, about age 48.}
\marriage{Nicolas married \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Lorgeleux.}}}}}
\childrenheading
\childentrylinked{3249}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elisabeth Isabelle Gobinet}}}}}
\dividerline

\entry{6499}{Marguerite Lorgeleux .}{}
\marriage{Marguerite married \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Gobinet.}}}}}
\dividerline

\entry{6504}{Francois Charles was born about 1617 in Creteil}{Paris, Ile-de-France, France and died in 1667 in Chambly, Quebec, Canada, about age 50.}
\marriage{Francois married \href{#}{\textcolor{accent}{\textbf{\underline{Colombe Regnault on 8 Nov 1637 in Creteil}}}}, Paris, Ile-de-France, France.}
\childrenheading
\childentrylinked{3252}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Etienne Charles}}}}}
\dividerline

\entry{6505}{Colombe Regnault died in 1667 in Villejuif}{Val-de-Marne, Ile-de-France, France.}
\marriage{Colombe married \href{#}{\textcolor{accent}{\textbf{\underline{Francois Charles on 8 Nov 1637 in Creteil}}}}, Paris, Ile-de-France, France.}
\dividerline

\entry{6510}{Jean Valiquet was born on 14 Jul 1632 in Anjou}{Isere, Rhone-Alpes, France and died on 20 Aug 1696 in Quebec, Canada, at age 64.}
\marriage{Jean married \href{#}{\textcolor{accent}{\textbf{\underline{Renee Loppe on 23 Sep 1658 in Montreal}}}}, Quebec, Canada.}
\childrenheading
\childentrylinked{3255}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elisabeth Valiquet}}}}}
\dividerline

\entry{6511}{Renee Loppe was born on 23 Sep 1643 in St Jean de la Mothe}{Nans, Maine, France and died before 20 Mar 1679 in Montreal, Quebec, Canada.}
\marriage{Renee married \href{#}{\textcolor{accent}{\textbf{\underline{Jean Valiquet on 23 Sep 1658 in Montreal}}}}, Quebec, Canada.}
\dividerline

\entry{6512}{Rene de Lavoie was born on 6 Mar 1601 in St Maclou}{Rouen, Normandie, France.}
\marriage{Rene married \href{#}{\textcolor{accent}{\textbf{\underline{Isabelle Belanger.}}}}}
\childrenheading
\childentrylinked{3256}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Rene de Lavoie}}}}}
\dividerline

\entry{6513}{Isabelle Belanger .}{}
\marriage{Isabelle married \href{#}{\textcolor{accent}{\textbf{\underline{Rene de Lavoie.}}}}}
\dividerline

\entry{6514}{Elie Gaudin was born about 1617 in France and died on 5 Jan 1672 in Ste Anne de Beaupre}{Quebec, Canada, about age 55.}
\marriage{Elie married \href{#}{\textcolor{accent}{\textbf{\underline{Esther Marie Ramage.}}}}}
\childrenheading
\childentrylinked{3257}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Anne Godin}}}}}
\dividerline

\entry{6515}{Esther Marie Ramage .}{}
\marriage{Esther married \href{#}{\textcolor{accent}{\textbf{\underline{Elie Gaudin.}}}}}
\dividerline

\entry{6516}{Marin Boucher}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Boucher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Francoise Paigne}}}}, was born on 15 Apr 1589 in St Langis les Mortagne, Perche, France and died on 25 Mar 1671 in Chateau-Richer, La Cote-de-Beaupre, Quebec, Canada, at age 81.}
\marriage{Marin married \href{#}{\textcolor{accent}{\textbf{\underline{Julienne Baril on 7 Feb 1611 in Mortagne-au-Perche}}}}, Orne, Basse-Normandie, France.}
\childrenrenheading
\childentrylinked{3258}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jean-Galeran Boucher}}}}}
\childentryplain{Marin next married Perrine Mallet}{ii}{, daughter of Pierre Mallet and Jacquette Francoise Leger.}
\childentrylinked{--}{iii}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Francoise Boucher was born on 22 Jun 1636 in Courgeon, Orne, Basse-Normandie, France}}}}}
\childentryplain{and died on 18 Apr 1711 in Ste Familie}{iv}{, Ille d'Orleans, Quebec, Canada, at age 74.}
\childentry{}{6517. Julienne Baril .}
\childentryplain{Julienne married Marin Boucher}{vi}{, son of Jacques Boucher and Marie Francoise Paigne, on 7 Feb 1611 in}
\childentryplain{Mortagne-au-Perche}{vii}{, Orne, Basse-Normandie, France.}
\dividerline

\entry{6518}{Jonas Leclerc died in 1661 in Dieppe}{Seine-Maritime, Haute-Normandie, France.}
\marriage{Jonas married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Parmentier.}}}}}
\childrenheading
\childentrylinked{3259}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Helene Leclerc}}}}}
\dividerline

\entry{6519}{Marie Parmentier .}{}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Jonas Leclerc.}}}}}
\dividerline

\entry{6592}{Claude Morin was born about 1591 in St-Etienne-de-Brie-Comte-Robert}{Brie, France and died in 1640 in France, about age 49.}
\marriage{Claude married \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Moreau.}}}}}
\childrenheading
\childentrylinked{3296}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Noel Morin}}}}}
\dividerline

\entry{6593}{Jeanne Moreau died in Dec 1639 in Melum}{Brie, France.}
\marriage{Jeanne married \href{#}{\textcolor{accent}{\textbf{\underline{Claude Morin.}}}}}
\dividerline

\entry{6594}{Pierre Desportes}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Louis Desportes}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Ann Dupoteau}}}}, was born about 1584 in Lisieux, Calvados, Basse-Normandie, France and died on 18 May 1629 in Quebec City, Quebec, Canada, about age 45.}
\marriage{Pierre married \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Langlois}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Guillaume Langlois}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Millette}}}}.}
\childrenheading
\childentrylinked{3297}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Helene Desportes}}}}}
\dividerline

\entry{6595}{Francoise Langlois}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Guillaume Langlois}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Millette}}}}, was born about 1599 in Lisieux, Calvados, Basse-Normandie, France and died on 18 May 1629 in Lisieux, Calvados, Basse-Normandie, France, about age 30.}
\marriage{Francoise married \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Desportes}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Louis Desportes}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Ann Dupoteau}}}}.}
\dividerline

\entry{6596}{Michel Mignier was born about 1610 in La Rochelle}{Manche, Basse-Normandie, France and died on 20 May 1678 in France, about age 68.}
\marriage{Michel married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Masson.}}}}}
\childrenrenheading
\childentrylinked{3298}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Andre Mignier}}}}}
\childentryplain{6597. Catherine Masson was born about 1615 in La Rochelle}{ii}{, Manche, Basse-Normandie, France and died on 10}
\childentryplain{May 1669 in La Rochelle}{iii}{, Manche, Basse-Normandie, France, about age 54.}
\childentry{}{Catherine married Michel Mignier.}
\dividerline

\entry{6598}{Jacques Michel was born about 1610 in La Rochelle}{Manche, Basse-Normandie, France and died on 23 Oct 1668 in St. Martin, Puy-de-Dome, Auvergne, France, about age 58.}
\marriage{Jacques married \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Dupont.}}}}}
\childrenheading
\childentrylinked{3299}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jacquette Michel}}}}}
\dividerline

\entry{6599}{Jeanne Dupont was born on 19 Feb 1610 in La Rochelle}{Manche, Basse-Normandie, France.}
\marriage{Jeanne married \href{#}{\textcolor{accent}{\textbf{\underline{Jacques Michel.}}}}}
\dividerline

\entry{6602}{Pierre Campion was born on 6 May 1625 in Rouen}{Seine-Maritime, Haute-Normandie, France and died on 30 Dec 1695 in Rouen, Seine-Maritime, Haute-Normandie, France, at age 70.}
\marriage{Pierre married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Marguerite Henault.}}}}}
\childrenheading
\childentrylinked{3301}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Catherine Marie Campion}}}}}
\dividerline

\entry{6603}{Marie Marguerite Henault was born in Apr 1630 in Rouen}{Seine-Maritime, Haute-Normandie, France and died on 30 Jun 1704 in Rouen, Seine-Maritime, Haute-Normandie, France, at age 74.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Campion.}}}}}
\dividerline

\entry{6604}{Pierre Miville}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Isaac Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Salome Lomene}}}}, was born in 1605 in Fribourg, La Sarine, Fribourg, Switzerland and died on 14 Oct 1669 in Levis, Chaudiere-Appalaches, Quebec, Canada, at age 64.}
\marriage{Pierre married \href{#}{\textcolor{accent}{\textbf{\underline{Charlotte Maugis}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Alphonse Maugis}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Louise de Merle}}}}.}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Miville was born on 13 Dec 1632 in Hiers-Brouage, Charente-Maritime, Poitou-Charentes,}}}}}
\childentryplain{France and died on 5 Sep 1702 in Quebec City}{ii}{, Quebec, Canada, at age 69.}
\childentry{}{3302 ii. Francois Miville}
\childentrylinked{--}{iv}{\href{#}{\textcolor{accent}{\textbf{\underline{Madeleine Miville was born on 18 Nov 1636 in Brouage, Charente, Poitou-Charentes, France and}}}}}
\childentryplain{died on 16 Sep 1708 in Chateau-Richer}{v}{, La Cote-de-Beaupre, Quebec, Canada, at age 71.}
\childentry{}{3304 iv. Jacques Miville}
\dividerline

\entry{6605}{Charlotte Maugis}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Alphonse Maugis}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Louise de Merle}}}}, died on 11 Oct 1676 in Quebec, Canada.}
\marriage{Charlotte married \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Miville}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Isaac Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Salome Lomene}}}}.}
\dividerline

\entry{6606}{Noel Langlois}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Guillaume Langlois}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Millet}}}}, was born about 1605 in Alencon, Orne, Basse- Normandie, France and died on 14 Jul 1684 in Beauport, Quebec, Canada, about age 79.}
\marriage{Noel married \href{#}{\textcolor{accent}{\textbf{\underline{Francoise Grenier.}}}}}
\childrenrenheading
\childentrylinked{--}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Elisabeth Langlois was born on 21 Feb 1645 in Quebec City, Quebec, Canada}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{died on 18 Nov}}}}}
\childentryplain{1696 in Cap-St-Ignace}{ii}{, Quebec, Canada, at age 51.}
\childentry{}{3303 ii. Marie Langlois}
\dividerline

\entry{6607}{Francoise Grenier died on 1 Nov 1665 in Montmorency}{Ile d'Orleans, Quebec, Canada.}
\marriage{Francoise married \href{#}{\textcolor{accent}{\textbf{\underline{Noel Langlois}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Guillaume Langlois}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Millet}}}}.}
\dividerline

\entry{6608}{Pierre Miville}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Isaac Miville}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Salome Lomene}}}}, was born in 1605 in Fribourg, La Sarine, Fribourg, Switzerland and died on 14 Oct 1669 in Levis, Chaudiere-Appalaches, Quebec, Canada, at age 64. (Duplicate. See Person 6604 on Page 1)}
\dividerline

\entry{6609}{Charlotte Maugis}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Alphonse Maugis}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Louise de Merle}}}}, died on 11 Oct 1676 in Quebec, Canada. (Duplicate. See Person 6605 on Page 1)}
\dividerline

\entry{6610}{Alphonse Baillon}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Adam de Baillon - Seigneur of Valence}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Renee de Maillard}}}}, was born about 1605 in Montfort, Chartres, Ille-et-Vilaine, Bretagne, France and died on 25 Oct 1673 in Yvelines, Ile-de-France, France, about age 68.}
\marriage{Alphonse married \href{#}{\textcolor{accent}{\textbf{\underline{Louise de Marle}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Mathurin de Marle}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Bizet}}}}.}
\childrenheading
\childentrylinked{3305}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Catherine Baillon}}}}}
\dividerline

\entry{6611}{Louise de Marle}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Mathurin de Marle}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Bizet}}}}, was born on 14 Nov 1618 in Yvelines, Ile- de-France, France and died on 25 Oct 1673 in Yvelines, Ile-de-France, France, at age 54.}
\marriage{Louise married \href{#}{\textcolor{accent}{\textbf{\underline{Alphonse Baillon}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Adam de Baillon - Seigneur of Valence}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Renee de Maillard}}}}.}
\dividerline

\entry{6612}{Pierre Vallee was born about 1606 in Saint-Saens}{Seine-Maritime, Haute-Normandie, France and died on 28 Mar 1657 in Saint-Saens, Seine-Maritime, Haute-Normandie, France, about age 51.}
\marriage{Pierre married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Madeleine Dumesnil}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Dumesnil}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Marie Laplanche}}}}.}
\childrenheading
\childentrylinked{3306}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Pierre Vallee}}}}}
\dividerline

\entry{6613}{Marie Madeleine Dumesnil}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Robert Dumesnil}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Marie Laplanche}}}}, died on 20 Mar 1646 in Saint-Saens, Seine-Maritime, Haute-Normandie, France.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Vallee.}}}}}
\dividerline

\entry{6616}{Olivier Roy was born on 2 Oct 1604 in Joigny}{Yonne, Bourgogne, France and died on 6 Dec 1661 in Joigny, Yonne, Bourgogne, France, at age 57.}
\marriage{Olivier married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Boderge.}}}}}
\childrenheading
\childentrylinked{3308}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Antoine Roy}}}}}
\dividerline

\entry{6617}{Catherine Boderge died on 20 Dec 1659 in Joigny}{Yonne, Bourgogne, France.}
\marriage{Catherine married \href{#}{\textcolor{accent}{\textbf{\underline{Olivier Roy.}}}}}
\dividerline

\entry{6618}{Jean Major}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Major}}}}, was born about 1615 in Grace, Calvados, Basse-Normandie, France and died on 11 Sep 1668 in Lisieux, Calvados, Basse-Normandie, France, about age 53.}
\marriage{Jean married \href{#}{\textcolor{accent}{\textbf{\underline{Marguerite le Pele.}}}}}
\childrenheading
\childentrylinked{3309}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marie Major}}}}}
\dividerline

\entry{6619}{Marguerite le Pele was born about 1610 in Touques}{Calvados, Basse-Normandie, France.}
\marriage{Marguerite married \href{#}{\textcolor{accent}{\textbf{\underline{Jean Major}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine Major}}}}.}
\dividerline

\entry{6622}{Jean-Galeran Boucher}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Marin Boucher}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Julienne Baril}}}}, was born on 16 Feb 1632 in St Langis les Mortagne, Perche, France and died on 28 Mar 1714 in Riviere-Ouelle, Kamouraska, Quebec, Canada, at age 82. (Duplicate. See Person 3258 on Page 1)}
\dividerline

\entry{6623}{Marie Helene Leclerc}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jonas Leclerc}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Marie Parmentier}}}}, was born on 13 Feb 1633 in Dieppe, Seine-Maritime, Haute-Normandie, France and died on 8 Oct 1702 in Chateau-Richer, La Cote-de-Beaupre, Quebec, Canada, at age 69. (Duplicate. See Person 3259 on Page 1)}
\dividerline

\entry{6628}{Aubin Doison}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Martin Doison}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Aubreton}}}}, was born about 1595 in Nantes, Haute, Bretagne, France and died on 2 Nov 1669 in Nantes, Haute, Bretagne, France, about age 74.}
\marriage{Aubin married \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Chartier on 31 Dec 1621 in Nantes}}}}, Haute, Bretagne, France.}
\childrenheading
\childentrylinked{3314}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Sebastian Doison}}}}}
\dividerline

\entry{6629}{Jeanne Chartier died on 15 Jul 1684 in Rennes}{Ille-et-Vilaine, Bretagne, France. Bretagne, France.}
\marriage{Jeanne married \href{#}{\textcolor{accent}{\textbf{\underline{Aubin Doison}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Martin Doison}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anne Aubreton}}}}, on 31 Dec 1621 in Nantes, Haute,}
\dividerline

\entry{6630}{Pierre Marechal was born about 1605 in Bellac}{Haute-Vienne, Limousin, France and died in 1669 in Limoges, Haute-Vienne, Limousin, France, about age 64.}
\marriage{Pierre married \href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Dubois.}}}}}
\childrenrenheading
\childentrylinked{3315}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Marguerite Marechal}}}}}
\childentryplain{6631. Jeanne Dubois died in 1679 in Amiens}{ii}{, Somme, Picardie, France.}
\childentry{}{Jeanne married Pierre Marechal.}
\dividerline

\entry{6632}{Nicolas Senecal was born about 1585 in Courcon}{Charente-Maritime, Poitou-Charentes, France and died on 17 Aug 1656 in Laguevin, Haute Garonne, Midi-Pyrenees, France, about age 71.}
\marriage{Nicolas married \href{#}{\textcolor{accent}{\textbf{\underline{Marie Gertrude Petit.}}}}}
\childrenheading
\childentrylinked{3316}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Adrien Senecal}}}}}
\dividerline

\entry{6633}{Marie Gertrude Petit was born in Rouen}{Seine-Maritime, Haute-Normandie, France and died on 4 Aug 1662 in Le Fay Saint Quentin, Oise, France.}
\marriage{Marie married \href{#}{\textcolor{accent}{\textbf{\underline{Nicolas Senecal.}}}}}
\dividerline

\entry{6634}{Jean Baptiste Lecompte}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Louis Lecompte}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Magdaleine Weber}}}}, was born on 20 Jul 1617 in La Rochelle, Aunis, Charente Maritime, France and died on 18 May 1662 in Elvange, Moselle, Lorraine, France, at age 44.}
\marriage{Jean married \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Monnette}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Monnette}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Helene}}}}.}
\childrenheading
\childentrylinked{3317}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jeanne le Compte}}}}}
\dividerline

\entry{6635}{Catherine Monnette}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Pierre Monnette}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Helene}}}}, was born on 23 Jan 1614 in Le Port, Gironde, Aquitaine, France and died in 1670 in Brie, Ille et Villaine, Bretagne, France, at age 56.}
\marriage{Catherine married \href{#}{\textcolor{accent}{\textbf{\underline{Jean Baptiste Lecompte}}}}, son of \href{#}{\textcolor{accent}{\textbf{\underline{Jean Louis Lecompte}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Magdaleine Weber}}}}.}
\dividerline

\entry{6638}{Augustin Hebert was born about 1623 in Paris}{Ile-de-France, France and died on 23 Nov 1653 in Trois Rivieres, Kamouraska, Quebec, Canada, about age 30. in Paris, Ile-de-France, France.}
\marriage{Augustin married \href{#}{\textcolor{accent}{\textbf{\underline{Adrienne du Vivier}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine du Vivier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Journe}}}}, on 13 Jun 1646}
\childrenheading
\childentrylinked{3319}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Jeanne Hebert}}}}}
\dividerline

\entry{6639}{Adrienne du Vivier}{daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Antoine du Vivier}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Catherine Journe}}}}, was born in Corbeny, Laon, Picardie, France and died on 20 Oct 1706 in Montreal, Quebec, Canada.}
\marriage{Adrienne married \href{#}{\textcolor{accent}{\textbf{\underline{Augustin Hebert on 13 Jun 1646 in Paris}}}}, Ile-de-France, France.}
\dividerline

\entry{7304}{Adam Lautenschlaeger}{son of \href{#}{\textcolor{accent}{\textbf{\underline{Wilhelm Lautenschlaeger}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Anna Catharina Ihrig}}}}, was born on 20 Nov 1603 in Gunterfurst, Erbach, Hesse, Germany and died on 9 Jun 1679 in Laudenau, Starkenburg, Hesse, Germany, at age 75.}
\marriage{Adam married \href{#}{\textcolor{accent}{\textbf{\underline{Anna Ihrig}}}}, daughter of \href{#}{\textcolor{accent}{\textbf{\underline{Jost Ihrig}}}} and \href{#}{\textcolor{accent}{\textbf{\underline{Margaretha Ziegler}}}}.}
\childrenheading
\childentrylinked{3652}{i}{\href{#}{\textcolor{accent}{\textbf{\underline{Johann Peter Lautenschlaeger}}}}}
\dividerline
